% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica VII Post Pentecosten}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Omnes gentes, pláudite mánibus: iubiláte Deo in voce exsultatiónis.
Quóniam Dóminus excélsus, terríbilis: Rex magnus super omnem terram.
}
\newcommand{\introitTranslation}{%
All you peoples clap your hands, shout to God with cries of gladness.
For the Lord, the Most High, the awesome, is the great King over all the earth.
}
% 
\newcommand{\collect}{%
  \l{%
Deus, cuius providéntia in sui dispositióne non fállitur: te súpplices exorámus; ut nóxia cuncta submóveas, et ómnia nobis profutúra concédas.
  }
  \e{%
O God, Whose providence never fails to set things in order, we humbly beseech You to remove from us whatever is harmful and grant whatever is for our benefit.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
Fratres: Humánum dico, propter infirmitátem carnis vestræ: sicut enim exhibuístis membra vestra servíre immundítiæ et iniquitáti ad iniquitátem, ita nunc exhibéte membra vestra servíre iustítiæ in sanctificatiónem. Cum enim servi essétis peccáti, líberi fuístis iustítiæ. Quem ergo fructum habuístis tunc in illis, in quibus nunc erubéscitis? Nam finis illórum mors est. Nunc vero liberáti a peccáto, servi autem facti Deo, habétis fructum vestrum in sanctificatiónem, finem vero vitam ætérnam. Stipéndia enim peccáti mors. Grátia autem Dei vita ætérna, in Christo Iesu, Dómino nostro.
  }
  \e{%
Brethren: I speak in a human way because of the weakness of your flesh; for as you yielded your members as slaves of uncleanness and iniquity unto iniquity, so now yield your members as slaves of justice unto sanctification. For when you were slaves of sin, you were free as regards justice. But what fruit had you then from those things of which you are now ashamed? For the end of these things is death. But now set free from sin and become slaves to God, you have your fruit unto sanctification, and as your end, life everlasting. For the wages of sin is death, but the gift of God is life everlasting in Christ Jesus our Lord.
  }
}

% 
\newcommand{\gradual}{%
Veníte, fílii, audíte me: timórem Dómini docébo vos.
Accédite ad eum, et illuminámini: et fácies vestræ non confundéntur.
Allelúia, allelúia.
Omnes gentes, pláudite mánibus: iubiláte Deo in voce exsultatiónis. Allelúia.
}
\newcommand{\gradualTranslation}{%
Come, children, hear me; I will teach you the fear of the Lord.
Look to Him that you may be radiant with joy, and your faces may not blush with shame. Alleluia, alleluia.
All you peoples, clap your hands, shout to God with cries of gladness. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Dixit Iesus discípulis suis: Atténdite a falsis prophétis, qui véniunt ad vos in vestiméntis óvium, intrínsecus autem sunt lupi rapáces: a frúctibus eórum cognoscétis eos. Numquid cólligunt de spinis uvas, aut de tríbulis ficus? Sic omnis arbor bona fructus bonos facit: mala autem arbor malos fructus facit. Non potest arbor bona malos fructus fácere: neque arbor mala bonos fructus fácere. Omnis arbor, quæ non facit fructum bonum, excidétur et in ignem mittétur. Igitur ex frúctibus eórum cognoscétis eos. Non omnis, qui dicit mihi, Dómine, Dómine, intrábit in regnum cœlórum: sed qui facit voluntátem Patris mei, qui in cœlis est, ipse intrábit in regnum cœlórum.
  }
  \e{%
At that time, Jesus said to His disciples: Beware of false prophets, who come to you in sheep’s clothing, but inwardly are ravenous wolves. By their fruits you will know them. Do men gather grapes from thorns, or figs from thistles? Even so, every good tree bears good fruit, but the bad tree bears bad fruit. A good tree cannot bear bad fruit, nor can a bad tree bear good fruit. Every tree that does not bear good fruit is cut down and thrown into the fire. Therefore, by their fruits you will know them. Not everyone who says to Me, ‘Lord, Lord,’ shall enter the kingdom of heaven; but he who does the will of My Father in heaven shall enter the kingdom of heaven.
  }
}
\newcommand{\offertory}{%
Sicut in holocáustis aríetum et taurórum, et sicut in mílibus agnórum pínguium: sic fiat sacrifícium nostrum in conspéctu tuo hódie, ut pláceat tibi: quia non est confúsio confidéntibus in te, Dómine.
}
\newcommand{\offertoryTranslation}{%
As though it were holocausts of rams and bullocks, or thousands of fat lambs, so let our sacrifice be in Your presence today, that it may please You; for those who trust in You cannot be put to shame, O Lord.
}
\newcommand{\secret}{%
  \l{%
Deus, qui legálium differéntiam hostiárum unius sacrifícii perfectione sanxísti: accipe sacrifícium a devótis tibi fámulis, et pari benedictióne, sicut múnera Abel, sanctífica; ut, quod sínguli obtulérunt ad maiestátis tuæ honórem, cunctis profíciat ad salútem.
  }
  \e{%
O God, You Who have given us in one perfect sacrifice the fulfillment of the various sacrifices made under the Old Law, accept these sacrificial gifts offered You by Your devoted servants, and make them holy as You did the gifts of Abel, so that what each one of us has offered in praise of Your majesty may profit for the salvation of all.
  }
  \per
}
\newcommand{\communion}{%
Inclína aurem tuam, accélera, ut erípias me.
}
\newcommand{\communionTranslation}{%
Incline Your ear to me, make haste to deliver me.
}
\newcommand{\postcommunion}{%
  \l{%
Tua nos, Dómine, medicinális operátio, et a nostris perversitátibus cleménter expédiat, et ad ea, quæ sunt recta, perdúcat.
  }
  \e{%
May Your healing action, O Lord, mercifully rid us of our evil inclinations and lead us to do good.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.


\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}

\newcommand{\itePath}{../Ordinaries/masses/11/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
