% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{In Circumcisione Domini}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Puer natus est nobis, et fílius datus est nobis: cujus impérium super húmerum ejus: et vocábitur nomen ejus magni consílii Angelus.
Cantáte Dómino cánticum novum, quia mirabília fecit.
}
\newcommand{\introitTranslation}{%
A Child is born to us, a Son is given to us; upon His shoulder dominion rests; and His name shall be called the Angel of great counsel.
Sing to the Lord a new song, for He has done wondrous deeds.
}
% 
\newcommand{\collect}{%
  \l{%
Deus, qui salútis ætérnæ, beátæ Maríæ virginitáte fecúnda, humáno generi præmia præstitísti: tríbue, quǽsumus; ut ipsam pro nobis intercédere sentiámus, per quam merúimus auctórem vitæ suscípere, Dóminum nostrum Jesum Christum, Fílium tuum:
  }
  \e{%
O God, Who by the fruitful virginity of blessed Mary, have bestowed upon mankind the reward of eternal salvation, grant, we beseech You, that we may enjoy the intercession of her through whom we have been found worthy to receive among us the author of life, our Lord Jesus Christ, Your Son,
  }
  \quiTecum
}
\newcommand{\lesson}{%
  \l{%
Caríssime: Appáruit grátia Dei Salvatóris nostri ómnibus homínibus, erúdiens nos, ut, abnegántes impietátem et sæculária desidéria, sóbrie et juste et pie vivámus in hoc sǽculo, exspectántes beátam spem et advéntum glóriæ magni Dei et Salvatóris nostri Jesu Christi: qui dedit semetípsum pro nobis: ut nos redímeret ab omni iniquitáte, et mundáret sibi pópulum acceptábilem, sectatórem bonórum óperum. Hæc lóquere et exhortáre: in Christo Jesu, Dómino nostro.
  }
  \e{%
Beloved: The grace of God our Saviour has appeared to all men, instructing us, in order that, rejecting ungodliness and worldly lusts, we may live temperately and justly and piously in this world; looking for the blessed hope and glorious coming of our great God and Saviour, Jesus Christ, Who gave Himself for us that He might redeem us from all iniquity and cleanse for Himself an acceptable people, pursuing good works. Thus speak, and exhort, in Christ Jesus our Lord.
  }
}

% 
\newcommand{\gradual}{%
Vidérunt omnes fines terræ salutare Dei nostri: jubiláte Deo, omnis terra.
Notum fecit Dominus salutare suum: ante conspéctum géntium revelávit justitiam suam. 
Allelúja, allelúja.
Multifárie olim Deus loquens pátribus in Prophétis, novíssime diébus istis locútus est nobis in Fílio. Allelúja.
}
\newcommand{\gradualTranslation}{%
All the ends of the earth have seen the salvation by our God. Sing joyfully to God, all you lands. 
The Lord has made His salvation known: in the sight of the nations He has revealed His justice. Alleluia, alleluia. 
God, Who in diverse ways spoke in times past to the fathers by the prophets; last of all, in these days, has spoken to us by His Son. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Postquam consummáti sunt dies octo, ut circumciderétur Puer: vocátum est nomen ejus Jesus, quod vocátum est ab Angelo, priúsquam in útero conciperétur.
  }
  \e{%
At that time, when eight days were fulfilled for the circumcision of the Child, His name was called Jesus, the name given Him by the angel before He was conceived in the womb.
  }
}
\newcommand{\offertory}{%
Tui sunt cœli et tua est terra: orbem terrárum et plenitúdinem ejus tu fundásti: justítia et judícium præparátio sedis tuæ.
}
\newcommand{\offertoryTranslation}{%
Yours are the heavens, and Yours is the earth; the world and its fullness You have founded. Justice and judgment are the foundation of Your throne.
}
\newcommand{\secret}{%
  \l{%
Obláta, Dómine, múnera, nova Unigéniti tui Nativitáte sanctífica: nosque a peccatórum nostrórum máculis emúnda.
  }
  \e{%
Make holy the sacrificial gifts we offer, O Lord, and by the new birth of Your only-begotten Son cleanse us from the stains of our sins.
  }
  \perEundem
}
\newcommand{\communion}{%
Vidérunt omnes fines terræ salutáre Dei nostri.
}
\newcommand{\communionTranslation}{%
All the ends of the earth have seen the salvation by our God.
}
\newcommand{\postcommunion}{%
  \l{%
Hæc nos commúnio, Dómine, purget a crímine: et, intercedénte beáta Vírgine Dei Genetríce María, cœléstis remédii fáciat esse consórtes.
  }
  \e{%
May this Communion, O Lord, cleanse us from sin and, through the intercession of the Blessed Virgin Mary, Mother of God, make us sharers of Your heavenly healing.
  }
  \perEundem
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/2/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/2/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/2/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/2/agnus}

\newcommand{\itePath}{../Ordinaries/masses/2/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/alma-redemptoris-mater}
\input{../MarianAntiphons/alma-redemptoris-mater_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
