% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Festum Sanctissimi Corporis Christi}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Cibávit eos ex ádipe fruménti, allelúia: et de petra, melle saturávit eos, allelúia, allelúia, allelúia.
Exsultáte Deo, adiutóri nostro: iubiláte Deo Iacob.
}
\newcommand{\introitTranslation}{%
He fed them with the fat of wheat, alleluia; and filled them with honey from the rock, alleluia, alleluia, alleluia.
Sing joyfully to God our strength; acclaim the God of Jacob.
}
% 
\newcommand{\collect}{%
  \l{%
  Deus, qui nobis sub Sacraménto mirábili passiónis tuæ memóriam reliquísti: tríbue, quǽsumus, ita nos Córporis et Sánguinis tui sacra mystéria venerári; ut redemptiónis tuæ fructum in nobis iúgiter sentiámus:
  }
  \e{%
  O God, You Who in this wondrous sacrament have left us a memorial of Your passion, grant us, we beseech You, so to venerate the sacred mysteries of Your Body and Blood that we may ever experience within us the effect of Your redemption.
  }
  \per
  \amen
}
\newcommand{\lesson}{%
  \l{%
  Fratres: Ego enim accépi a Dómino quod et trádidi vobis, quóniam Dóminus Iesus, in qua nocte tradebátur, accépit panem, et grátias agens fregit, et dixit: Accípite, et manducáte: hoc est corpus meum, quod pro vobis tradétur: hoc fácite in meam commemoratiónem. Simíliter et cálicem, postquam cenávit, dicens: Hic calix novum Testaméntum est in meo sánguine. Hoc fácite, quotiescúmque bibétis, in meam commemoratiónem. Quotiescúmque enim manducábitis panem hunc et cálicem bibétis, mortem Dómini annuntiábitis, donec véniat. Itaque quicúmque manducáverit panem hunc vel bíberit cálicem Dómini indígne, reus erit córporis et sánguinis Dómini. Probet autem seípsum homo: et sic de pane illo edat et de calice bibat. Qui enim mandúcat et bibit indígne, iudícium sibi mandúcat et bibit: non diiúdicans corpus Dómini.
  }
  \e{%
  Brethren: I myself have received from the Lord - what I also delivered to you, - that the Lord Jesus, on the night in which He was betrayed, took bread, and giving thanks broke, and said, Take and eat. This is My Body which shall be given up for you; do this in remembrance of Me. In like manner also the cup, after He had supped, saying, This is the new covenant in My Blood; do this as often as you drink it, in remembrance of Me. For as often as you shall eat this Bread and drink the cup, you proclaim the death of the Lord, until He comes. Therefore whoever eats this Bread or drinks the cup of the Lord unworthily, will be guilty of the Body and the Blood of the Lord. But let a man prove himself, and so let him eat of that Bread and drink of the cup; for he who eats and drinks unworthily, without distinguishing the Body, eats and drinks judgment to himself.
  }
}

% 
\newcommand{\gradual}{%
Oculi ómnium in te sperant, Dómine: et tu das illis escam in témpore opportúno,
Aperis tu manum tuam: et imples omne animal benedictióne. Allelúia, allelúia.
Caro mea vere est cibus, et sanguis meus vere est potus: qui mandúcat meam carnem et bibit meum sánguinem, in me manet et ego in eo. Alleluia.
}
\newcommand{\gradualTranslation}{%
The eyes of all hope in You, O Lord; and You give them their food in due season.
You open Your hand; and fill every living creature with Your blessing. Alleluia, alleluia.
My Flesh is food indeed, and My Blood is drink indeed. He who eats My Flesh, and drinks My Blood, abides in Me and I in him.
}
% 
\newcommand{\sequentia}{
Lauda, Sion, Salvatórem,
lauda ducem et pastórem
in hymnis et cánticis.

Quantum potes, tantum aude:
quia maior omni laude,
nec laudáre súfficis.

Laudis thema speciális,
panis vivus et vitális
hódie propónitur.

Quem in sacræ mensa cenæ
turbæ fratrum duodénæ
datum non ambígitur.

Sit laus plena, sit sonóra,
sit iucúnda, sit decóra
mentis iubilátio.

Dies enim sollémnis agitur,
in qua mensæ prima recólitur
huius institútio.

In hac mensa novi Regis,
novum Pascha novæ legis
Phase vetus términat.

Vetustátem nóvitas,
umbram fugat véritas,
noctem lux elíminat.

Quod in cœna Christus gessit,
faciéndum hoc expréssit
in sui memóriam.

Docti sacris institútis,
panem, vinum in salútis
consecrámus hóstiam.

Dogma datur Christiánis,
quod in carnem transit panis
et vinum in sánguinem.

Quod non capis, quod non vides,
animosa fírmat fides,
præter rerum órdinem.

Sub divérsis speciébus,
signis tantum, et non rebus,
latent res exímiæ.

Caro cibus, sanguis potus:
manet tamen Christus totus
sub utráque spécie.

A suménte non concísus,
non confráctus, non divísus:
ínteger accípitur.

Sumit unus, sumunt mille:
quantum isti, tantum ille:
nec sumptus consúmitur.

Sumunt boni, sumunt mali
sorte tamen inæquáli,
vitæ vel intéritus.

Mors est malis, vita bonis:
vide, paris sumptiónis
quam sit dispar éxitus.

Fracto demum sacraménto,
ne vacílles, sed meménto,
tantum esse sub fragménto,
quantum toto tégitur.

Nulla rei fit scissúra:
signi tantum fit fractúra:
qua nec status nec statúra
signáti minúitur.

Ecce panis Angelórum,
factus cibus viatórum:
vere panis filiórum,
non mitténdus cánibus.

In figúris præsignátur,
cum Isaac immolátur:
agnus paschæ deputátur:
datur manna pátribus.

Bone pastor, panis vere,
Iesu, nostri miserére:
tu nos pasce, nos tuére:
tu nos bona fac vidére
in terra vivéntium.

Tu, qui cuncta scis et vales:
qui nos pascis hic mortáles:
tuos ibi commensáles,
coherédes et sodáles
fac sanctórum cívium.
Amen. Allelúia.
}
\newcommand{\sequentiaTranslation}{
Sion, lift up thy voice and sing:
Praise thy Savior and thy King,
Praise with hymns thy shepherd true:

Strive thy best to praise him well,
Yet doth he all praise excel;
None can ever reach his due.

See today before us laid
The living and life-giving Bread,
Theme for praise and joy profound.

The same which at the sacred board
Was, by our incarnate Lord,
Given to His Apostles round.

Let the praise be loud and high:
Sweet and tranquil be the joy
Felt today in every breast;

On this festival divine
Which records the origin
Of the glorious Eucharist.

On this table of the King,
Our new Pas\-chal offering
Brings to end the olden rite.

Here, for empty shadows fled,
Is reality instead;
Here, instead of darkness, light.

His own act, at supper seated
Christ ordained to be repeated
In His memory divine;

Wherefore now, with adoration,
We the host of our salvation
Consecrate from bread and wine.

Hear what holy Church maintaineth,
That the bread its substance changeth
Into Flesh, the wine to Blood.

Doth it pass thy comprehending?
Faith, the law of sight transcending
Leaps to things not understood.

Here beneath these signs are hidden
Priceless things, to sense forbidden,\linebreak[5]
Signs, not things, are all we see,--

Flesh from bread, and Blood from wine,
Yet is Christ in either sign,
All entire, confessed to be.

They, who of Him here partake,
Sever not, nor rend, nor break:
But, entire, their Lord receive.

Whether one or thousands eat:
All receive the selfsame meat:
Nor the less for others leave.

Both the wicked and the good
Eat of this celestial Food:
But with ends how opposite!

Here 'tis life: and there 'tis death:
The same, yet issuing to each
In a difference infinite.

Nor a single doubt retain,
When they break the Host in twain,
But that in each part remains
What was in the whole before.

Since the simple sign alone
Suffers change in state or form:
The signified remaining one
And the same for evermore.

Behold the Bread of Angels,
For us pilgrims food, and token
Of the promise by Christ spoken,
Children's meat, to dogs denied.

In the old types foresignified
With Issac's immolation:
Of the appointed Pas\-chal lamb:
Manna given to the fathers.

Jesu, shepherd of the sheep:
Thou thy flock in safety keep,
Living bread, thy life supply:
Strengthen us, or else we die,
Fill us with celestial grace.

Thou, who feedest us below:
Source of all we have or know:
Grant that with Thy Saints above,
Sitting at the feast of love,
We may see Thee face to face.
Amen. Alleluia.
}
\newcommand{\gospel}{%
  \l{%
  In illo témpore: Dixit Iesus turbis Iudæórum: Caro mea vere est cibus et sanguis meus vere est potus. Qui mandúcat meam carnem et bibit meum sánguinem, in me manet et ego in illo. Sicut misit me vivens Pater, et ego vivo propter Patrem: et qui mandúcat me, et ipse vivet propter me. Hic est panis, qui de cœlo descéndit. Non sicut manducavérunt patres vestri manna, et mórtui sunt. Qui mandúcat hunc panem, vivet in ætérnum.
  }
  \e{%
  At that time, Jesus said to the crowds of the Jews: My Flesh is food indeed, and My Blood is drink indeed. He who eats My Flesh, and drinks My Blood, abides in Me and I in him. As the living Father has sent Me, and as I live because of the Father, so he who eats Me, he also shall live because of Me. This is the Bread that has come down from heaven; not as your fathers ate the manna, and died. He who eats this Bread shall live forever.
  }
}
\newcommand{\offertory}{%
Sacerdótes Dómini incénsum et panes ófferunt Deo: et ideo sancti erunt Deo suo, et non pólluent nomen eius, allelúia.
}
\newcommand{\offertoryTranslation}{%
The priests of the Lord offer incense and loaves to God, and therefore they shall be sacred to their God and shall not profane His name. Alleluia.
}
\newcommand{\secret}{%
  \l{%
  Ecclésiæ tuæ, quǽsumus, Dómine, unitátis et pacis propítius dona concéde: quæ sub oblátis munéribus mýstice designántur.
  }
  \e{%
  Graciously give Your Church, we beseech You, O Lord, the gifts of unity and peace which are betokened by the gifts we offer.
  }
}
\newcommand{\communion}{%
Quotiescúmque manducábitis panem hunc et cálicem bibétis, mortem Dómini annuntiábitis, donec véniat: itaque quicúmque manducáverit panem vel bíberit calicem Dómini indígne, reus erit córporis et sánguinis Dómini, allelúia.
}
\newcommand{\communionTranslation}{%
As often as you shall eat this Bread and drink the cup, you proclaim the death of the Lord, until He comes. Therefore whoever eats this Bread or drinks the cup of the Lord unworthily, will be guilty of the Body and Blood of the Lord. Alleluia.
}
\newcommand{\postcommunion}{%
  \l{%
  Fac nos, quǽsumus, Dómine, divinitátis tuæ sempitérna fruitióne repléri: quam pretiósi Corporis et Sanguinis tui temporalis percéptio præfigúrat:
  }
  \e{%
  Grant, we beseech You, O Lord, that we may be filled with that everlasting enjoyment of Your Godhead, as foreshadowed here on earth by the partaking of Your precious Body and Blood.
  }
  \per
  \amen
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../Ordinaries/masses/1/kyrie}
\newcommand{\gloriaPath}{../Ordinaries/masses/1/gloria}
\newcommand{\sanctusPath}{../Ordinaries/masses/1/sanctus}
\newcommand{\agnusPath}{../Ordinaries/masses/1/agnus}
\newcommand{\itePath}{../Ordinaries/masses/1/ite}
% 
\newcommand{\creedPath}{../Ordinaries/credo/1/credo}
% 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
