% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica II Post Pentecosten}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
  Factus est Dóminus protéctor meus, et edúxit me in latitúdinem: salvum me fecit, quóniam vóluit me.
  Díligam te. Dómine, virtus mea: Dóminus firmaméntum meum et refúgium meum et liberátor meus.
}
\newcommand{\introitTranslation}{%
  The Lord came to my support. He set me free in the open, and rescued me, because He loves me.
  I love You, O Lord, my strength, O Lord, my rock, my fortress, my deliverer.
}
% 
\newcommand{\collect}{%
  \l{%
    Sancti nóminis tui, Dómine, timórem páriter et amórem fac nos habére perpétuum: quia numquam tua gubernatióne destítuis, quos in soliditáte tuæ dilectiónis instítuis.
  }
  \e{%
    Grant, O Lord, that we may always fear and love Your holy Name, for You never fail to guide those whom You firmly establish in Your love.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
    Caríssimi: Nolíte mirári, si odit vos mundus. Nos scimus, quóniam transláti sumus de morte ad vitam, quóniam dilígimus fratres. Qui non díligit, manet in morte: omnis, qui odit fratrem suum, homícida est. Et scitis, quóniam omnis homícida non habet vitam ætérnam in semetípso manéntem. In hoc cognóvimus caritátem Dei, quóniam ille ánimam suam pro nobis pósuit: et nos debémus pro frátribus ánimas pónere. Qui habúerit substántiam huius mundi, et víderit fratrem suum necessitátem habére, et cláuserit víscera sua ab eo: quómodo cáritas Dei manet in eo? Filíoli mei, non diligámus verbo neque lingua, sed ópere et veritáte.
  }
  \e{%
    Beloved: Do not be surprised if the world hates you. We know that we have passed from death to life, because we love the brethren. He who does not love abides in death. Everyone who hates his brother is a murderer. And you know that no murderer has eternal life abiding in him. In this we have come to know His love, that He laid down His life for us; and we likewise ought to lay down our life for the brethren. He who has the goods of this world and sees his brother in need and closes his heart to him, how does the love of God abide in him? My dear children, let us not love in word, neither with the tongue, but in deed and in truth.
  }
}

% 
\newcommand{\gradual}{%
  Ad Dóminum, cum tribulárer, clamávi, et exaudívit me.
  \v~Dómine, libera ánimam meam a lábiis iníquis, et a lingua dolósa. Allelúia, allelúia
  Dómine, Deus meus, in te sperávi: salvum me fac ex ómnibus persequéntibus me et líbera me. Allelúia.
}
\newcommand{\gradualTranslation}{%
  In my distress I called to the Lord, and He answered me.
  \v~O Lord, deliver me from lying lip, from treacherous tongue. Alleluia, alleluia.
  O Lord my God, in You I take refuge; save me from all my pursuers and rescue me. Alleluia.
}
% 
\newcommand{\gospel}{%
  \l{%
    In illo témpore: Dixit Iesus pharisǽis parábolam hanc: Homo quidam fecit cœnam magnam, et vocávit multos. Et misit servum suum hora cœnæ dícere invitátis, ut venírent, quia iam paráta sunt ómnia. Et cœpérunt simul omnes excusáre. Primus dixit ei: Villam emi, et necésse hábeo exíre et vidére illam: rogo te, habe me excusátum. Et alter dixit: Iuga boum emi quinque et eo probáre illa: rogo te, habe me excusátum. Et álius dixit: Uxórem duxi, et ídeo non possum veníre. Et revérsus servus nuntiávit hæc dómino suo. Tunc irátus paterfamílias, dixit servo suo: Exi cito in pláteas et vicos civitátis: et páuperes ac débiles et cæcos et claudos íntroduc huc. Et ait servus: Dómine, factum est, ut imperásti, et adhuc locus est. Et ait dóminus servo: Exi in vias et sepes: et compélle intrare, ut impleátur domus mea. Dico autem vobis, quod nemo virórum illórum, qui vocáti sunt, gustábit cœnam meam.
  }
  \e{%
At that time, Jesus spoke to the Pharisees this parable: A certain man gave a great supper, and he invited many. And he sent his servant at supper time to tell those invited to come, for everything is now ready. And they all with one accord began to excuse themselves. The first said to him, ‘I have bought a farm, and I must go out and see it; I pray you hold me excused.’ And another said, ‘I have bought five yoke of oxen, and I am on my way to try them; I pray you hold me excused.’ And another said, ‘I have married a wife, and therefore I cannot come.’ And the servant returned, and reported these things to his master. Then the master of the house was angry and said to his servant, ‘Go out quickly into the streets and lanes of the city, and bring in here the poor, and the crippled, and the blind, and the lame.’ And the servant said, ‘Sir, your order has been carried out, and still there is room.’ Then the master said to the servant, ‘Go out into the highways and hedges, and make them come in, so that my house may be filled. For I tell you that none of those who were invited shall taste of my supper.’
  }
}
\newcommand{\offertory}{%
}
\newcommand{\offertoryTranslation}{%
}
\newcommand{\secret}{%
  \l{%
    Dómine, convértere, et éripe ánimam meam: salvum me fac propter misericórdiam tuam.
  }
  \e{%
    Return, O Lord, save my life; rescue me because of Your kindness.
  }
}
\newcommand{\communion}{%
  Cantábo Dómino, qui bona tríbuit mihi: et psallam nómini Dómini altíssimi.
}
\newcommand{\communionTranslation}{%
  I will sing of the Lord, He has been good to me; and I will sing to the Name of the Lord the Most High.
}
\newcommand{\postcommunion}{%
  \l{%
    Sumptis munéribus sacris, quǽsumus, Dómine: ut cum frequentatióne mystérii, crescat nostræ salútis efféctus.
  }
  \e{%
    We beseech You, O Lord, that having received Your gifts, each partaking of this sacrament may increase within us its saving effects.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}
\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}
\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}
\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}
\newcommand{\itePath}{../Ordinaries/masses/11/ite}
% 
\newcommand{\creedPath}{../Ordinaries/credo/1/credo}
% 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
