% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica XXIII Post Pentecosten}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Dicit Dóminus: Ego cógito cogitatiónes pacis, et non afflictiónis: invocábitis me, et ego exáudiam vos: et redúcam captivitátem vestram de cunctis locis.
Benedixísti, Dómine, terram tuam: avertísti captivitátem Jacob.
}
\newcommand{\introitTranslation}{%
The Lord says: “I think thoughts of peace, and not of affliction. You shall call upon Me, and I will hear you; and I will bring back your captivity from all places.”
You have favored, O Lord, Your land; You have restored the well-being of Jacob.
}
% 
\newcommand{\collect}{%
  \l{%
  Absólve, quǽsumus, Dómine, tuórum delícta populórum: ut a peccatórum néxibus, quæ pro nostra fragilitáte contráximus, tua benignitáte liberémur.
  }
  \e{%
  Forgive, we beseech You, O Lord, the sins of Your faithful people, so that by Your goodness we may be released from the net of sin in which we have been caught by our weakness.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
  Fratres: Imitatóres mei estóte, et observáte eos, qui ita ámbulant, sicut habétis formam nostram. Multi enim ámbulant, quos sæpe dicébam vobis - nunc autem et flens dico - inimícos Crucis Christi: quorum finis intéritus: quorum Deus venter est: et glória in confusióne ipsórum, qui terréna sápiunt. Nostra autem conversátio in cœlis est: unde étiam Salvatórem exspectámus, Dóminum nostrum Jesum Christum, qui reformábit corpus humilitátis nostræ, configurátum córpori claritátis suæ, secúndum operatiónem, qua étiam possit subjícere sibi ómnia. Itaque, fratres mei caríssimi et desideratíssimi, gáudium meum et coróna mea: sic state in Dómino, caríssimi. Evódiam rogo et Sýntychen déprecor idípsum sápere in Dómino. Etiam rogo et te, germáne compar, ádjuva illas, quæ mecum laboravérunt in Evangélio cum Cleménte et céteris adjutóribus meis, quorum nómina sunt in libro vitæ.
  }
  \e{%
  Brethren: Be imitators of me, and mark those who walk after the pattern you have in us. For many walk, of whom I have told you often and now tell you even weeping, that they are enemies of the Cross of Christ. Their end is ruin, their god is the belly, their glory is in their shame, they mind the things of earth. But our citizenship is in heaven from which also we eagerly await a Saviour, our Lord Jesus Christ, Who will refashion the body of our lowliness, conforming it to the body of His glory by exerting the power by which He is able also to subject all things to Himself. So then, my brethren, beloved and longed for, my joy and my crown, stand fast thus in the Lord, beloved. I entreat Evodia and I exhort Syntyche to be of one mind in the Lord. And I beseech you also, my loyal comrade, help them, for they have toiled with me in the gospel, as have Clement and the rest of my fellow-workers whose names are in the book of life.
  }
}

% 
\newcommand{\gradual}{%
Liberásti nos, Dómine, ex affligéntibus nos: et eos, qui nos odérunt, confudísti.
In Deo laudábimur tota die, et in nómine tuo confitébimur in sǽcula. Allelúja, allelúja.
De profúndis clamávi ad te, Dómine: Dómine, exáudi oratiónem meam. Allelúja.
}
\newcommand{\gradualTranslation}{%
You saved us, O Lord, from our foes, and those who hated us You put to shame.
Out of the depths I have cried to thee, O Lord: Lord, hear my prayer.
Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
  In illo témpore: Loquénte Jesu ad turbas, ecce, princeps unus accéssit et adorábat eum, dicens: Dómine, fília mea modo defúncta est: sed veni, impóne manum tuam super eam, et vivet. Et surgens Jesus sequebátur eum et discípuli ejus. Et ecce múlier, quæ sánguinis fluxum patiebátur duódecim annis, accéssit retro et tétigit fímbriam vestiménti ejus. Dicébat enim intra se: Si tetígero tantum vestiméntum ejus, salva ero. At Jesus convérsus et videns eam, dixit: Confíde, fília, fides tua te salvam fecit. Et salva facta est múlier ex illa hora. Et cum venísset Jesus in domum príncipis, et vidísset tibícines et turbam tumultuántem, dicebat: Recédite: non est enim mórtua puélla, sed dormit. Et deridébant eum. Et cum ejécta esset turba, intrávit et ténuit manum ejus. Et surréxit puélla. Et éxiit fama hæc in univérsam terram illam.
  }
  \e{%
  At that time, as Jesus was speaking to the crowds, behold, a ruler came up and worshipped Him, saying, “Lord, my daughter has just now died; but come and lay Your hand upon her, and she will return to life.” And Jesus arose and followed him, and so did His disciples. Now a woman who for twelve years had been suffering from hemorrhage, came up behind him and touched the tassel of His cloak saying to herself, “If I touch but His cloak I shall be saved.” But Jesus, turning and seeing her, said, “Take courage, daughter; your faith has saved you.” And the woman was restored to health from that moment. And when Jesus came to the ruler's house, and saw the flute players and the crowd making a din, He said, “Begone, the girl is asleep, not dead.” And they laughed Him to scorn. But when the crowd had been put out, He went in and took her by the hand; and the girl arose. And the report of this spread throughout all that district.
  }
}
\newcommand{\offertory}{%
De profúndis clamávi ad te, Dómine: Dómine, exáudi oratiónem meam: de profúndis clamávi ad te, Dómine.
}
\newcommand{\offertoryTranslation}{%
Out of the depths I cry to You, O Lord; Lord, hear my prayer! Out of the depths I cry to You, O Lord.
}
\newcommand{\secret}{%
  \l{%
  Pro nostræ servitútis augménto sacrifícium tibi, Dómine, laudis offérimus: ut, quod imméritis contulísti, propítius exsequáris.
  }
  \e{%
  We offer You O Lord, the sacrifice of praise that we may serve You even better, so that You may graciously complete what You have given us, Your undeserving servants.
  }
  \perDominum
}
\newcommand{\communion}{%
Amen, dico vobis, quidquid orántes pétitis, crédite, quia accipiétis, et fiet vobis.
}
\newcommand{\communionTranslation}{%
Amen I say to you, all things whatever you ask for in prayer, believe that you shall receive, and it shall be done to you.
}
\newcommand{\postcommunion}{%
  \l{%
  Quǽsumus, omnípotens Deus: ut, quos divína tríbuis participatióne gaudére, humánis non sinas subjacére perículis.
  }
  \e{%
  We beseech You, almighty God, let not human dangers overcome us to whom You grant joyful participation in things divine.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}

\newcommand{\itePath}{../Ordinaries/masses/11/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
