% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica in Quinquagesima}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
  Esto mihi in Deum protectórem, et in locum refúgii, ut salvum me fácias: quóniam firmaméntum meum et refúgium meum es tu: et propter nomen tuum dux mihi eris, et enútries me.
  In te, Dómine, sperávi, non confúndar in ætérnum: in iustítia tua líbera me et éripe me.
}
\newcommand{\introitTranslation}{%
  Be my rock of refuge, O God, a stronghold to give me safety. You are my rock and my fortress; for Your name’s sake You will lead and guide me.
  In You, O Lord, I take refuge; let me never be put to shame. In Your justice rescue me and deliver me.
}
% 
\newcommand{\collect}{%
  \l{%
    Preces nostras, quǽsumus, Dómine, cleménter exáudi: atque, a peccatórum vínculis absolútos, ab omni nos adversitáte custódi.
  }
  \e{%
    O Lord, we beseech You, mercifully hear our prayers; loose us from the chains of our sins and keep us from all adversity.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
Fratres: Si linguis hóminum loquar et Angelórum, caritátem autem non hábeam, factus sum velut æs sonans aut cýmbalum tínniens. Et si habúero prophetíam, et nóverim mystéria ómnia et omnem sciéntiam: et si habúero omnem fidem, ita ut montes tránsferam, caritátem autem non habúero, nihil sum. Et si distribúero in cibos páuperum omnes facultátes meas, et si tradídero corpus meum, ita ut árdeam, caritátem autem non habuero, nihil mihi prodest. Cáritas patiens est, benígna est: cáritas non æmulátur, non agit pérperam, non inflátur, non est ambitiósa, non quærit quæ sua sunt, non irritátur, non cógitat malum, non gaudet super iniquitáte, congáudet autem veritáti: ómnia suffert, ómnia credit, ómnia sperat, ómnia sústinet. Cáritas numquam éxcidit: sive prophétiæ evacuabúntur, sive linguæ cessábunt, sive sciéntia destruétur. Ex parte enim cognóscimus, et ex parte prophetámus. Cum autem vénerit quod perféctum est, evacuábitur quod ex parte est. Cum essem párvulus, loquébar ut párvulus, sapiébam ut párvulus, cogitábam ut párvulus. Quando autem factus sum vir, evacuávi quæ erant párvuli. Vidémus nunc per spéculum in ænígmate: tunc autem fácie ad fáciem. Nunc cognósco ex parte: tunc autem cognóscam, sicut et cógnitus sum. Nunc autem manent fides, spes, cáritas, tria hæc: maior autem horum est cáritas.
  }
  \e{%
Brethren: If I should speak with the tongues of men and of angels, but do not have charity, I have become as sounding brass or a tinkling cymbal. And if I have prophecy and know all mysteries and all knowledge, and if I have all faith so as to remove mountains, yet do not have charity, I am nothing. And if I distribute all my goods to feed the poor, and if I deliver my body to be burned, yet do not have charity, it profits me nothing. Charity is patient, is kind; charity does not envy, is not pretentious, is not puffed up, is not ambitious, is not self-seeking, is not provoked; thinks no evil, does not rejoice over wickedness, but rejoices with the truth; bears with all things, believes all things, hopes all things, endures all things. Charity never fails, whereas prophecies will disappear, and tongues will cease, and knowledge will be destroyed. For we know in part and we prophesy in part; but when that which is perfect has come, that which is imperfect will be done away with. When I was a child, I spoke as a child, I felt as a child, I thought as a child. Now that I have become a man, I have put away the things of a child. We see now through a mirror in an obscure manner, but then face to face. Now I know in part, but then I shall know even as I have been known. So there abide faith, hope and charity, these three; but the greatest of these is charity.
  }
}

% 
\newcommand{\gradual}{%
  Tu es Deus qui facis mirabília solus: notam fecísti in géntibus virtútem tuam.
  Liberásti in bráchio tuo pópulum tuum, fílios Israël et Ioseph.
  Iubiláte Deo, omnis terra: servíte Dómino in lætítia,
  Intráte in conspéctu eius in exsultatióne: scitóte, quod Dóminus ipse est Deus.
  Ipse fecit nos, et non ipsi nos: nos autem pópulus eius, et oves páscuæ eius.
}
\newcommand{\gradualTranslation}{%
  You are the God Who alone works wonders; among the peoples You have made known Your power.
  With Your strong arm You delivered Your people, the sons of Israel and Joseph.
  Sing joyfully to God, all you lands; serve the Lord with gladness.
  Come before Him with joyful song; know that the Lord is God.
  He made us, His we are; His people, the flock He tends.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Assúmpsit Iesus duódecim, et ait illis: Ecce, ascéndimus Ierosólymam, et consummabúntur ómnia, quæ scripta sunt per Prophétas de Fílio hominis. Tradétur enim Géntibus, et illudétur, et flagellábitur, et conspuétur: et postquam flagelláverint, occídent eum, et tértia die resúrget. Et ipsi nihil horum intellexérunt, et erat verbum istud abscónditum ab eis, et non intellegébant quæ dicebántur. Factum est autem, cum appropinquáret Iéricho, cæcus quidam sedébat secus viam, mendícans. Et cum audíret turbam prætereúntem, interrogábat, quid hoc esset. Dixérunt autem ei, quod Iesus Nazarénus transíret. Et clamávit, dicens: Iesu, fili David, miserére mei. Et qui præíbant, increpábant eum, ut tacéret. Ipse vero multo magis clamábat: Fili David, miserére mei. Stans autem Iesus, iussit illum addúci ad se. Et cum appropinquásset, interrogávit illum, dicens: Quid tibi vis fáciam? At ille dixit: Dómine, ut vídeam. Et Iesus dixit illi: Réspice, fides tua te salvum fecit. Et conféstim vidit, et sequebátur illum, magníficans Deum. Et omnis plebs ut vidit, dedit laudem Deo.
  }
  \e{%
At that time, Jesus taking to Himself the Twelve said to them, Behold, we are going up to Jerusalem, and all things that have been written by the prophets concerning the Son of Man will be accomplished. For He will be delivered to the Gentiles, and will be mocked and scourged and spit upon; and after they have scourged Him, they will put Him to death; and on the third day He will rise again. And they understood none of these things and this saying was hidden from them, neither did they get to know the things that were being said. Now it came to pass as He drew near to Jericho, that a certain blind man was sitting by the wayside, begging; but hearing a crowd passing by, he inquired what this might be. And they told him that Jesus of Nazareth was passing by. And he cried out, saying, Jesus, Son of David, have mercy on me! And they who went in front angrily tried to silence him. But he cried out all the louder, Son of David, have mercy on me! Then Jesus stopped and commanded that he should be brought to Him. And when he drew near, He asked him, saying, What would you have Me do for you? And he said, Lord, that I may see. And Jesus said to him, Receive your sight, your faith has saved you. And at once he received his sight, and followed Him, glorifying God. And all the people upon seeing it gave praise to God.
  }
}
\newcommand{\offertory}{%
  Benedíctus es, Dómine, doce me iustificatiónes tuas: in lábiis meis pronuntiávi ómnia iudícia oris tui.
}
\newcommand{\offertoryTranslation}{%
  Blessed are You, O Lord; teach me Your statutes. With my lips I declare all the ordinances of Your mouth.
}
\newcommand{\secret}{%
  \l{%
    Hæc hóstia, Dómine, quǽsumus, emúndet nostra delícta: et, ad sacrifícium celebrándum, subditórum tibi córpora mentésque sanctíficet.
  }
  \e{%
    Hæc hóstia, Dómine, quǽsumus, emúndet nostra delícta: et, ad sacrifícium celebrándum, subditórum tibi córpora mentésque sanctíficet.
  }
  \per
}
\newcommand{\communion}{%
  Manducavérunt, et saturári sunt nimis, et desidérium eórum áttulit eis Dóminus: non sunt fraudáti a desidério suo.
}
\newcommand{\communionTranslation}{%
  They ate and were wholly surfeited; the Lord had brought them what they craved: they were not defrauded of that which they craved.
}
\newcommand{\postcommunion}{%
  \l{%
    Quǽsumus, omnípotens Deus: ut, qui coeléstia aliménta percépimus, per hæc contra ómnia adversa muniámur.
  }
  \e{%
    We beseech You, almighty God, that we who have received the Bread of heaven, may by it be protected from all adversity.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.


\newcommand{\kyriePath}{../Ordinaries/masses/4/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/4/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/4/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/4/agnus}

\newcommand{\itePath}{../Ordinaries/masses/4/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/ave-regina-caelorum}
\input{../MarianAntiphons/ave-regina-caelorum_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
