% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica VI quæ superfuit Post Epiphaniam}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Da pacem, Dómine, sustinéntibus te, ut prophétæ tui fidéles inveniántur: exáudi preces servi tui et plebis tuæ Israël
Lætátus sum in his, quæ dicta sunt mihi: in domum Dómini íbimus.
}
\newcommand{\introitTranslation}{%
Give peace, O Lord, to those who have hoped in You, and let Your Prophets be proved true. Hear the prayers of Your servant, and of Your people Israel.
I rejoiced because they said to me, We will go up to the house of the Lord.
}
% 
\newcommand{\collect}{%
  \l{%
    Præsta, quǽsumus, omnípotens Deus: ut, semper rationabília meditántes, quæ tibi sunt plácita, et dictis exsequámur et factis.
  }
  \e{%
    Grant us, we beseech You, almighty God, ever to think of spiritual things and in every word and work always to do what is well pleasing in Your sight.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
    Fratres: Grátias ágimus Deo semper pro ómnibus vobis, memóriam vestri faciéntes in oratiónibus nostris sine intermissióne, mémores óperis fídei vestræ, et labóris, et caritátis, et sustinéntiæ spei Dómini nostri Jesu Christi, ante Deum et Patrem nostrum: sciéntes, fratres, dilécti a Deo. electiónem vestram: quia Evangélium nostrum non fuit ad vos in sermóne tantum, sed et in virtúte, et in Spíritu Sancto, et in plenitúdine multa, sicut scitis quales fuérimus in vobis propter vos. Et vos imitatóres nostri facti estis, et Dómini, excipiéntes verbum in tribulatióne multa, cum gáudio Spíritus Sancti: ita ut facti sitis forma ómnibus credéntibus in Macedónia et in Achája. A vobis enim diffamátus est sermo Dómini, non solum in Macedónia et in Achája, sed et in omni loco fides vestra, quæ est ad Deum, profécta est, ita ut non sit nobis necésse quidquam loqui. Ipsi enim de nobis annúntiant, qualem intróitum habuérimus ad vos: et quómodo convérsi estis ad Deum a simulácris, servíre Deo vivo et vero, et exspectáre Fílium ejus de cœlis quem suscitávit ex mórtuis Jesum, qui erípuit nos ab ira ventúra.
  }
  \e{%
    Brethren: We give thanks to God always for you all, continually making a remembrance of you in our prayers; being mindful before God our Father of your work of faith, and labor, and charity, and your enduring hope in our Lord Jesus Christ. We know, brethren, beloved of God, how you were chosen. For our Gospel was not delivered to you in word only, but in power also, and in the Holy Spirit, and in much fullness, as indeed you know what manner of men we have been among you for your sakes. And you became imitators of us and of the Lord, receiving the word in great tribulation, with joy of the Holy Spirit, so that you became a pattern to all the believers in Macedonia and in Achaia. For from you the word of the Lord has been spread abroad, not only in Macedonia and Achaia, but in every place your faith in God has gone forth, so that we need say nothing further. For they themselves report concerning us how we entered among you, and how you turned to God from idols, to serve the living and true God, and to await from heaven Jesus, His Son, Whom He raised from the dead, Who has delivered us from the wrath to come.
  }
}

% 
\newcommand{\gradual}{%
Lætátus sum in his, quæ dicta sunt mihi: in domum Dómini íbimus.
Fiat pax in virtúte tua: et abundántia in túrribus tuis. Allelúia, allelúia
Timébunt gentes nomen tuum, Dómine, et omnes reges terræ glóriam tuam. Allelúia.
}
\newcommand{\gradualTranslation}{%
I rejoiced because they said to me, We will go up to the house of the Lord.
May peace be within your walls, prosperity in your buildings. Alleluia, alleluia.
The nations shall revere Your name, O Lord, and all the kings of the earth Your glory. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
    In illo témpore: Dixit Jesus turbis parábolam hanc: Símile est regnum cœlórum grano sinápis, quod accípiens homo seminávit in agro suo: quod mínimum quidem est ómnibus semínibus: cum autem créverit, majus est ómnibus oléribus, et fit arbor, ita ut vólucres cœli véniant et hábitent in ramis ejus. Aliam parábolam locútus est eis: Símile est regnum cœlórum ferménto, quod accéptum múlier abscóndit in farínæ satis tribus, donec fermentátum est totum. Hæc ómnia locútus est Jesus in parábolis ad turbas: et sine parábolis non loquebátur eis: ut implerétur quod dictum erat per Prophétam dicéntem: Apériam in parábolis os meum, eructábo abscóndita a constitutióne mundi.
  }
  \e{%
    At that time, Jesus spoke this parable to the crowds: The kingdom of heaven is like a grain of mustard seed, which a man took and sowed in his field. This indeed is the smallest of all the seeds; but when it grows up it is larger than any herb and becomes a tree, so that the birds of the air come and dwell in its branches. He told them another parable: The kingdom of heaven is like leaven, which a woman took and buried in three measures of flour, until all of it was leavened. All these things Jesus spoke to the crowds in parables, and without parables he did not speak to them; that what was spoken by the prophet might be fulfilled, I will open My mouth in parables, I will utter things hidden since the foundation of the world.
  }
}
\newcommand{\offertory}{%
  Sanctificávit Móyses altáre Dómino, ófferens super illud holocáusta et ímmolans víctimas: fecit sacrifícium vespertínum in odórem suavitátis Dómino Deo, in conspéctu filiórum Israël.
}
\newcommand{\offertoryTranslation}{%
  Moses consecrated an altar to the Lord, offering upon it holocausts, and sacrificing victims: he made an evening sacrifice to the Lord God for an odor of sweetness, in the sight of the Israelites.
}
\newcommand{\secret}{%
  \l{%
    Hæc nos oblátio, Deus, mundet, quǽsumus, et rénovet, gubérnet et prótegat.
  }
  \e{%
    May this offering, O God, we beseech You, cleanse and renew us, govern and protect us.
  }
  \perDominum
}
\newcommand{\communion}{%
  Tóllite hóstias, et introíte in átria eius: adoráte Dóminum in aula sancta eius.
}
\newcommand{\communionTranslation}{%
  Bring gifts and enter His courts; worship the Lord in His holy court.
}
\newcommand{\postcommunion}{%
  \l{%
    Cœléstibus, Dómine, pasti delíciis: quǽsumus; ut semper éadem, per quæ veráciter vívimus, appétimus.
  }
  \e{%
    Nourished by Your heavenly food, O Lord, we beseech You that we may always strive after those things that give us true life.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}

\newcommand{\itePath}{../Ordinaries/masses/11/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
