% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica III Post Pentecosten}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Réspice in me et miserére mei, Dómine: quóniam únicus et pauper sum ego: vide humilitátem meam et labórem meum: et dimítte ómnia peccáta mea, Deus meus.
Ad te, Dómine, levávi ánimam meam: Deus meus, in te confído, non erubéscam.
}
\newcommand{\introitTranslation}{%
Look toward me, and have pity on me, O Lord, for I am alone and afflicted. Put an end to my affliction and my suffering, and take away all my sins, O my God.
To You, I lift up my soul, O Lord. In You, O my God, I trust; let me not be put to shame.
}
% 
\newcommand{\collect}{%
  \l{%
Protéctor in te sperántium, Deus, sine quo nihil est válidum, nihil sanctum: multíplica super nos misericórdiam tuam; ut, te rectóre, te duce, sic transeámus per bona temporália, ut non amittámus ætérna.
  }
  \e{%
O God, protector of all who hope in You, without Whom nothing is strong, nothing is holy, increase Your mercy toward us, that, with Your guidance and direction we may so pass through the things of this temporal life as not to lose those of life eternal.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
Caríssimi: Humiliámini sub poténti manu Dei, ut vos exáltet in témpore visitatiónis: omnem sollicitúdinem vestram proiiciéntes in eum, quóniam ipsi cura est de vobis. Sóbrii estote et vigiláte: quia adversárius vester diábolus tamquam leo rúgiens circuit, quærens, quem dévoret: cui resístite fortes in fide: sciéntes eándem passiónem ei, quæ in mundo est, vestræ fraternitáti fíeri. Deus autem omnis grátiæ, qui vocávit nos in ætérnam suam glóriam in Christo Iesu, módicum passos ipse perfíciet, confirmábit solidabítque. Ipsi glória et impérium in sǽcula sæculórum. 
  }
  \e{%
Beloved: Humble yourselves under the mighty hand of God, that He may exalt you in the time of visitation; cast all your anxiety upon Him, because He cares for you. Be sober, be watchful! For your adversary the devil, as a roaring lion, goes about seeking someone to devour. Resist him, steadfast in the faith, knowing that the same suffering befalls your brethren all over the world. But the God of all grace, Who has called us unto His eternal glory in Christ Jesus, will Himself, after we have suffered a little while, perfect, strengthen and establish us. To Him is the glory and the dominion forever and ever. Amen.
  }
}

% 
\newcommand{\gradual}{%
Iacta cogitátum tuum in Dómino: et ipse te enútriet.
Dum clamárem ad Dóminum, exaudívit vocem meam ab his, qui appropínquant mihi. Allelúia, allelúia.
Deus iudex iustus, fortis et pátiens, numquid iráscitur per síngulos dies? Allelúia.
}
\newcommand{\gradualTranslation}{%
Cast your care upon the Lord, and He will support you.
When I called upon the Lord, He heard my voice from those who war against me. Alleluia, alleluia.
A just judge is God, strong and patient; is He angry every day? Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Erant appropinquántes ad Iesum publicáni et peccatóres, ut audírent illum. Et murmurábant pharisǽi et scribæ, dicéntes: Quia hic peccatóres recipit et mandúcat cum illis. Et ait ad illos parábolam istam, dicens: Quis ex vobis homo, qui habet centum oves: et si perdíderit unam ex illis, nonne dimíttit nonagínta novem in desérto, et vadit ad illam, quæ períerat, donec invéniat eam? Et cum invénerit eam, impónit in húmeros suos gaudens: et véniens domum, cónvocat amícos et vicínos, dicens illis: Congratulámini mihi, quia invéni ovem meam, quæ períerat? Dico vobis, quod ita gáudium erit in cœlo super uno peccatóre pœniténtiam agénte, quam super nonagínta novem iustis, qui non índigent pœniténtia. Aut quæ múlier habens drachmas decem, si perdíderit drachmam unam, nonne accéndit lucérnam, et evérrit domum, et quærit diligénter, donec invéniat? Et cum invénerit, cónvocat amícas et vicínas, dicens: Congratulámini mihi, quia invéni drachmam, quam perdíderam? Ita dico vobis: gáudium erit coram Angelis Dei super uno peccatóre pœniténtiam agénte.
  }
  \e{%
At that time, the publicans and sinners were drawing near to Him to listen to Him. And the Pharisees and the Scribes murmured, saying, This man welcomes sinners and eats with them. But He spoke to them this parable, saying, What man of you having a hundred sheep, and losing one of them, does not leave the ninety-nine in the desert, and go after that which is lost, until he finds it? And when he has found it, he lays it upon his shoulders rejoicing. And on coming home he calls together his friends and neighbors, saying to them, ‘Rejoice with me, because I have found my sheep that was lost.’ I say to you that, even so, there will be joy in heaven over one sinner who repents, more then over ninety-nine just who have no need of repentance. Or what woman, having ten drachmas, if she loses one drachma, does not light a lamp and sweep the house and search carefully until she finds it? And when she has found it, she calls together her friends and neighbors, saying, ‘Rejoice with me, for I have found the drachma that I had lost.’ Even so, I say to you, there will be joy among the angels of God over one sinner who repents.
  }
}
\newcommand{\offertory}{%
Sperent in te omnes, qui novérunt nomen tuum, Dómine: quóniam non derelínquis quæréntes te: psállite Dómino, qui hábitat in Sion: quóniam non est oblítus oratiónem páuperum.
}
\newcommand{\offertoryTranslation}{%
They trust in You who cherish Your name, O Lord, for You forsake not those who seek You. Sing praise to the Lord enthroned in Sion, for He has not forgotten the cry of the afflicted.
}
\newcommand{\secret}{%
  \l{%
Réspice, Dómine, múnera supplicántis Ecclésiæ: et salúti credéntium perpétua sanctificatióne suménda concéde.
  }
  \e{%
Look favorably, O Lord, upon the offerings of Your prayerful Church and grant that those who believe may, in continual holiness, partake of them for their salvation.
  }
  \perDominum
}
\newcommand{\communion}{%
Dico vobis: gáudium est Angelis Dei super uno peccatóre pœniténtiam agénte.
}
\newcommand{\communionTranslation}{%
I say to you: there is joy among the angels of God over one sinner who repents.
}
\newcommand{\postcommunion}{%
  \l{%
Sancta tua nos, Dómine, sumpta vivíficent: et misericórdiæ sempitérnæ prǽparent expiátos.
  }
  \e{%
May the holy things of which we have partaken bring us to life and prepare for Your everlasting mercy those whom You have cleansed from sin.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}

\newcommand{\itePath}{../Ordinaries/masses/11/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
