% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica IX Post Pentecosten}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Ecce, Deus adiuvat me, et Dóminus suscéptor est ánimæ meæ: avérte mala inimícis meis, et in veritáte tua dispérde illos, protéctor meus, Dómine.
Deus, in nómine tuo salvum me fac: et in virtúte tua libera me.
}
\newcommand{\introitTranslation}{%
Behold, God is my helper, the Lord sustains my life. Turn back the evil upon my foes; in Your faithfulness destroy them, O Lord, my protector.
O God, by Your name save me, and by Your might deliver me.
}
% 
\newcommand{\collect}{%
  \l{%
Páteant aures misericórdiæ tuæ, Dómine, précibus supplicántium: et, ut peténtibus desideráta concédas; fac eos quæ tibi sunt plácita, postuláre.
  }
  \e{%
May Your merciful ears be open, O Lord, to the prayers of those who humbly entreat You; grant that they may ask for what pleases You so that You may fulfill their desires.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
Fratres: Non simus concupiscéntes malórum, sicut et illi concupiérunt. Neque idolólatræ efficiámini, sicut quidam ex ipsis: quemádmodum scriptum est: Sedit pópulus manducáre et bíbere, et surrexérunt lúdere. Neque fornicémur, sicut quidam ex ipsis fornicáti sunt, et cecidérunt una die vigínti tria mília. Neque tentémus Christum, sicut quidam eórum tentavérunt, et a serpéntibus periérunt. Neque murmuravéritis, sicut quidam eórum murmuravérunt, et periérunt ab exterminatóre. Hæc autem ómnia in figúra contingébant illis: scripta sunt autem ad correptiónem nostram, in quos fines sæculórum devenérunt. Itaque qui se exístimat stare, vídeat ne cadat. Tentátio vos non apprehéndat, nisi humána: fidélis autem Deus est, qui non patiétur vos tentári supra id, quod potéstis, sed fáciet étiam cum tentatióne provéntum, ut póssitis sustinére.
  }
  \e{%
Brethren: We should not lust after evil things even as they lusted. And do not become idolaters, even as some of them were, as it is written, The people sat down to eat and drink, and rose up to play. Neither let us commit fornication, even as some of them committed fornication, and there fell in one day twenty-three thousand. Neither let us tempt Christ, as some of them tempted, and perished by the serpents. Neither murmur, as some of them murmured, and perished at the hands of the destroyer. Now all these things happened to them as a type, and they were written for our correction, upon whom the final age of the world has come. Therefore let him who thinks he stands take heed lest he fall. May no temptation take hold of you but such as man is equal to. God is faithful and will not permit you to be tempted beyond your strength, but with the temptation will also give you a way out that you may be able to bear it.
  }
}

% 
\newcommand{\gradual}{%
Dómine, Dóminus noster, quam admirábile est nomen tuum in universa terra!
Quóniam eleváta est magnificéntia tua super cœlos.
Allelúia, allelúia.
Eripe me de inimícis meis, Deus meus: et ab insurgéntibus in me líbera me. Allelúia.
}
\newcommand{\gradualTranslation}{%
O Lord, our Lord, how glorious is Your name over all the earth!
You have elevated Your Majesty above the heavens.
Alleluia, alleluia.
Rescue me from my enemies, O my God; from my adversaries defend me. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Cum appropinquáret Iesus Ierúsalem, videns civitátem, flevit super illam, dicens: Quia si cognovísses et tu, et quidem in hac die tua, quæ ad pacem tibi, nunc autem abscóndita sunt ab óculis tuis. Quia vénient dies in te: et circúmdabunt te inimíci tui vallo, et circúmdabunt te: et coangustábunt te úndique: et ad terram prostérnent te, et fílios tuos, qui in te sunt, et non relínquent in te lápidem super lápidem: eo quod non cognóveris tempus visitatiónis tuæ. Et ingréssus in templum, cœpit eiícere vendéntes in illo et eméntes, dicens illis: Scriptum est: Quia domus mea domus oratiónis est. Vos autem fecístis illam speluncam latrónum. Et erat docens cotídie in templo.
  }
  \e{%
At that time, when Jesus drew near to Jerusalem and saw the city, He wept over it, saying, If you had known, in this your day, even you, the things that are for your peace! But now they are hidden from your eyes. For days will come upon you when your enemies will throw up a rampart about you, and surround you and shut you in on every side, and will dash you to the ground and your children within you, and will not leave in you one stone upon another, because you have not known the time of your visitation. And He entered the temple, and began to cast out those who were selling and buying in it, saying to them, It is written, ‘My house is a house of prayer,’ but you have made it a den of thieves. And He was teaching daily in the temple.
  }
}
\newcommand{\offertory}{%
Iustítiæ Dómini rectæ, lætificántes corda, et iudícia eius dulcióra super mel et favum: nam et servus tuus custódit ea.
}
\newcommand{\offertoryTranslation}{%
The precepts of the Lord are right, rejoicing the heart, and His ordinances sweeter than syrup or honey from the comb; therefore Your servant is careful of them.
}
\newcommand{\secret}{%
  \l{%
Concéde nobis, quǽsumus, Dómine, hæc digne frequentáre mystéria: quia, quóties huius hóstiæ commemorátio celebrátur, opus nostræ redemptiónis exercétur.
  }
  \e{%
Grant us, we beseech You, O Lord, to take part worthily and frequently in this sacramental action: for as often as this sacrifice of commemoration is offered, the work of our redemption is performed.
  }
  \perDominum
}
\newcommand{\communion}{%
Qui mandúcat meam carnem et bibit meum sánguinem, in me manet et ego in eo, dicit Dóminus.
}
\newcommand{\communionTranslation}{%
He who eats My Flesh, and drinks My Blood, abides in Me, and I in him, says the Lord.
}
\newcommand{\postcommunion}{%
  \l{%
Tui nobis, quǽsumus, Dómine, commúnio sacraménti, et purificatiónem cónferat, et tríbuat unitátem.
  }
  \e{%
May the partaking of Your sacrament, we beseech You, O Lord, cleanse us and unite us.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}

\newcommand{\itePath}{../Ordinaries/masses/11/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
