% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{In Vigilia Nativitatis Domini}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
  Hódie sciétis, quia véniet Dóminus et salvábit nos: et mane vidébitis glóriam eius.
  Dómini est terra, et plenitúdo eius: orbis terrárum, et univérsi, qui hábitant in eo.
}
\newcommand{\introitTranslation}{%
}
% 
\newcommand{\collect}{%
  \l{%
    Deus, qui nos redemptiónis nostræ ánnua exspectatióne lætíficas: præsta; ut Unigénitum tuum, quem Redemptórem læti suscípimus, veniéntem quoque Iúdicem secúri videámus, Dóminum nostrum Iesum Christum, Fílium tuum:
  }
  \e{%
    O God, You Who gladden us year after year with the expectation of our redemption, grant that we, who now welcome with joy Your only-begotten Son as our Redeemer, may also gaze upon Him without fear when He comes as our judge, our Lord Jesus Christ.
  }
  \l{
    Qui tecum vivit et regnat in unitáte Spíritus Sancti Deus per ómnia sǽcula sæculórum.
  }
  \e{
    Who livest and reignest with God the Father, in the unity of the Holy Spirit, God, world without end.
  }
  \amen
}
\newcommand{\lesson}{%
  \l{%
    Paulus, servus Iesu Christi, vocátus Apóstolus, segregátus in Evangélium Dei, quod ante promíserat per Prophétas suos in Scriptúris sanctis de Fílio suo, qui factus est ei ex sémine David secúndum carnem: qui prædestinátus est Fílius Dei in virtúte secúndum spíritum sanctificatiónis ex resurrectióne mortuórum Iesu Christi, Dómini nostri: per quem accépimus grátiam, et apostolátum ad obœdiéndum fídei in ómnibus géntibus pro nómine eius, in quibus estis et vos vocáti Iesu Christi, Dómini nostri.
  }
  \e{%
    Paul, the servant of Jesus Christ, called to be an Apostle, set apart for the Gospel of God, which He had promised before-hand through His prophets in the Holy Scriptures, concerning His Son Who was born to Him according to the flesh of the offspring of David; Who was foreordained Son of God by an act of power in keeping with the holiness of His spirit, by resurrection from the dead, Jesus Christ our Lord, through Whom we have received the grace of apostleship to bring about obedience to faith among all the nations for His name’s sake; among whom are you also called to be Jesus Christ’s, our Lord.
  }
}

% 
\newcommand{\gradual}{%
  Hódie sciétis, quia véniet Dóminus et salvábit nos: et mane vidébitis glóriam eius.
  \v~Qui regis Israël, inténde: qui dedúcis, velut ovem, Ioseph: qui sedes super Chérubim, appáre coram Ephraim, Béniamin, et Manásse. Allelúia, allelúia.
  \v~Crástina die delébitur iníquitas terræ: et regnábit super nos Salvátor mundi. Allelúia.
}
\newcommand{\gradualTranslation}{%
  This day you shall know that the Lord will come and save us: and in the morning you shall see His glory.
  \v~O Shepherd of Israel, hearken, O Guide of the flock of Joseph! From Your throne upon the Cherubim, shine forth before Ephraim, Benjamin and Manasse. Allelúja, allelúja.
  \v~On the morrow * the sins of the earth shall be washed away, and the Saviour of the world will be our King. Allelúja.
}
% 
\newcommand{\gospel}{%
  \l{%
    Cum esset desponsáta Mater Iesu Maria Ioseph, ántequam convenírent, inventa est in útero habens de Spiritu Sancto. Ioseph autem, vir eius, cum esset iustus et nollet eam tradúcere, vóluit occúlte dimíttere eam. Hæc autem eo cogitánte, ecce, Angelus Dómini appáruit in somnis ei, dicens: Ioseph, fili David, noli timére accípere Maríam cóniugem tuam: quod enim in ea natum est, de Spíritu Sancto est. Páriet autem fílium, et vocábis nomen eius Iesum: ipse enim salvum fáciet pópulum suum a peccátis eórum.
  }
  \e{%
    When Mary, the Mother of Jesus, has been betrothed to Joseph, before they came together, she was found to be with child by the Holy Spirit. But Joseph her husband, being a just man, and not wishing to expose her to reproach, was minded to put her away privately. But while he thought on these things, behold, an angel of the Lord appeared to him in a dream, saying, Do not be afraid, Joseph, son of David, to take to you Mary your wife, for that which is begotten in her is of the Holy Spirit. And she shall bring forth a Son, and you shall call His name Jesus; for He shall save His people from their sins.
  }
}
\newcommand{\offertory}{%
  Tóllite portas, principes, vestras: et elevámini, portæ æternáles, et introíbit Rex glóriæ.
}
\newcommand{\offertoryTranslation}{%
  Lift up, O gates, your lintels; reach up, you ancient portals, that the King of glory may come in.
}
\newcommand{\secret}{%
  \l{%
    Da nobis, quǽsumus, omnípotens Deus: ut, sicut adoránda Fílii tui natalítia prævenímus, sic eius múnera capiámus sempitérna gaudéntes:
  }
  \e{%
    Grant us, we beseech You, almighty God, that, as we anticipate the celebration of Your Son’s birthday, so we may joyfully receive His everlasting gifts.
  }
  \l{
    Qui tecum vivit et regnat in unitáte Spíritus Sancti Deus per ómnia sǽcula sæculórum.
  }
  \e{
    Who livest and reignest with God the Father, in the unity of the Holy Spirit, God, world without end.
  }
  \amen
}
\newcommand{\communion}{%
  Revelábitur glória Dómini: et vidébit omnis caro salutáre Dei nostri.
}
\newcommand{\communionTranslation}{%
  The glory of the Lord shall be revealed, and all mankind shall see the salvation of our God.
}
\newcommand{\postcommunion}{%
  \l{%
    Da nobis, quǽsumus, Dómine: unigéniti Fílii tui recensíta nativitáte respiráre; cuius cœlésti mystério páscimur et potámur.
  }
  \e{%
    Grant us, we beseech You, O Lord, to begin a new life with this commemoration of the birth of Your only-begotten Son, Who gives us food and drink in His heavenly sacrament.
  }
  \l{
    Per eúndem Dóminum nostrum Iesum Christum Fílium tuum, qui tecum vivit et regnat in unitáte Spíritus Sancti, Deus, per ómnia sǽcula sæculórum.
  }
  \e{
    Through the same Jesus Christ, thy Son, Our Lord, Who liveth and reigneth with thee in the unity of the Holy Ghost, God, world without end. 
  }
  \amen
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../Ordinaries/masses/17/kyrie}
\newcommand{\gloriaPath}{../Ordinaries/masses/17/gloria}
\newcommand{\sanctusPath}{../Ordinaries/masses/17/sanctus}
\newcommand{\agnusPath}{../Ordinaries/masses/17/agnus}
\newcommand{\itePath}{../Ordinaries/masses/17/ite}
% 
\newcommand{\creedPath}{../Ordinaries/credo/1/credo}
% 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
