% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica infra Octavam Ascensionis}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Exáudi, Dómine, vocem meam, qua clamávi ad te, allelúia: tibi dixit cor meum, quæsívi vultum tuum, vultum tuum, Dómine, requíram: ne avértas fáciem tuam a me, allelúia, allelúia.
Dóminus illuminátio mea et salus mea: quem timébo?
}
\newcommand{\introitTranslation}{%
Hear, O Lord, the sound of my call, alleluia; to You my heart speaks; Your glance I seek; Your presence, O Lord, I seek. Hide not Your face from me, alleluia, alleluia.
The Lord is my light and my salvation; whom should I fear?
}
% 
\newcommand{\collect}{%
  \l{%
Omnípotens sempitérne Deus: fac nos tibi semper et devótam gérere voluntátem; et maiestáti tuæ sincéro corde servíre.
  }
  \e{%
Almighty and eternal God, give us a will ever dedicated to You, and a true heart to serve Your majesty.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
Caríssimi: Estóte prudéntes et vigiláte in oratiónibus. Ante ómnia autem mútuam in vobismetípsis caritátem contínuam habéntes: quia cáritas óperit multitúdinem peccatórum. Hospitáles ínvicem sine murmuratióne: unusquísque, sicut accépit grátiam, in altérutrum illam administrántes, sicut boni dispensatóres multifórmis grátiæ Dei. Si quis lóquitur, quasi sermónes Dei: si quis minístrat, tamquam ex virtúte, quam adminístrat Deus: ut in ómnibus honorificétur Deus per Iesum Christum, Dóminum nostrum.
  }
  \e{%
Beloved: Be prudent and watchful in prayers. But above all things have a constant mutual charity among yourselves: for charity covers a multitude of sins. Be hospitable to one another without murmuring. According to the gift that each has received, minister it to one another as good stewards of the manifold grace of God. If anyone speaks, let it be as with words of God. If anyone ministers, let it be as from the strength that God furnishes; that in all things God may be honored through Jesus Christ our Lord.
  }
}

% 
\newcommand{\gradual}{%
Allelúia, allelúia.
Regnávit Dóminus super omnes gentes: Deus sedet super sedem sanctam suam. Allelúia.
Non vos relínquam órphanos: vado, et vénio ad vos, et gaudébit cor vestrum. Allelúia.
}
\newcommand{\gradualTranslation}{%
Alleluia, alleluia.
The Lord reigns over all the nations, God sits upon His holy throne. Alleluia.
I will not leave you orphans; I go away and I come to you, and your heart shall rejoice. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Dixit Iesus discípulis suis: Cum vénerit Paráclitus, quem ego mittam vobis a Patre, Spíritum veritátis, qui a Patre procédit, ille testimónium perhibébit de me: et vos testimónium perhibébitis, quia ab inítio mecum estis. Hæc locútus sum vobis, ut non scandalizémini. Absque synagógis fácient vos: sed venit hora, ut omnis, qui intérficit vos, arbitrétur obséquium se præstáre Deo. Et hæc fácient vobis, quia non novérunt Patrem neque me. Sed hæc locútus sum vobis: ut, cum vénerit hora eórum, reminiscámini, quia ego dixi vobis.
  }
  \e{%
At that time, Jesus said to His disciples: When the Advocate has come, Whom I will send you from the Father, the Spirit of truth Who proceeds from the Father, He will bear witness concerning Me. And you also will bear witness, because from the beginning you are with Me. These things I have spoken to you that you may not be scandalized. They will expel you from the synagogues. Yes, the hour is coming for everyone who kills you to think he is offering worship to God. And these things they will do because they have not known the Father nor Me. But these things I have spoken to you, that when the time for them has come you may remember that I told you.
  }
}
\newcommand{\offertory}{%
Ascéndit Deus in iubilatióne, et Dóminus in voce tubæ, allelúia.
}
\newcommand{\offertoryTranslation}{%
God mounts His throne amid shouts of joy; the Lord, amid trumpet blasts. Alleluia.
}
\newcommand{\secret}{%
  \l{%
Sacrifícia nos, Dómine, immaculáta puríficent: et méntibus nostris supérnæ grátiæ dent vigórem.
  }
  \e{%
May this pure sacrifice cleanse us, O Lord, and impart to our minds the strength of heavenly grace.
  }
  \perDominum
}
\newcommand{\communion}{%
Pater, cum essem cum eis, ego servábam eos, quos dedísti mihi, allelúia: nunc autem ad te vénio: non rogo, ut tollas eos de mundo, sed ut serves eos a malo, allelúia, allelúia.
}
\newcommand{\communionTranslation}{%
Father, while I was with them, I kept them whom You have given Me, alleluia; but now I am coming to You; I do not pray that You take them out of the world, but that You keep them from evil, alleluia, alleluia.
}
\newcommand{\postcommunion}{%
  \l{%
Repléti, Dómine, munéribus sacris: da, quǽsumus; ut in gratiárum semper actióne maneámus.
  }
  \e{%
We who have been filled with heavenly gifts beseech You, O Lord, grant us to continue giving thanks to You.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/vidi-aquam}

\newcommand{\kyriePath}{../Ordinaries/masses/1/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/1/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/1/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/1/agnus}

\newcommand{\itePath}{../Ordinaries/masses/1/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/regina-caeli}
\input{../MarianAntiphons/regina-caeli_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
