% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica VI Post Epiphaniam}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Adoráte Deum, omnes Angeli ejus: audívit, et lætáta est Sion: et exsultavérunt fíliæ Judæ.
Dóminus regnávit, exsúltet terra: læténtur ínsulæ multæ. 
}
\newcommand{\introitTranslation}{%
Adore God, all you His angels: Sion hears and is glad, and the cities of Juda rejoice.
The Lord is King; let the earth rejoice; let the many isles be glad.
}
% 
\newcommand{\collect}{%
  \l{%
Præsta, quǽsumus, omnípotens Deus: ut, semper rationabília meditántes, quæ tibi sunt plácita, et dictis exsequámur et factis.
  }
  \e{%
Grant us, we beseech You, almighty God, ever to think of spiritual things and in every word and work always to do what is well pleasing in Your sight.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
Fratres: Grátias ágimus Deo semper pro ómnibus vobis, memóriam vestri faciéntes in oratiónibus nostris sine intermissióne, mémores óperis fídei vestræ, et labóris, et caritátis, et sustinéntiæ spei Dómini nostri Jesu Christi, ante Deum et Patrem nostrum: sciéntes, fratres, dilécti a Deo. electiónem vestram: quia Evangélium nostrum non fuit ad vos in sermóne tantum, sed et in virtúte, et in Spíritu Sancto, et in plenitúdine multa, sicut scitis quales fuérimus in vobis propter vos. Et vos imitatóres nostri facti estis, et Dómini, excipiéntes verbum in tribulatióne multa, cum gáudio Spíritus Sancti: ita ut facti sitis forma ómnibus credéntibus in Macedónia et in Achája. A vobis enim diffamátus est sermo Dómini, non solum in Macedónia et in Achája, sed et in omni loco fides vestra, quæ est ad Deum, profécta est, ita ut non sit nobis necésse quidquam loqui. Ipsi enim de nobis annúntiant, qualem intróitum habuérimus ad vos: et quómodo convérsi estis ad Deum a simulácris, servíre Deo vivo et vero, et exspectáre Fílium ejus de cœlis quem suscitávit ex mórtuis Jesum, qui erípuit nos ab ira ventúra.
  }
  \e{%
Brethren: We give thanks to God always for you all, continually making a remembrance of you in our prayers; being mindful before God our Father of your work of faith, and labor, and charity, and your enduring hope in our Lord Jesus Christ. We know, brethren, beloved of God, how you were chosen. For our Gospel was not delivered to you in word only, but in power also, and in the Holy Spirit, and in much fullness, as indeed you know what manner of men we have been among you for your sakes. And you became imitators of us and of the Lord, receiving the word in great tribulation, with joy of the Holy Spirit, so that you became a pattern to all the believers in Macedonia and in Achaia. For from you the word of the Lord has been spread abroad, not only in Macedonia and Achaia, but in every place your faith in God has gone forth, so that we need say nothing further. For they themselves report concerning us how we entered among you, and how you turned to God from idols, to serve the living and true God, and to await from heaven Jesus, His Son, Whom He raised from the dead, Who has delivered us from the wrath to come.
  }
}

% 
\newcommand{\gradual}{%
Timébunt gentes nomen tuum, Dómine, et omnes reges terræ glóriam tuam.
Quóniam ædificávit Dóminus Sion, et vidébitur in majestáte sua. Allelúja, allelúja.
Dóminus regnávit, exsúltet terra: læténtur ínsulæ multæ. Allelúja.
}
\newcommand{\gradualTranslation}{%
The nations shall revere Your name, O Lord, and all the kings of the earth Your glory.
For the Lord has rebuilt Sion, and He shall appear in His glory. Alleluia, alleluia.
The Lord is King; let the earth rejoice; let the many isles be glad.  Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Dixit Jesus turbis parábolam hanc: Símile est regnum cœlórum grano sinápis, quod accípiens homo seminávit in agro suo: quod mínimum quidem est ómnibus semínibus: cum autem créverit, majus est ómnibus oléribus, et fit arbor, ita ut vólucres cœli véniant et hábitent in ramis ejus. Aliam parábolam locútus est eis: Símile est regnum cœlórum ferménto, quod accéptum múlier abscóndit in farínæ satis tribus, donec fermentátum est totum. Hæc ómnia locútus est Jesus in parábolis ad turbas: et sine parábolis non loquebátur eis: ut implerétur quod dictum erat per Prophétam dicéntem: Apériam in parábolis os meum, eructábo abscóndita a constitutióne mundi.
  }
  \e{%
At that time, Jesus spoke this parable to the crowds: The kingdom of heaven is like a grain of mustard seed, which a man took and sowed in his field. This indeed is the smallest of all the seeds; but when it grows up it is larger than any herb and becomes a tree, so that the birds of the air come and dwell in its branches. He told them another parable: The kingdom of heaven is like leaven, which a woman took and buried in three measures of flour, until all of it was leavened. All these things Jesus spoke to the crowds in parables, and without parables he did not speak to them; that what was spoken by the prophet might be fulfilled, I will open My mouth in parables, I will utter things hidden since the foundation of the world.
  }
}
\newcommand{\offertory}{%
Déxtera Dómini fecit virtutem, déxtera Dómini exaltávit me: non móriar, sed vivam, et narrábo ópera Dómini.
}
\newcommand{\offertoryTranslation}{%
The right hand of the Lord has struck with power: the right hand of the Lord has exalted me; I shall not die, but live, and declare the works of the Lord.
}
\newcommand{\secret}{%
  \l{%
Hæc nos oblátio, Deus, mundet, quǽsumus, et rénovet, gubérnet et prótegat.
  }
  \e{%
May this offering, O God, we beseech You, cleanse and renew us, govern and protect us.
  }
  \perDominum
}
\newcommand{\communion}{%
Mirabántur omnes de his, quæ procedébant de ore Dei.
}
\newcommand{\communionTranslation}{%
All marvelled at the words that came from the mouth of God.
}
\newcommand{\postcommunion}{%
  \l{%
Cœléstibus, Dómine, pasti delíciis: quǽsumus; ut semper éadem, per quæ veráciter vívimus, appétimus.
  }
  \e{%
Nourished by Your heavenly food, O Lord, we beseech You that we may always strive after those things that give us true life.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/4/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/4/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/4/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/4/agnus}

\newcommand{\itePath}{../Ordinaries/masses/4/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
