% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica in Albis}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Quasi modo géniti infántes, allelúia: rationábiles, sine dolo lac concupíscite, allelúia, allelúia, allelúia.
Exsultáte Deo, adiutóri nostro: iubiláte Deo Iacob.
}
\newcommand{\introitTranslation}{%
As newborn babes, alleluia, desire the rational milk without guile, alleluia, alleluia, alleluia.
Rejoice to God our Helper; sing aloud to the God of Jacob.
}
% 
\newcommand{\collect}{%
  \l{%
Præsta, quǽsumus, omnípotens Deus: ut, qui paschália festa perégimus, hæc, te largiénte, móribus et vita teneámus.
  }
  \e{%
Grant, we beseech Thee, almighty God, that we who have celebrated the Paschal Feast, may, by Thy bounty, retain its fruits in our daily habits and behavior.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
Caríssimi: Omne, quod natum est ex Deo, vincit mundum: et hæc est victória, quæ vincit mundum, fides nostra. Quis est, qui vincit mundum, nisi qui credit, quóniam Iesus est Fílius Dei? Hic est, qui venit per aquam et sánguinem, Iesus Christus: non in aqua solum, sed in aqua et sánguine. Et Spíritus est, qui testificátur, quóniam Christus est véritas. Quóniam tres sunt, qui testimónium dant in cœlo: Pater, Verbum, et Spíritus Sanctus: et hi tres unum sunt. Et tres sunt, qui testimónium dant in terra: Spíritus, et aqua, et sanguis: et hi tres unum sunt. Si testimónium hóminum accípimus, testimónium Dei maius est: quóniam hoc est testimónium Dei, quod maius est: quóniam testificátus est de Fílio suo. Qui credit in Fílium Dei, habet testimónium Dei in se.
  }
  \e{%
Dearly beloved, Whatsoever is born of God overcometh the world: and this is the victory, which overcometh the world, our faith. Who is he that overcometh the world, but he that believeth that Jesus is the Son of God? This is He that came by water and blood, Jesus Christ: not by water only, but by water and blood. And it is the Spirit which testifieth that Christ is the truth. And there are three who give testimony in heaven: the Father, the Word and the Holy Ghost: and these three are one. And there are three that give testimony on earth: the Spirit and the water and the blood; and these three are one. If we receive the testimony of men, the testimony of God is greater: for this is the testimony of God, which is greater, because He hath testified of His Son. He that believeth in the Son of God hath the testimony of God in himself.
  }
}

% 
\newcommand{\gradual}{%
Allelúia, allelúia.
In die resurrectiónis meæ, dicit Dóminus, præcédam vos in Galilǽam. Allelúia.
Post dies octo, iánuis clausis, stetit Iesus in médio discipulórum suórum, et dixit: Pax vobis. Allelúia.
}
\newcommand{\gradualTranslation}{%
Alleluia, alleluia.
On the day of My Resurrection, saith the Lord, I will go before you into Galilee. Alleluia.
After eight days, the doors being shut, Jesus stood in the midst of His disciples and said: Peace be to you. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Cum sero esset die illo, una sabbatórum, et fores essent clausæ, ubi erant discípuli congregáti propter metum Iudæórum: venit Iesus, et stetit in médio, et dixit eis: Pax vobis. Et cum hoc dixísset, osténdit eis manus et latus. Gavísi sunt ergo discípuli, viso Dómino. Dixit ergo eis íterum: Pax vobis. Sicut misit me Pater, et ego mitto vos. Hæc cum dixísset, insufflávit, et dixit eis: Accípite Spíritum Sanctum: quorum remiséritis peccáta, remittúntur eis; et quorum retinuéritis, reténta sunt. Thomas autem unus ex duódecim, qui dícitur Dídymus, non erat cum eis, quando venit Iesus. Dixérunt ergo ei álii discípuli: Vídimus Dóminum. Ille autem dixit eis: Nisi vídero in mánibus eius fixúram clavórum, et mittam dígitum meum in locum clavórum, et mittam manum meam in latus eius, non credam. Et post dies octo, íterum erant discípuli eius intus, et Thomas cum eis. Venit Iesus, iánuis clausis, et stetit in médio, et dixit: Pax vobis. Deínde dicit Thomæ: Infer dígitum tuum huc et vide manus meas, et affer manum tuam et mitte in latus meum: et noli esse incrédulus, sed fidélis. Respóndit Thomas et dixit ei: Dóminus meus et Deus meus. Dixit ei Iesus: Quia vidísti me, Thoma, credidísti: beáti, qui non vidérunt, et credidérunt. Multa quidem et ália signa fecit Iesus in conspéctu discipulórum suórum, quæ non sunt scripta in libro hoc. Hæc autem scripta sunt, ut credátis, quia Iesus est Christus, Fílius Dei: et ut credéntes vitam habeátis in nómine eius.
  }
  \e{%
At that time, when it was late that same day, the first of the week, and the doors were shut, where the disciples were gathered together for fear of the Jews, Jesus came, and stood in the midst and said to them: Peace be to you. And when He had said this, He showed them His hands and His side. The disciples therefore were glad, when they saw the Lord. He said therefore to them again: Peace be to you. As the Father hath sent Me, I also send you. When He had said this, He breathed on them, and He said to them: Receive ye the Holy Ghost: whose sins you shall forgive, they are forgiven them; and whose sins you shall retain, they are retained. Now Thomas, one of the Twelve, who is called Didymus, was not with them when Jesus came. The other disciples therefore said to him: We have seen the Lord. But he said to them: Except I shall see in His hands the print of the nails, and put my finger into the place of the nails, and put my hand into His side, I will not believe. And after eight days, again His disciples were within, and Thomas with them. Jesus cometh, the doors being shut, and stood in the midst, and said: Peace be to you. Then He saith to Thomas: Put in thy finger hither, and see My hands, and bring hither thy hand, and put into My side; and be not faithless, but believing. Thomas answered and said to Him: my Lord and my God. Jesus saith to him: Because thou hast seen Me, Thomas, thou hast believed; blessed are they that have not seen, and have believed. Many other signs also did Jesus in the sight of His disciples, which are not written in this book. But these are written, that you may believe that Jesus is the Christ, the Son of God; and that, believing, you may have life in His Name.
  }
}
\newcommand{\offertory}{%
Angelus Dómini descéndit de cœlo, et dixit muliéribus: Quem quǽritis, surréxit, sicut dixit, allelúia.
}
\newcommand{\offertoryTranslation}{%
An Angel of the Lord descended from heaven, and said to the women; He whom you seek is risen, as He said. Alleluia.
}
\newcommand{\secret}{%
  \l{%
Súscipe múnera, Dómine, quǽsumus, exsultántis Ecclésiæ: et, cui causam tanti gáudii præstitísti, perpétuæ fructum concéde lætítiæ.
  }
  \e{%
Receive, we beseech Thee, O Lord, the gifts of Thine exultant Church: and to her whom Thou hast given cause for so great joy, grant the fruit of perpetual happiness.
  }
  \per
}
\newcommand{\communion}{%
Mitte manum tuam, et cognósce loca clavórum, allelúia: et noli esse incrédulus, sed fidélis, allelúia, allelúia.
}
\newcommand{\communionTranslation}{%
Put in thy hand, and know the place of the nails, alleluia; and be not faithless, but believing, alleluia, alleluia.
}
\newcommand{\postcommunion}{%
  \l{%
Quǽsumus, Dómine, Deus noster: ut sacrosáncta mystéria, quæ pro reparatiónis nostræ munímine contulísti; et præsens nobis remédium esse fácias et futúrum.
  }
  \e{%
We beseech Thee, O Lord, our God, to make the most holy Mysteries which Thou hast given us as a defense of our renewal, a remedy for us now, and in the future.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.


\newcommand{\kyriePath}{../Ordinaries/masses/1/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/1/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/1/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/1/agnus}

\newcommand{\itePath}{../Ordinaries/masses/1/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\vidiAquamPath}{../ToniCommunes/roman/vidi-aquam}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/regina-caeli}
\include{../MarianAntiphons/regina-caeli_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
