% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica X Post Pentecosten}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Dum clamárem ad Dóminum, exaudívit vocem meam, ab his, qui appropínquant mihi: et humiliávit eos, qui est ante sǽcula et manet in ætérnum: iacta cogitátum tuum in Dómino, et ipse te enútriet.
Exáudi, Deus, oratiónem meam, et ne despéxeris deprecatiónem meam: inténde mihi et exáudi me.
}
\newcommand{\introitTranslation}{%
When I call upon the Lord, He heard my voice, from those who war against me; and He humbled them, Who is before all ages, and remains forever: cast your care upon the Lord, and He will support you.
Hearken, O God, to my prayer; turn not away from my pleading; give heed to me, and answer me.
}
% 
\newcommand{\collect}{%
  \l{%
Deus, qui omnipoténtiam tuam parcéndo máxime et miserándo maniféstas: multíplica super nos misericórdiam tuam; ut, ad tua promíssa curréntes, cœléstium bonórum fácias esse consórtes.
  }
  \e{%
O God, You manifest Your power, particularly in forbearance and pity, show us Your mercy again and again, so that hastening toward Your promises we may become partakers of the blessings of heaven.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
Fratres: Scitis, quóniam, cum gentes essétis, ad simulácra muta prout ducebámini eúntes. Ideo notum vobisfacio, quod nemo in Spíritu Dei loquens, dicit anáthema Iesu. Et nemo potest dícere, Dóminus Iesus, nisi in Spíritu Sancto. Divisiónes vero gratiárum sunt, idem autem Spíritus. Et divisiónes ministratiónum sunt, idem autem Dóminus. Et divisiónes operatiónum sunt, idem vero Deus, qui operátur ómnia in ómnibus. Unicuíque autem datur manifestátio Spíritus ad utilitátem. Alii quidem per Spíritum datur sermo sapiéntiæ álii autem sermo sciéntiæ secúndum eúndem Spíritum: álteri fides in eódem Spíritu: álii grátia sanitátum in uno Spíritu: álii operátio virtútum, álii prophetía, álii discrétio spirítuum, álii génera linguárum, álii interpretátio sermónum. Hæc autem ómnia operátur unus atque idem Spíritus, dívidens síngulis, prout vult.
  }
  \e{%
Brethren: You know that when you were Gentiles, you went to dumb idols according as you were led. Wherefore I give you to understand that no one speaking in the Spirit of God, says Anathema to Jesus. And no one can say Jesus is Lord, except in the Holy Spirit. Now there are varieties of gifts, but the same Spirit; and there are varieties of ministries, but the same Lord; and there are varieties of workings, but the same God, Who works all things in all. Now the manifestation of the Spirit is given to everyone for profit. To one through the Spirit is given the utterance of wisdom; and to another the utterance of knowledge, according to the same Spirit; to another faith, in the same Spirit; to another the gift of healing, in the one Spirit; to another the working of miracles; to another prophecy; to another the distinguishing of spirits; to another various kinds of tongues; to another interpretation of tongues. But all these things are the work of one and the same Spirit, Who allots to everyone according as He will.
  }
}

% 
\newcommand{\gradual}{%
Custódi me, Dómine, ut pupíllam óculi: sub umbra alárum tuárum prótege me.
De vultu tuo iudícium meum pródeat: óculi tui vídeant æquitátem.
Allelúia, allelúia.
Te decet hymnus, Deus, in Sion: et tibi reddétur votum in Ierúsalem. Allelúia.
}
\newcommand{\gradualTranslation}{%
Keep me, O Lord, as the apple of Your eye; hide me in the shadow of Your wings.
From You let judgment come; Your eyes behold what is right. Alleluia, alleluia.
To You we owe our hymn of praise, O God, in Sion; to You must vows be fulfilled in Jerusalem. Alleluia
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Dixit Iesus ad quosdam, qui in se confidébant tamquam iusti et aspernabántur céteros, parábolam istam: Duo hómines ascendérunt in templum, ut orárent: unus pharisǽus, et alter publicánus. Pharisǽus stans, hæc apud se orábat: Deus, grátias ago tibi, quia non sum sicut céteri hóminum: raptóres, iniústi, adúlteri: velut étiam hic publicánus. Ieiúno bis in sábbato: décimas do ómnium, quæ possídeo. Et publicánus a longe stans nolébat nec óculos ad cœlum leváre: sed percutiébat pectus suum, dicens: Deus, propítius esto mihi peccatóri. Dico vobis: descéndit hic iustificátus in domum suam ab illo: quia omnis qui se exáltat, humiliábitur: et qui se humíliat, exaltábitur.
  }
  \e{%
At that time, Jesus spoke this parable to some who trusted in themselves as being just and despised others. Two men went up to the temple to pray, the one a Pharisee and the other a publican. The Pharisee stood and began to pray thus within himself: ‘O God, I thank You that I am not like the rest of men, robbers, dishonest, adulterers, or even like this publican. I fast twice a week; I pay tithes of all that I possess.’ But the publican, standing afar off, would not so much as lift up his eyes to heaven, but kept striking his breast, saying, ‘O God, be merciful to me the sinner!’ I tell you, this man went back to his home justified rather than the other; for everyone who exalts himself shall be humbled, and he who humbles himself shall be exalted.
  }
}
\newcommand{\offertory}{%
Ad te, Dómine, levávi ánimam meam: Deus meus, in te confído, non erubéscam: neque irrídeant me inimíci mei: étenim univérsi, qui te exspéctant, non confundéntur.
}
\newcommand{\offertoryTranslation}{%
To You I lift up my soul, O Lord. In You, O my God, I trust; let me not be put to shame, let not my enemies exult over me. No one who waits for You shall be put to shame.
}
\newcommand{\secret}{%
  \l{%
Tibi, Dómine, sacrifícia dicáta reddántur: quæ sic ad honórem nóminis tui deferénda tribuísti, ut eadem remédia fíeri nostra præstáres.
  }
  \e{%
Let the sacred gifts be offered to You, O Lord, Who have given them to be presented for the honor of Your name, for in them You have given us a remedy for all our ills.
  }
  \per
}
\newcommand{\communion}{%
Acceptábis sacrificium iustítiæ, oblatiónes et holocáusta, super altáre tuum, Dómine.
}
\newcommand{\communionTranslation}{%
  You shall be pleased with due sacrifices, burnt offerings and holocausts on Your altar, O Lord.
}
\newcommand{\postcommunion}{%
  \l{%
Quǽsumus, Dómine, Deus noster: ut, quos divínis reparáre non désinis sacraméntis, tuis non destítuas benígnus auxíliis.
  }
  \e{%
We beseech You, O Lord our God, that in Your mercy You will not withhold Your help from those whom You constantly restore with divine sacraments.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.


\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}

\newcommand{\itePath}{../Ordinaries/masses/11/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
