% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica I Passionis}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
  Iúdica me, Deus, et discérne causam meam de gente non sancta: ab hómine iníquo et dolóso éripe me: quia tu es Deus meus et fortitúdo mea.
  Emítte lucem tuam et veritátem tuam: ipsa me de duxérunt et adduxérunt in montem sanctum tuum et in tabernácula tua.
}
\newcommand{\introitTranslation}{%
  Judge me, O God, and fight my fight against a faithless people; from the deceitful and impious man rescue me. For You are my God and my strength.
  Send forth Your light and Your truth; they shall lead me on and bring me to Your holy mountain, to Your dwelling-place.
}
% 
\newcommand{\collect}{%
  \l{%
    Quǽsumus, omnípotens Deus, famíliam tuam propítius réspice: ut, te largiénte, regátur in córpore; et, te servánte, custodiátur in mente.
  }
  \e{%
    Look graciously upon Your household, almighty God, we beseech You, that by Your grace we may be governed in body, and by Your protection safeguarded in mind.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
    Fratres: Christus assístens Póntifex futurórum bonórum, per ámplius et perféctius tabernáculum non manufáctum, id est, non huius creatiónis: neque per sánguinem hircórum aut vitulórum, sed per próprium sánguinem introívit semel in Sancta, ætérna redemptióne invénta. Si enim sanguis hircórum et taurórum, et cinis vítulæ aspérsus, inquinátos sanctíficat ad emundatiónem carnis: quanto magis sanguis Christi, qui per Spíritum Sanctum semetípsum óbtulit immaculátum Deo, emundábit consciéntiam nostram ab opéribus mórtuis, ad serviéndum Deo vivénti? Et ídeo novi Testaménti mediátor est: ut, morte intercedénte, in redemptiónem eárum prævaricatiónum, quæ erant sub prióri Testaménto, repromissiónem accípiant, qui vocáti sunt ætérnæ hereditátis, in Christo Iesu, Dómino nostro.
  }
  \e{%
    Brethren: When Christ appeared as high priest of the good things to come, He entered once for all through the greater and more perfect tabernacle, not made by hands - that is, not of this creation, - nor again by virtue of blood of goats and calves, but by virtue of His own blood, into the Holies, having obtained eternal redemption. For if the blood of goats and bulls and the sprinkled ashes of a heifer sanctify the unclean unto the cleansing of the flesh, how much more will the Blood of Christ, Who through the Holy Spirit offered Himself unblemished unto God, cleanse your conscience from dead works to serve the living God? And this is why He is mediator of a new covenant, that whereas a death has taken place for redemption from the transgressions committed under the former covenant, they who have been called may receive eternal inheritance according to the promise, in Christ Jesus our Lord.
  }
}

% 
\newcommand{\gradual}{%
  Eripe me, Dómine, de inimícis meis: doce me fácere voluntátem tuam
  Liberátor meus, Dómine, de géntibus iracúndis: ab insurgéntibus in me exaltábis me: a viro iníquo erípies me.
  Sæpe expugnavérunt me a iuventúte mea.
  Dicat nunc Israël: sæpe expugnavérunt me a iuventúte mea.
  Etenim non potuérunt mihi: supra dorsum meum fabricavérunt peccatóres.
  Prolongavérunt iniquitátes suas: Dóminus iustus concídit cervíces peccatórum.
}
\newcommand{\gradualTranslation}{%
  Rescue me from my enemies, O Lord; teach me to do Your will.
  O Lord, my deliverer from the angry nations, truly above my adversaries You exalt me and from the violent man You have rescued me.
  Much have they oppressed me from my youth.
  Let Israel say: Much have they oppressed me from my youth.
  Yet they have not prevailed against me; upon my back the plowers plowed.
  Long did they make their furrows. But the just Lord has severed the cords of the wicked.
}
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Dicébat Iesus turbis Iudæórum: Quis ex vobis árguet me de peccáto? Si veritátem dico vobis, quare non créditis mihi? Qui ex Deo est, verba Dei audit. Proptérea vos non audítis, quia ex Deo non estis. Respondérunt ergo Iudǽi et dixérunt ei: Nonne bene dícimus nos, quia Samaritánus es tu, et dæmónium habes? Respóndit Iesus: Ego dæmónium non hábeo, sed honorífico Patrem meum, et vos inhonorástis me. Ego autem non quæro glóriam meam: est, qui quærat et iúdicet. Amen, amen, dico vobis: si quis sermónem meum serváverit, mortem non vidébit in ætérnum. Dixérunt ergo Iudǽi: Nunc cognóvimus, quia dæmónium habes. Abraham mórtuus est et Prophétæ; et tu dicis: Si quis sermónem meum serváverit, non gustábit mortem in ætérnum. Numquid tu maior es patre nostro Abraham, qui mórtuus est? et Prophétæ mórtui sunt. Quem teípsum facis? Respóndit Iesus: Si ego glorífico meípsum, glória mea nihil est: est Pater meus, qui gloríficat me, quem vos dícitis, quia Deus vester est, et non cognovístis eum: ego autem novi eum: et si díxero, quia non scio eum, ero símilis vobis, mendax. Sed scio eum et sermónem eius servo. Abraham pater vester exsultávit, ut vidéret diem meum: vidit, et gavísus est. Dixérunt ergo Iudǽi ad eum: Quinquagínta annos nondum habes, et Abraham vidísti? Dixit eis Iesus: Amen, amen, dico vobis, ántequam Abraham fíeret, ego sum. Tulérunt ergo lápides, ut iácerent in eum: Iesus autem abscóndit se, et exívit de templo.
  }
  \e{%
At that time, Jesus said to the crowds of the Jews: Which of you can convict Me of sin? If I speak the truth, why do you not believe Me? He who is of God hears the words of God. The reason why you do not hear is that you are not of God. The Jews therefore in answer said to Him, Are we not right in saying that You are a Samaritan, and have a devil? Jesus answered, I have not a devil, but I honor My Father, and you dishonor Me. Yet, I do not seek My own glory; there is One Who seeks and Who judges. Amen, amen, I say to you, if anyone keep My word, he will never see death. The Jews therefore said, Now we know that You have a devil. Abraham is dead, and the prophets, and You say, ‘If anyone keep My word he will never taste death.’ Are You greater than our father Abraham, who is dead? And the prophets are dead. Whom do You make Yourself? Jesus answered, If I glorify Myself, My glory is nothing. It is My Father Who glorifies Me, of Whom you say that He is your God. And you do not know Him, but I know Him. And if I say that I do not know Him, I shall be like you, a liar. But I know Him, and I keep His word. Abraham your father rejoiced that he was to see My day. He saw it and was glad. The Jews therefore said to Him, You are not yet fifty years old, and have You seen Abraham? Jesus said to them, Amen, amen, I say to you, before Abraham came to be, I am. They therefore took up stones to cast at Him; but Jesus hid Himself, and went out from the temple.
  }
}
\newcommand{\offertory}{%
  Confitébor tibi, Dómine, in toto corde meo: retríbue servo tuo: vivam, et custódiam sermónes tuos: vivífica me secúndum verbum tuum, Dómine.
}
\newcommand{\offertoryTranslation}{%
  I praise You, O Lord, with all my heart; be good to Your servant, that I may live and keep Your words. O Lord, give me life according to Your word.
}
\newcommand{\secret}{%
  \l{%
    Hæc múnera, quǽsumus Dómine, et víncula nostræ pravitátis absólvant, et tuæ nobis misericórdiæ dona concílient.
  }
  \e{%
    May these offerings, we beseech You, O Lord, loose the bonds of our wickedness, and obtain for us the gifts of Your mercy.
  }
  \perDominum
}
\newcommand{\communion}{%
  Hoc corpus, quod pro vobis tradétur: hic calix novi Testaménti est in meo sánguine, dicit Dóminus: hoc fácite, quotiescúmque súmitis, in meam commemoratiónem.
}
\newcommand{\communionTranslation}{%
  This is My Body, which shall be given up for you: this is the cup of the new covenant in My Blood, says the Lord; Do this as often as you receive it, in remembrance of Me.
}
\newcommand{\postcommunion}{%
  \l{%
    Adésto nobis, Dómine, Deus noster: et, quos tuis mystériis recreásti, perpétuis defénde subsídiis.
  }
  \e{%
    Stand by us, O Lord our God, and protect by Your everlasting help those to whom You have given new strength through Your sacrament.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/17/kyrie}

\newcommand{\sanctusPath}{../Ordinaries/masses/17/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/17/agnus}

\newcommand{\itePath}{../Ordinaries/masses/17/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_simple}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/ave-regina-caelorum}
\input{../MarianAntiphons/ave-regina-caelorum_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
