% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica XIV Post Pentecosten}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Protéctor noster, áspice, Deus, et réspice in fáciem Christi tui: quia mélior est dies una in átriis tuis super mília.
Quam dilécta tabernácula tua, Dómine virtútum! concupíscit, et déficit ánima mea in átria Dómini.
}
\newcommand{\introitTranslation}{%
Behold, O God, our Protector, and look upon the face of Your Anointed. Better is one day in Your courts than a thousand elsewhere.
How lovely is Your dwelling place, O Lord of Hosts! My soul yearns and pines for the courts of the Lord.
}
% 
\newcommand{\collect}{%
  \l{%
Custódi, Dómine, quǽsumus, Ecclésiam tuam propitiatióne perpétua: et quia sine te lábitur humána mortálitas; tuis semper auxíliis et abstrahátur a nóxiis et ad salutária dirigátur.
  }
  \e{%
Protect Your Church by Your abiding mercy, we beseech You, O Lord, and since all mortals fall without You, may Your help keep them from danger and guide them to salvation.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
Fratres: Spíritu ambuláte, et desidéria carnis non perficiétis. Caro enim concupíscit advérsus spíritum, spíritus autem advérsus carnem: hæc enim sibi ínvicem adversántur, ut non quæcúmque vultis, illa faciátis. Quod si spíritu ducímini, non estis sub lege. Manifésta sunt autem ópera carnis, quæ sunt fornicátio, immundítia, impudicítia, luxúria, idolórum sérvitus, venefícia, inimicítiæ, contentiónes, æmulatiónes, iræ, rixæ, dissensiónes, sectæ, invídiæ, homicídia, ebrietátes, comessatiónes, et his simília: quæ prædíco vobis, sicut prædíxi: quóniam, qui talia agunt, regnum Dei non consequántur. Fructus autem Spíritus est: cáritas, gáudium, pax, patiéntia, benígnitas, bónitas, longanímitas, mansuetúdo, fides, modéstia, continéntia, cástitas. Advérsus hujúsmodi non est lex. Qui autem sunt Christi, carnem suam crucifixérunt cum vítiis et concupiscéntiis.
  }
  \e{%
Brethren: Walk in the Spirit, and you will not fulfill the lusts of the flesh. For the flesh lusts against the spirit, and the spirit against the flesh; for these are opposed to each other, so that you do not do what you would. But if you are led by the Spirit, you are not under the Law. Now the works of the flesh are manifest, which are immorality, uncleanness, licentiousness, idolatry, witchcrafts, enmities, contentions, jealousies, anger, quarrels, factions, parties, envies, murders, drunkenness, carousings, and suchlike. And concerning these I warn you, as I have warned you, that they who do such things will not attain the kingdom of God. But of the fruit of the Spirit is: charity, joy, peace, patience, kindness, goodness, long-suffering, mildness, faith, modesty, continency, chastity. Against such things there is no law. And they who belong to Christ have crucified their flesh with its passions and desires.
  }
}

% 
\newcommand{\gradual}{%
Bonum est confidére in Dómino, quam confidére in hómine. 
Bonum est speráre in Dómino, quam speráre in princípibus. Allelúja, allelúja.
Veníte, exsultémus Dómino, jubilémus Deo, salutári nostro. Allelúja.
}
\newcommand{\gradualTranslation}{%
It is better to take refuge in the Lord than to trust in man.
It is better to take refuge in the Lord than to trust in princes. Alleluia, alleluia.
Come, let us sing joyfully to the Lord; let us acclaim the God of our salvation. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Dixit Jesus discípulis suis: Nemo potest duóbus dóminis servíre: aut enim unum ódio habébit, et álterum díliget: aut unum sustinébit, et álterum contémnet. Non potéstis Deo servíre et mammónæ. Ideo dico vobis, ne sollíciti sitis ánimæ vestræ, quid manducétis, neque córpori vestro, quid induámini. Nonne ánima plus est quam esca: et corpus plus quam vestiméntum? Respícite volatília cœli, quóniam non serunt neque metunt neque cóngregant in hórrea: et Pater vester cœléstis pascit illa. Nonne vos magis pluris estis illis? Quis autem vestrum cógitans potest adjícere ad statúram suam cúbitum unum? Et de vestiménto quid sollíciti estis? Consideráte lília agri, quómodo crescunt: non labórant neque nent. Dico autem vobis, quóniam nec Sálomon in omni glória sua coopértus est sicut unum ex istis. Si autem fænum agri, quod hódie est et cras in clíbanum míttitur, Deus sic vestit: quanto magis vos módicæ fídei? Nolíte ergo sollíciti esse, dicéntes: Quid manducábimus aut quid bibémus aut quo operiémur? Hæc enim ómnia gentes inquírunt. Scit enim Pater vester, quia his ómnibus indigétis. Quǽrite ergo primum regnum Dei et justítiam ejus: et hæc ómnia adjiciéntur vobis.
  }
  \e{%
At that time, Jesus said to His disciples: No man serve two masters; for either he will hate the one and love the other, or else he will stand by the one and despise the other. You cannot serve God and mammon. Therefore I say to you, do not be anxious for your life, what you shall eat; nor yet for your body, what you shall put on. Is not the life a greater thing than the food, and the body than the clothing? Look at the birds of the air: they do not sow, or reap, or gather into barns; yet your heavenly Father feeds them. Are not you of much more value than they? But which of you by being anxious about it can add to his stature a single cubit? And as for clothing, why are you anxious? Consider how the lilies of the field grow; they neither toil nor spin, yet I say to you that not even Solomon in all his glory was arrayed like one of those. But if God so clothes the grass of the field, which flourishes today but tomorrow is thrown into the oven, how much more you, O you of little faith! Therefore do not be anxious, saying, ‘What shall we eat?’ or, ‘What shall we drink?’ or, ‘What are we to put on?’ - for after all these things the Gentiles seek; - for your Father knows that you need all these things. But seek first the Kingdom of God and His justice, and all these things shall be given you besides.
  }
}
\newcommand{\offertory}{%
Immíttet Angelus Dómini in circúitu timéntium eum, et erípiet eos: gustáte et vidéte, quóniam suávis est Dóminus.
}
\newcommand{\offertoryTranslation}{%
The Angel of the Lord encamps around those who fear Him, and delivers them. Taste and see how good the Lord is.
}
\newcommand{\secret}{%
  \l{%
Concéde nobis, Dómine, quǽsumus, ut hæc hóstia salutáris et nostrórum fiat purgátio delictórum, et tuæ propitiátio potestátis.
  }
  \e{%
Grant us, Lord, we beseech You, that this salutary sacrifice may be not only a cleansing from our sins but also a propitiation of Your divine power.
  }
  \perDominum
}
\newcommand{\communion}{%
Primum quǽrite regnum Dei, et ómnia adjiciéntur vobis, dicit Dóminus.
}
\newcommand{\communionTranslation}{%
Seek first the Kingdom of God; and all things shall be given you besides, says the Lord.
}
\newcommand{\postcommunion}{%
  \l{%
Puríficent semper et múniant tua sacraménta nos, Deus: et ad perpétuæ ducant salvatiónis efféctum.
  }
  \e{%
May Your sacrament, O God, ever cleanse and strengthen us, and bring us to everlasting salvation.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}

\newcommand{\itePath}{../Ordinaries/masses/11/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
