% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica I in Quadragesima}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
%
\newcommand{\introit}{%
  Invocábit me, et ego exáudiam eum: erípiam eum, et glorificábo eum: longitúdine diérum adimplébo eum.
  Qui hábitat in adiutório Altíssimi, in protectióne Dei cœli commorábitur.
}
\newcommand{\introitTranslation}{%
  He shall call upon Me, and I will answer him; I will deliver him and glorify him; with length of days I will gratify him.
  You who dwell in the shelter of the Most High, shall abide in the shadow of the Almighty.
}
%
\newcommand{\collect}{%
  \l{%
    Deus, qui Ecclésiam tuam ánnua quadragesimáli observatióne puríficas: præsta famíliæ tuæ; ut, quod a te obtinére abstinéndo nítitur, hoc bonis opéribus exsequátur.
  }
  \e{%
    O God, You Who purify Your Church by the yearly Lenten observance, grant to Your household that what they strive to obtain from You by abstinence, they may achieve by good works.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
Fratres: Exhortámur vos, ne in vácuum grátiam Dei recipiátis. Ait enim: Témpore accépto exaudívi te, et in die salútis adiúvi te. Ecce, nunc tempus acceptábile, ecce, nunc dies salútis. Némini dantes ullam offensiónem, ut non vituperétur ministérium nostrum: sed in ómnibus exhibeámus nosmetípsos sicut Dei minístros, in multa patiéntia, in tribulatiónibus, in necessitátibus, in angústiis, in plagis, in carcéribus, in seditiónibus, in labóribus, in vigíliis, in ieiúniis, in castitáte, in sciéntia, in longanimitáte, in suavitáte, in Spíritu Sancto, in caritáte non ficta, in verbo veritátis, in virtúte Dei, per arma iustítiæ a dextris et a sinístris: per glóriam et ignobilitátem: per infámiam et bonam famam: ut seductóres et veráces: sicut qui ignóti et cógniti: quasi moriéntes et ecce, vívimus: ut castigáti et non mortificáti: quasi tristes, semper autem gaudéntes: sicut egéntes, multos autem locupletántes: tamquam nihil habéntes et ómnia possidéntes.
  }
  \e{%
Brethren: We entreat you not to receive the grace of God in vain. For He says, In an acceptable time I have heard you, and in the day of salvation I have helped you. Behold, now is the acceptable time; behold, now is the day of salvation! We give no offense to anyone, that our ministry may not be blamed. On the contrary, let us conduct ourselves in all circumstances as God’s ministers, in much patience; in tribulations, in hardships, in distresses; in stripes, in imprisonments, in tumults; in labors, in sleepless nights, in fastings; in innocence, in knowledge, in long-sufferings; in kindness, in the Holy Spirit, in unaffected love; in the word of truth, in the power of God; with the armor of justice on the right hand and on the left; in honor and dishonor, in evil report and good report; as deceivers and yet truthful, as unknown and yet well known, as dying, and behold, we live, as chastised but not killed, as sorrowful yet always rejoicing, as poor yet enriching many, as having nothing yet possessing all things.
  }
}

%
\newcommand{\gradual}{%
Angelis suis Deus mandávit de te, ut custódiant te in ómnibus viis tuis.
\v\ In mánibus portábunt te, ne umquam offéndas ad lápidem pedem tuum.
Qui hábitat in adiutório Altíssimi, in protectióne Dei cœli commorántur.
\v\ Dicet Dómino: Suscéptor meus es tu et refúgium meum: Deus meus, sperábo in eum.
\v\ Quóniam ipse liberávit me de láqueo venántium et a verbo áspero.
\v\ Scápulis suis obumbrábit tibi, et sub pennis eius sperábis.
\v\ Scuto circúmdabit te véritas eius: non timébis a timóre noctúrno.
\v\ A sagítta volánte per diem, a negótio perambulánte in ténebris, a ruína et dæmónio meridiáno.
\v\ Cadent a látere tuo mille, et decem mília a dextris tuis: tibi autem non appropinquábit.
\v\ Quóniam Angelis suis mandávit de te, ut custódiant te in ómnibus viis tuis.
\v\ In mánibus portábunt te, ne umquam offéndas ad lápidem pedem tuum,
\v\ Super áspidem et basilíscum ambulábis, et conculcábis leónem et dracónem.
\v\ Quóniam in me sperávit, liberábo eum: prótegam eum, quóniam cognóvit nomen meum,
\v\ Invocábit me, et ego exáudiam eum: cum ipso sum in tribulatióne,
\v\ Erípiam eum et glorificábo eum: longitúdine diérum adimplébo eum, et osténdam illi salutáre meum.
}
\newcommand{\gradualTranslation}{%
To His angels God has given command about you, that they guard you in all your ways.
\v\ Upon their hands they shall bear you up, lest you dash your foot against a stone.
You who dwell in the shelter of the Most High, shall abide in the shadow of the Almighty.
\v\ Say to the Lord, My refuge and my fortress, my God, in Whom I trust.
\v\ For He will rescue you from the snare of the fowler, from the destroying pestilence.
\v\ With His pinions He will cover you, and under His wings you shall take refuge.
\v\ His faithfulness is a buckler and a shield; you shall not fear the terror of the night.
\v\ Nor the arrow that flies by day; nor the pestilence that roams in darkness; nor the devastating plague at noon.
\v\ Though a thousand fall at your side, ten thousand at your right side, near you it shall not come.
\v\ For to His angels He has given command about you, that they may guard you in all your ways.
\v\ Upon their hands they shall bear you up, lest you dash your foot against a stone.
\v\ You shall tread upon the asp and the viper; you shall trample down the lion and the dragon.
\v\ Because he clings to Me, I will deliver him; I will set him on high because he acknowledges My name.
\v\ He shall call upon Me, and I will answer him; I will be with him in distress.
\v\ I will deliver him and glorify him; with length of days I will gratify him and will show him My salvation.
}
%
\newcommand{\gospel}{%
  \l{%
In illo témpore: Ductus est Iesus in desértum a Spíritu, ut tentarétur a diábolo. Et cum ieiunásset quadragínta diébus et quadragínta nóctibus, postea esúriit. Et accédens tentátor, dixit ei: Si Fílius Dei es, dic, ut lápides isti panes fiant. Qui respóndens, dixit: Scriptum est: Non in solo pane vivit homo, sed in omni verbo, quod procédit de ore Dei. Tunc assúmpsit eum diábolus in sanctam civitátem, et státuit eum super pinnáculum templi, et dixit ei: Si Fílius Dei es, mitte te deórsum. Scriptum est enim: Quia Angelis suis mandávit de te, et in mánibus tollent te, ne forte offéndas ad lápidem pedem tuum. Ait illi Iesus: Rursum scriptum est: Non tentábis Dóminum, Deum tuum. Iterum assúmpsit eum diábolus in montem excélsum valde: et ostendit ei ómnia regna mundi et glóriam eórum, et dixit ei: Hæc ómnia tibi dabo, si cadens adoráveris me. Tunc dicit ei Iesus: Vade, Sátana; scriptum est enim: Dóminum, Deum tuum, adorábis, et illi soli sérvies. Tunc relíquit eum diábolus: et ecce, Angeli accessérunt et ministrábant ei.
  }
  \e{%
At that time, Jesus was led into the desert by the Spirit, to be tempted by the devil. And after fasting forty days and forty nights, He was hungry. And the tempter came and said to Him, If You are the Son of God, command that these stones become loaves of bread. But He answered and said, It is written, ‘Not by bread alone does man live, but by every word that comes forth from the mouth of God.’ Then the devil took Him into the holy city and set Him on the pinnacle of the temple, and said to Him, If You are the Son of God, throw Yourself down; for it is written, ‘He has given His angels charge concerning You; and upon their hands they shall bear You up, lest You dash Your foot against a stone.’ Jesus said to him, It is written further, ‘You shall not tempt the Lord your God.’ Again, the devil took Him to a very high mountain, and showed Him all the kingdoms of the world and the glory of them. And he said to Him, All these things will I give You, if You will fall down and worship me. Then Jesus said to him, Begone, Satan, for it is written, ‘The Lord your God shall you worship and Him only shall you serve.’ Then the devil left Him; and behold, angels came and ministered to Him.
  }
}
\newcommand{\offertory}{%
  Scápulis suis obumbrábit tibi Dóminus, et sub pennis eius sperábis: scuto circúmdabit te véritas eius.
}
\newcommand{\offertoryTranslation}{%
  With His pinions the Lord will shade you, and under His wings you shall hope;
  His truth will surround you as a shield.
}
\newcommand{\secret}{%
  \l{%
    Sacrifícium quadragesimális inítii sollémniter immolámus, te, Dómine, deprecántes: ut, cum epulárum restrictióne carnálium, a noxiis quoque voluptátibus temperémus.
  }
  \e{%
    We offer these sacrificial gifts at the beginning of Lent, praying You, O Lord, that while we practice restraint in the use of bodily food, we may also refrain from harmful pleasures.
  }
  \per
}
\newcommand{\communion}{%
  Scápulis suis obumbrábit tibi Dóminus, et sub pennis eius sperábis: scuto circúmdabit te véritas eius.
}
\newcommand{\communionTranslation}{%
  With His pinions the Lord will shade you, and under His wings you shall hope;
  His truth will surround you as a shield.
}
\newcommand{\postcommunion}{%
  \l{%
    Qui nos, Dómine, sacraménti libátio sancta restáuret: et a vetustáte purgátos, in mystérii salutáris fáciat transíre consórtium.
  }
  \e{%
    May the holy offering of Your sacrament renew us, O Lord, and cause us to be purified from our old ways and come to the fellowship of this saving mystery.
  }
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../Ordinaries/masses/17/kyrie}
\newcommand{\gloriaPath}{../Ordinaries/masses/17/gloria}
\newcommand{\sanctusPath}{../Ordinaries/masses/17/sanctus}
\newcommand{\agnusPath}{../Ordinaries/masses/17/agnus}
\newcommand{\itePath}{../Ordinaries/masses/17/ite}
%
\newcommand{\creedPath}{../Ordinaries/credo/1/credo}
%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
