% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica XV Post Pentecosten}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
  Inclína, Dómine, aurem tuam ad me, et exáudi me: salvum fac servum tuum, Deus meus, sperántem in te: miserére mihi, Dómine, quóniam ad te clamávi tota die.
  Lætífica ánimam servi tui: quia ad te, Dómine, ánimam meam levávi.
}
\newcommand{\introitTranslation}{%
  Incline Your ear, O Lord; answer me; save Your servant, O my God, who trusts in You. Have pity on me, O Lord, for to You I call all the day.
  Gladden the soul of Your servant, for to You, O Lord, I lift up my soul.
}
% 
\newcommand{\collect}{%
  \l{%
    Ecclésiam tuam, Dómine, miserátio continuáta mundet et múniat: et quia sine te non potest salva consístere; tuo semper múnere gubernétur.
  }
  \e{%
    May Your abiding mercy, O Lord, cleanse and strengthen Your Church, and, since without You she cannot exist in safety, let her be ever guided by Your grace.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
Fratres: Si spíritu vívimus, spíritu et ambulémus. Non efficiámur inanis glóriæ cúpidi, ínvicem provocántes, ínvicem invidéntes. Fratres, et si præoccupátus fúerit homo in áliquo delícto, vos, qui spirituáles estis, huiúsmodi instrúite in spíritu lenitátis, consíderans teípsum, ne et tu tentéris. Alter alteríus ónera portáte, et sic adimplébitis legem Christi. Nam si quis exístimat se áliquid esse, cum nihil sit, ipse se sedúcit. Opus autem suum probet unusquísque, et sic in semetípso tantum glóriam habébit, et non in áltero. Unusquísque enim onus suum portábit. Commúnicet autem is, qui catechizátur verbo, ei, qui se catechízat, in ómnibus bonis. Nolíte erráre: Deus non irridétur. Quæ enim semináverit homo, hæc et metet. Quóniam qui séminat in carne sua, de carne et metet corruptiónem: qui autem séminat in spíritu, de spíritu metet vitam ætérnam. Bonum autem faciéntes, non deficiámus: témpore enim suo metémus, non deficiéntes. Ergo, dum tempus habémus, operémur bonum ad omnes, maxime autem ad domésticos fídei.
  }
  \e{%
Brethren: If we live by the Spirit, by the Spirit let us also walk. Let us not become desirous of vainglory, provoking one another, envying one another. Brethren, even if a person is caught doing something wrong, you who are spiritual instruct such a one in a spirit of meekness, considering yourself, lest you also be tempted. Bear one another’s burdens, and so you will fulfill the law of Christ. For if anyone thinks himself to be something, whereas he is nothing, he deceives himself. But let everyone test his own work, and so he will have glory in himself only, and not in comparison with another. For each one will bear his own burden. And let him who is instructed in the word share all good things with his teacher. Be not deceived, God is not mocked. For what a man sows in the flesh, from the flesh also will reap corruption. But he who sows in the spirit, from the spirit will reap life everlasting. And in doing good let us not grow tired; for in due time we shall reap if we do not relax. Therefore, while we have time, let us do good to all men, but especially to those who are of the household of faith.
  }
}

% 
\newcommand{\gradual}{%
  Bonum est confitéri Dómino: et psallere nómini tuo, Altíssime.
  \v.~Ad annuntiándum mane misericórdiam tuam, et veritátem tuam per noctem. Allelúia, allelúia.
  Quóniam Deus magnus Dóminus, et Rex magnus super omnem terram. Allelúia.
}
\newcommand{\gradualTranslation}{%
  It is good to give thanks to the Lord, to sing to Your name, Most High.
  \v.~To proclaim Your kindness at dawn and Your faithfulness throughout the night. Alleluia, alleluia.
  For the Lord is a great God, and a great King over all the earth. Alleluia.
}
% 
\newcommand{\gospel}{%
  \l{%
    In illo témpore: Ibat Iesus in civitátem, quæ vocátur Naim: et ibant cum eo discípuli eius et turba copiósa. Cum autem appropinquáret portæ civitátis, ecce, defúnctus efferebátur fílius únicus matris suæ: et hæc vidua erat: et turba civitátis multa cum illa. Quam cum vidísset Dóminus, misericórdia motus super eam, dixit illi: Noli flere. Et accéssit et tétigit lóculum. - Hi autem, qui portábant, stetérunt. - Et ait: Adoléscens, tibi dico, surge. Et resédit, qui erat mórtuus, et cœpit loqui. Et dedit illum matri suæ. Accépit autem omnes timor: et magnificábant Deum, dicéntes: Quia Prophéta magnus surréxit in nobis: et quia Deus visitávit plebem suam.
  }
  \e{%
    At that time, Jesus went to a town called Naim; and His disciples and a large crowd went with Him. And as He drew near the gate of the town, behold, a dead man was being carried out, the only son of his mother, and she was a widow; and a large gathering from the town was with her. And the Lord, seeing her, had compassion on her, and said to her, Do not weep. And He went up and touched the stretcher; and the bearers stood still. And He said, Young man, I say to you, arise. And he who was dead, sat up, and began to speak. And He gave him to his mother. But fear seized upon all, and they began to glorify God, saying, A great prophet has risen among us, and God has visited His people.
  }
}
\newcommand{\offertory}{%
  Exspéctans exspectávi Dóminum, et respéxit me: et exaudívit deprecatiónem meam: et immísit in os meum cánticum novum, hymnum Deo nostro.
}
\newcommand{\offertoryTranslation}{%
  I have waited, waited for the Lord, and He stooped toward me, and heard my cry. And He put a new song into my mouth, a hymn to our God.
}
\newcommand{\secret}{%
  \l{%
    Tua nos, Dómine, sacramenta custodiant: et contra diabólicos semper tueántur incúrsus.
  }
  \e{%
    May Your sacrament, O Lord, always keep us and guard us from the assaults of the devil.
  }
  \per
}
\newcommand{\communion}{%
  Panis, quem ego dédero, caro mea est pro sǽculi vita.
}
\newcommand{\communionTranslation}{%
  The bread that I will give is My Flesh for the life of the world.
}
\newcommand{\postcommunion}{%
  \l{%
    Mentes nostras et córpora possídeat, quǽsumus, Dómine, doni cœléstis operátio: ut non noster sensus in nobis, sed iúgiter eius prævéniat efféctus.
  }
  \e{%
    May the working of the heavenly gift, O Lord, so possess us, mind and body, that the action of the sacrament, rather than our senses, may continually prevail in us.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../Ordinaries/masses/8/kyrie}
\newcommand{\gloriaPath}{../Ordinaries/masses/8/gloria}
\newcommand{\sanctusPath}{../Ordinaries/masses/8/sanctus}
\newcommand{\agnusPath}{../Ordinaries/masses/8/agnus}
\newcommand{\itePath}{../Ordinaries/masses/8/ite}
% 
\newcommand{\creedPath}{../Ordinaries/credo/1/credo}
% 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
