\documentclass[a5paper,10pt]{memoir}
% Packages
\usepackage[nobottomtitles]{titlesec}
\usepackage{fontspec}
\setmainfont{TeX Gyre Pagella} %palatino clone
\usepackage{microtype}
\usepackage[british, latin]{babel}
% local
\usepackage{rubrics}
\usepackage{styling}
\usepackage{titlepage}
% Config
\copypagestyle{versionplain}{plain}
\newcommand{\version}{\tiny Release: v1.0.0 (template v2.4.7)}
\makeevenfoot{versionplain}{\thepage}{}{\version}
\makeoddfoot{versionplain}{\version}{}{\thepage}
\pagestyle{versionplain}
\thispagestyle{empty}
% =========
% per-document styling: we don't set this in `styling.sty' as we might want
% different layouts.
% =========
% layout
\setulmarginsandblock{0.5in}{0.7in}{*}
\setlrmarginsandblock{0.5in}{0.5in}{*}
\checkandfixthelayout
% headers
\setsecnumdepth{chapter}
\setsecheadstyle{\Large\scshape\raggedright\centering}
\setsubsubsecheadstyle{\color{red}\large\scshape\raggedright\centering}
\setparaheadstyle{\color{red}\large\raggedright\centering}
\setafterparaskip{1.5ex plus .2ex}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0em}
\midsloppy

\input{propers}

\begin{document}
\selectlanguage{latin}

\titlePage{Sacra Missa}{\masstype}{\feast}{../img/logo.pdf}

% 

% 
\section{Introit}
% 
\red{When the celebrant reaches the altar:}
% 
\gregorioscore{introit}
\oneColumnTranslation{\introitTranslation}
% 

\section{Kyrie}
\red{Immediately after the Introit:}
\gregorioscore{\kyriePath}

% 

\section{Collect}
\gregorioscore{\dominusVobiscumPath}
\black{
  \oremus
  \collect
}
\gregorioscore{\amenPath}

\section{Lesson}
\red{The lesson is chanted:}
\black{\lesson}

% 
% 
\section{Gradual}
% 
\red{After the Chanting of the lesson, or during the (secret) reading if
  so appointed:}
\gregorioscore{gradual}
% 
% 
\gregorioscore{tract}
% 
% 
\oneColumnTranslation{\gradualTranslation}
% 

% 
\section{Sequence}
\gregorioscore{sequentia}
\oneColumnTranslation{\sequentiaTranslation}
% 

\section{Gospel}
\red{The choir sings the responses at the Holy Gospel:}
\gregorioscore{\dominusVobiscumPath}
\gregorioscore{\sequentiPath}
\black{\gospel}

% 

\section{Response prior to the Offertory}
\red{Just before the chanting of the Offertory:}
\gregorioscore{\dominusVobiscumPath}

\section{Offertory}
\red{Immediately after the Celebrant chants the previous “Oremus”:}
\gregorioscore{offertory}
\oneColumnTranslation{\offertoryTranslation}

\red{A motet or hymn may be sung here.}

\section{Secret}
\black{\secret}

\section{Responses at the Preface}
\gregorioscore{\prefacePath}

\section{Sanctus and Benedictus}
\red{Immediately after the Celebrant concludes the chanting of the Preface:}
\gregorioscore{\sanctusPath}

\section{Amen at the end of the Canon of the Mass}
\gregorioscore{\amenPath}

\section{Pater Noster}
\red{The Celebrant alone chants the “Pater Noster.” The Choir sings the conclusion:}
\gregorioscore{\sedLiberaNosPath}

\section{Breaking of the Host}
\gregorioscore{\paxDominiPath}


\section{Agnus Dei}
\gregorioscore{\agnusPath}

\section{Communion}
\red{Once the Celebrant begins to distribute Holy Communion:}
\gregorioscore{communion}
\oneColumnTranslation{\communionTranslation}

\red{A motet or hymn may be sung here.}

\section{Post-Communion Collect}
\gregorioscore{\dominusVobiscumPath}
\black{
  \oremus
  \postcommunion
}
\gregorioscore{\amenPath}


\section{The Absolution}
\red{When the celebrant goes to the catafalque:}
\gregorioscore{libera}
\oneColumnTranslation{\liberaTranslation}

\red{Then the celebrant sings the Pater noster in silence, resuming:}
\black{
  \l{\v~Et ne nos indúcas in tentatiónem.}
  \e{\v~And lead us not into temptation.}
  \l{\r~Sed líbera nos a málo.}
  \e{\r~But deliver us from evil.}
  \l{\v~A pórta inferi.}
  \e{\v~From the gate of hell.}
  \l{\r~Erue, Dómine, ánimas eorum.}
  \e{\r~Rescue, O Lord, their souls.}
  \l{\v~Requiéscant in páce.}
  \e{\v~May they rest in peace.}
  \amen
  \domineexaudi
  \dominusvobiscum
}
\red{After the prayer:}\black{
  \l{\v~Réquiem aetérnam dóna éis Dómine.}
  \e{\v~Eternal rest grant unto them, O Lord. }
  \l{\r~Et lux perpétua lúceat éis.}
  \e{\r~And let perpetual light shine upon them.}
}
\gregorioscore{\itePath}


\printFoot

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: luatex
%%% End:
