% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica XIX Post Pentecosten}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
  Salus pópuli ego sum, dicit Dóminus: de quacúmque tribulatióne clamáverint ad me, exáudiam eos: et ero illórum Dóminus in perpétuum.
}
\newcommand{\introitTranslation}{%
  I am the salvation of the people, says the Lord; in whatever tribulation they shall cry to Me, I will hear them; and I will be their Lord forever.
}
% 
\newcommand{\collect}{%
  \l{%
    Omnípotens et miséricors Deus, univérsa nobis adversántia propitiátus exclúde: ut mente et córpore páriter expedíti, quæ tua sunt, líberis méntibus exsequámur.
  }
  \e{%
    Almighty and merciful God, graciously keep away from us all misfortune, that, unhampered in soul and body, we may perform with peaceful minds the works that are Yours.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
    Fratres: Renovámini spíritu mentis vestræ, et indúite novum hóminem, qui secúndum Deum creátus est in iustítia et sanctitáte veritátis. Propter quod deponéntes mendácium, loquímini veritátem unusquísque cum próximo suo: quóniam sumus ínvicem membra. Irascímini, et nolíte peccáre: sol non occídat super iracúndiam vestram. Nolíte locum dare diábolo: qui furabátur, iam non furétur; magis autem labóret, operándo mánibus suis, quod bonum est, ut hábeat, unde tríbuat necessitátem patiénti.
  }
  \e{%
    Brethren: Be renewed in the spirit of your mind, and put on the new man, which has been created according to God in justice and holiness of truth. Wherefore, put away lying and speak truth each one with his neighbor, because we are members of one another. Be angry and do not sin; do not let the sun go down upon your anger; do not give place to the devil. He who was wont to steal, let him steal no longer; but rather let him labor, working with his hands at what is good, that he may have something to share with him who suffers need.
  }
}

% 
\newcommand{\gradual}{%
  Dirigátur orátio mea, sicut incénsum in conspéctu tuo, Dómine.
  \v~Elevatio mánuum meárum sacrifícium vespertínum. Allelúia, allelúia
  \v~Confitémini Dómino, et invocáte nomen eius: annuntiáte inter gentes ópera eius. Allelúia.
}
\newcommand{\gradualTranslation}{%
  Let my prayer come like incense before You, O Lord.
  \v~The lifting up of my hands, like the evening sacrifice. Alleluia, alleluia.
  \v~Give thanks to the Lord, invoke His name; make known among the nations His deeds. Alleluia.
}
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Loquebátur Iesus princípibus sacerdótum et pharisǽis in parábolis, dicens: Símile factum est regnum cœlórum hómini regi, qui fecit núptias fílio suo. Et misit servos suos vocáre invitátos ad nuptias, et nolébant veníre. Iterum misit álios servos, dicens: Dícite invitátis: Ecce, prándium meum parávi, tauri mei et altília occísa sunt, et ómnia paráta: veníte ad núptias. Illi autem neglexérunt: et abiérunt, álius in villam suam, álius vero ad negotiatiónem suam: réliqui vero tenuérunt servos eius, et contuméliis afféctos occidérunt. Rex autem cum audísset, iratus est: et, missis exercítibus suis, pérdidit homicídas illos et civitátem illórum succéndit. Tunc ait servis suis: Núptiæ quidem parátæ sunt, sed, qui invitáti erant, non fuérunt digni. Ite ergo ad exitus viárum et, quoscúmque invenéritis, vocáte ad núptias. Et egréssi servi eius in vias, congregavérunt omnes, quos invenérunt, malos et bonos: et implétæ sunt núptiæ discumbéntium. Intrávit autem rex, ut vidéret discumbéntes, et vidit ibi hóminem non vestítum veste nuptiáli. Et ait illi: Amíce, quómodo huc intrásti non habens vestem nuptiálem? At ille obmútuit. Tunc dixit rex minístris: Ligátis mánibus et pédibus eius, míttite eum in ténebras exterióres: ibi erit fletus et stridor déntium. Multi enim sunt vocáti, pauci vero elécti.
  }
  \e{%
At that time, Jesus spoke to the chief priests and the Pharisees in parables, saying, The kingdom of heaven is like a king who made a marriage feast for his son. And he sent his servants to call in those invited to the marriage feast, but they would not come. Again he sent out other servants, saying, "Tell those who are invited, behold, I have prepared my dinner; my oxen and fatlings are killed, and everything is ready; come to the marriage feast." But they made light of it, and went off, one to his farm, and another to his business; and the rest laid hold of his servants, treated them shamefully, and killed them. But when the king heard of it, he was angry; and he sent his armies, destroyed those murderers, and burnt their city. Then he said to his servants, "The marriage feast indeed is ready, but those who were invited were not worthy; go therefore to the crossroads, and invite to the marriage feast whomever you shall find." And his servants went out into the roads, and gathered all whom they found, both good and bad; and the marriage feast was filled with guests. Now the king went in to see the guests, and he saw there a man who had not on a wedding garment. And he said to him, "Friend, how did you come in here without a wedding garment?" But he was speechless. Then the king said to the attendants, "Bind his hands and feet and cast him forth into the darkness outside, where there will be the weeping and the gnashing of teeth." For many are called, but few are chosen.
  }
}
\newcommand{\offertory}{%
  Si ambulávero in médio tribulatiónis, vivificábis me, Dómine: et super iram inimicórum meórum exténdes manum tuam, et salvum me fáciet déxtera tua.
}
\newcommand{\offertoryTranslation}{%
  Though I walk amid distress, You preserve me, O Lord; against the anger of my enemies You raise Your hand; Your right hand saves me.
}
\newcommand{\secret}{%
  \l{%
    Hæc múnera, quǽsumus, Dómine, quæ óculis tuæ maiestátis offérimus, salutária nobis esse concéde.
  }
  \e{%
    Grant, we beseech You, O Lord, that these gifts which we offer in the sight of Your majesty, may be the means of our salvation.
  }
  \per
}
\newcommand{\communion}{%
  Tu mandásti mandáta tua custodíri nimis: útinam dirigántur viæ meæ, ad custodiéndas iustificatiónes tuas.
}
\newcommand{\communionTranslation}{%
  You have commanded that Your precepts be diligently kept. Oh, that I might be firm in the ways of keeping Your statutes!
}
\newcommand{\postcommunion}{%
  \l{%
    Tua nos, Dómine, medicinális operátio, et a nostris perversitátibus cleménter expédiat, et tuis semper fáciat inhærére mandátis.
  }
  \e{%
    May Your healing power, O Lord, mercifully deliver us from our waywardness and make us ever keep Your commandments.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}
\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}
\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}
\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}
\newcommand{\itePath}{../Ordinaries/masses/11/ite}
% 
\newcommand{\creedPath}{../Ordinaries/credo/1/credo}
% 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
