% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica III Post Pascha}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Iubiláte Deo, omnis terra, allelúia: psalmum dícite nómini eius, allelúia: date glóriam laudi eius, allelúia, allelúia, allelúia.
Dícite Deo, quam terribília sunt ópera tua, Dómine! in multitúdine virtútis tuæ mentiéntur tibi inimíci tui.
}
\newcommand{\introitTranslation}{%
Shout with joy to God, all the earth, allelúja, sing ye a psalm to his name, allelúja; give glory to his praise, allelúja, allelúja, allelúja.
Say unto God, How terrible are thy works, O Lord! in the multitude of thy strength thy enemies shall lie to thee.
}
% 
\newcommand{\collect}{%
  \l{%
Deus, qui errántibus, ut in viam possint redíre iustítiæ, veritátis tuæ lumen osténdis: da cunctis, qui christiána professióne censéntur, et illa respúere, quæ huic inimíca sunt nómini; et ea, quæ sunt apta, sectári.
  }
  \e{%
Almighty God, Who showest to them that be in error the light of thy truth, to the intent that they may return into the way of righteousness, grant unto all them that are admitted into the Christian faith may eschew those things that are contrary to their profession, and follow all such things as are agreeable to the same.
}
  \per
  \amen
}
\newcommand{\lesson}{%
  \l{%
Caríssimi: Obsecro vos tamquam ádvenas et peregrínos abstinére vos a carnálibus desidériis, quæ mílitant advérsus ánimam, conversatiónem vestram inter gentes habéntes bonam: ut in eo, quod detréctant de vobis tamquam de malefactóribus, ex bonis opéribus vos considerántes, gloríficent Deum in die visitatiónis. Subiécti ígitur estóte omni humánæ creatúræ propter Deum: sive regi, quasi præcellénti: sive dúcibus, tamquam ab eo missis ad vindíctam malefactórum, laudem vero bonórum: quia sic est volúntas Dei, ut benefaciéntes obmutéscere faciátis imprudéntium hóminum ignorántiam: quasi líberi, et non quasi velámen habéntes malítiæ libertátem, sed sicut servi Dei. Omnes honoráte: fraternitátem dilígite: Deum timéte: regem honorificáte. Servi, súbditi estóte in omni timóre dóminis, non tantum bonis et modéstis, sed étiam dýscolis. Hæc est enim grátia: in Christo Iesu, Dómino nostro.
  }
  \e{%
Dearly beloved, I beseech you as strangers and pilgrims, to refrain yourselves from carnal desires which war against the soul, Having your conversation good among the Gentiles: that whereas they speak against you as evildoers, they may, by the good works, which they shall behold in you, glorify God in the day of visitation. Be ye subject therefore to every human creature for God's sake: whether it be to the king as excelling; Or to governors as sent by him for the punishment of evildoers, and for the praise of the good: For so is the will of God, that by doing well you may put to silence the ignorance of foolish men: As free, and not as making liberty a cloak for malice, but as the servants of God. Honour all men. Love the brotherhood. Fear God. Honour the king. Servants, be subject to your masters with all fear, not only to the good and gentle, but also to the froward. For this is thankworthy, if for conscience towards God, a man endure sorrows, suffering wrongfully.
  }
}

% 
\newcommand{\gradual}{%
Allelúia, allelúia.
Redemptiónem misit Dóminus pópulo suo. Allelúia.
Oportébat pati Christum, et resúrgere a mórtuis: et ita intráre in glóriam suam. Allelúia.
}
\newcommand{\gradualTranslation}{%
Allelúja, allelúja.
He hath sent redemption to his people:
Thus it behoved Christ to suffer, and to rise again from the dead, the third day. Allelúja.
}
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Dixit Iesus discípulis suis: Módicum, et iam non vidébitis me: et íterum módicum, et vidébitis me: quia vado ad Patrem. Dixérunt ergo ex discípulis eius ad ínvicem: Quid est hoc, quod dicit nobis: Módicum, et non vidébitis me: et íterum módicum, et vidébitis me, et quia vado ad Patrem? Dicébant ergo: Quid est hoc, quod dicit: Módicum? nescímus, quid lóquitur. Cognóvit autem Iesus, quia volébant eum interrogáre, et dixit eis: De hoc quǽritis inter vos, quia dixi: Módicum, et non vidébitis me: et íterum módicum, et vidébitis me. Amen, amen, dico vobis: quia plorábitis et flébitis vos, mundus autem gaudébit: vos autem contristabímini, sed tristítia vestra vertétur in gáudium. Múlier cum parit, tristítiam habet, quia venit hora eius: cum autem pepérerit púerum, iam non méminit pressúræ propter gáudium, quia natus est homo in mundum. Et vos ígitur nunc quidem tristítiam habétis, íterum autem vidébo vos, et gaudébit cor vestrum: et gáudium vestrum nemo tollet a vobis.
  }
  \e{%
At that time: Jesus said to his disciples: A little while, and now you shall not see me; and again a little while, and you shall see me: because I go to the Father. Then some of the disciples said one to another: What is this that he saith to us: A little while, and you shall not see me; and again a little while, and you shall see me, and, because I go to the Father? They said therefore: What is this that he saith, A little while? we know not what he speaketh. And Jesus knew that they had a mind to ask him; and he said to them: Of this do you inquire among yourselves, because I said: A little while, and you shall not see me; and again a little while, and you shall see me? Amen, amen I say to you, that you shall lament and weep, but the world shall rejoice; and you shall be made sorrowful, but your sorrow shall be turned into joy. A woman, when she is in labour, hath sorrow, because her hour is come; but when she hath brought forth the child, she remembereth no more the anguish, for joy that a man is born into the world. So also you now indeed have sorrow; but I will see you again, and your heart shall rejoice; and your joy no man shall take from you.
  }
}
\newcommand{\offertory}{%
Lauda, ánima mea, Dóminum: laudábo Dóminum in vita mea: psallam Deo meo, quámdiu ero, allelúia.
}
\newcommand{\offertoryTranslation}{%
Praise the Lord, O my soul, in my life I will praise the Lord: as long as I shall be. Allelúja.
}
\newcommand{\secret}{%
  \l{%
His nobis, Dómine, mystériis conferátur, quo, terréna desidéria mitigántes, discámus amáre cœléstia.
  }
  \e{%
Confer on us, O Lord, by these mysteries the moderation of our earthly desires: and teach us to love the things of heaven.
  }
  \per
}
\newcommand{\communion}{%
Módicum, et non vidébitis me, allelúia: íterum módicum, et vidébitis me, quia vado ad Patrem, allelúia, allelúia.
}
\newcommand{\communionTranslation}{%
A little while, and now you shall not see me; and again a little while, and you shall see me: because I go to the Father, allelúja, allelúja.
}
\newcommand{\postcommunion}{%
  \l{%
Sacraménta quæ súmpsimus, quǽsumus, Dómine: et spirituálibus nos instáurent aliméntis, et corporálibus tueántur auxíliis.
  }
  \e{%
May the Sacraments which we have received, O Lord, we ask, refresh us with spiritual nourishment, and preserve us with bodily assistance.
  }
  \per
  \amen
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../Ordinaries/masses/1/kyrie}
\newcommand{\gloriaPath}{../Ordinaries/masses/1/gloria}
\newcommand{\sanctusPath}{../Ordinaries/masses/1/sanctus}
\newcommand{\agnusPath}{../Ordinaries/masses/1/agnus}
\newcommand{\itePath}{../Ordinaries/masses/1/ite}
% 
\newcommand{\creedPath}{../Ordinaries/credo/1/credo}
% 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
