% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica V quæ superfuit Post Epiphaniam}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
  Dicit Dóminus: Ego cógito cogitatiónes pacis, et non afflictiónis: invocábitis me, et ego exáudiam vos: et redúcam captivitátem vestram de cunctis locis.
  Benedixísti, Dómine, terram tuam: avertísti captivitátem Iacob.
}
\newcommand{\introitTranslation}{%
  The Lord says: "I think thoughts of peace, and not of affliction. You shall call upon Me, and I will hear you; and I will bring back your captivity from all places."
  You have favored, O Lord, Your land; You have restored the well-being of Jacob.
}
% 
\newcommand{\collect}{%
  \l{%
    Famíliam tuam, quǽsumus, Dómine, contínua pietáte custódi: ut, quæ in sola spe grátiæ cœléstis innítitur, tua semper protectióne muniátur.
  }
  \e{%
    O Lord, we beseech You to keep Your household continually under Your mercy: that as it leans only upon the hope of Your heavenly grace, so it may always be protected by Your mighty power.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
    Fratres: Indúite vos sicut electi Dei, sancti et dilecti, víscera misericórdiæ, benignitátem, humilitátem, modéstiam, patiéntiam: supportántes ínvicem, et donántes vobismetípsis, si quis advérsus áliquem habet querélam: sicut et Dóminus donávit vobis, ita et vos. Super ómnia autem hæc caritátem habéte, quod est vínculum perfectionis: et pax Christi exsúltet in córdibus vestris, in qua et vocáti estis in uno córpore: et grati estóte. Verbum Christi hábitet in vobis abundánter, in omni sapiéntia, docéntes et commonéntes vosmetípsos psalmis, hymnis et cánticis spirituálibus, in grátia cantántes in córdibus vestris Deo. Omne, quodcúmque fácitis in verbo aut in ópere, ómnia in nómine Dómini Iesu Christi, grátias agéntes Deo et Patri per Iesum Christum, Dóminum nostrum.
  }
  \e{%
    Brethren: Put on, as God’s chosen ones, holy and beloved, a heart of mercy, kindness, humility, meekness, patience. Bear with one another and forgive one another, if anyone has a grievance against any other; even as the Lord has forgiven you, so also do you forgive. But above all these things have charity, which is the bond of perfection. And may the peace of Christ reign in your hearts; unto that peace, indeed, you were called in one body. Show yourselves thankful. Let the word of Christ dwell in you abundantly: in all wisdom teach and admonish one another by psalms, hymns and spiritual songs, singing in your hearts to God by His grace. Whatever you do in word or in work, do all in the name of the Lord Jesus Christ, giving thanks to God the Father through Jesus Christ our Lord.
  }
}

% 
\newcommand{\gradual}{%
  Liberásti nos, Dómine, ex affligéntibus nos: et eos, qui nos odérunt, confudísti.
  In Deo laudábimur tota die, et in nómine tuo confitébimur in sǽcula. Allelúia, allelúia.
  De profúndis clamávi ad te, Dómine: Dómine, exáudi oratiónem meam. Allelúia.
}
\newcommand{\gradualTranslation}{%
  You saved us, O Lord, from our foes, and those who hated us You put to shame.
  In God we gloried day by day; Your name we praised always. Alleluia, alleluia.
  Out of the depths I have cried to thee, O Lord: Lord, hear my prayer.
  Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
    In illo témpore: Dixit Iesus turbis parábolam hanc: Símile factum est regnum cœlórum hómini, qui seminávit bonum semen in agro suo. Cum autem dormírent hómines, venit inimícus eius, et superseminávit zizánia in médio trítici, et ábiit. Cum autem crevísset herba et fructum fecísset, tunc apparuérunt et zizánia. Accedéntes autem servi patrisfamílias, dixérunt ei: Dómine, nonne bonum semen seminásti in agro tuo? Unde ergo habet zizánia? Et ait illis: Inimícus homo hoc fecit. Servi autem dixérunt ei: Vis, imus, et collígimus ea? Et ait: Non: ne forte colligéntes zizánia eradicétis simul cum eis et tríticum. Sínite utráque créscere usque ad messem, et in témpore messis dicam messóribus: Collígite primum zizánia, et alligáte ea in fascículos ad comburéndum, tríticum autem congregáte in hórreum meum.
  }
  \e{%
    At that time, Jesus spoke this parable to the crowds: The kingdom of heaven is like a man who sowed good seed in his field; but while men were asleep, his enemy came and sowed weeds among the wheat, and went away. And when the blade sprang up and brought forth fruit, then the weeds appeared as well. And the servants of the householder came and said to him, ‘Sir, did you not sow good seed in your field? How then does it have weeds?’ He said to them, ‘An enemy has done this.’ And the servants said to him, ‘Will you have us go and gather them up?’ ‘No,’ he said, ‘lest in gathering the weeds you root up the wheat along with them. Let both grow together until the harvest; and at harvest time I will say to the reapers: Gather up the weeds first, and bind them in bundles to burn; but gather the wheat into my barns.’
  }
}
\newcommand{\offertory}{%
  De profúndis clamávi ad te, Dómine: Dómine, exáudi oratiónem meam: de profúndis clamávi ad te, Dómine.
}
\newcommand{\offertoryTranslation}{%
  Out of the depths I cry to You, O Lord; Lord, hear my prayer! Out of the depths I cry to You, O Lord.
}
\newcommand{\secret}{%
  \l{%
    Hóstias tibi, Dómine, placatiónis offérimus: ut et delícta nostra miserátus absólvas, et nutántia corda tu dírigas.
  }
  \e{%
    We offer You, O Lord, this sacrifice of atonement, that You would mercifully absolve our sins and direct our faltering hearts.
  }
  \per
}
\newcommand{\communion}{%
  Amen, dico vobis, quidquid orántes pétitis, crédite, quia accipiétis, et fiet vobis.
}
\newcommand{\communionTranslation}{%
  Amen I say to you, all things whatever you ask for in prayer, believe that you shall receive, and it shall be done to you.
}
\newcommand{\postcommunion}{%
  \l{%
    Quǽsumus, omnípotens Deus: ut illíus salutáris capiámus efféctum, cuius per hæc mystéria pignus accépimus.
  }
  \e{%
    We pray You, almighty God, that we may obtain that salvation whose pledge we have received in this divine sacrament.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.


\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}

\newcommand{\itePath}{../Ordinaries/masses/11/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
