% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{In Exaltatione Sanctæ Crucis}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Nos autem gloriári opórtet in Cruce Dómini nostri Iesu Christi: in quo est salus, vita et resurréctio nostra: per quem salváti et liberáti sumus.
Deus misereátur nostri, et benedícat nobis: illúminet vultum suum super nos, et misereátur nostri.
}
\newcommand{\introitTranslation}{%
But it behooves us to glory in the Cross of our Lord Jesus Christ: in Whom is our salvation, life, and resurrection: by Whom we are saved, and delivered.
May God have pity on us and bless us; may He let His face shine upon us; and may He have pity on us.
}
% 
\newcommand{\collect}{%
  \l{%
  Deus, qui nos hodiérna die Exaltatiónis sanctæ Crucis ánnua sollemnitáte lætíficas: præsta, quǽsumus; ut, cuius mystérium in terra cognóvimus, eius redemptiónis præmia in cœlo mereámur.
  }
  \e{%
  O God, Who gladden us this day by the yearly feast of the Exaltation of the Holy Cross, grant, we beseech You, that we who know on earth the mysteries of Christ may be found worthy to obtain in heaven the rewards of His redemption.
  }
  \perEundem
}
\newcommand{\lesson}{%
  \l{%
  Fratres: Hoc enim sentíte in vobis, quod et in Christo Iesu: qui, cum in forma Dei esset, non rapinam arbitrátus est esse se æquálem Deo: sed semetípsum exinanívit, formam servi accipiens, in similitudinem hóminum factus, et hábitu inventus ut homo. Humiliávit semetípsum, factus obœ́diens usque ad mortem, mortem autem crucis. Propter quod et Deus exaltávit illum: et donávit illi nomen, quod est super omne nomen: [hic genuflectitur] ut in nomine Iesu omne genu flectátur cœléstium, terréstrium et infernórum: et omnis lingua confiteátur, quia Dóminus Iesus Christus in glória est Dei Patris.
  }
  \e{%
  Brethren: Have this mind in you which was also in Christ Jesus, Who though He was by nature God, did not consider being equal to God a thing to be clung to, but emptied Himself, taking the nature of a slave and being made like unto men. And appearing in the form of man, He humbled Himself, becoming obedient to death, even to death on a cross. Therefore God also has exalted Him and has bestowed upon Him the name that is above every name, [here all genuflect] so that at the name of Jesus every knee should bend of those in heaven, on earth and under the earth, and every tongue should confess that the Lord Jesus Christ is in the glory of God the Father.
  }
}

% 
\newcommand{\gradual}{%
Christus factus est pro nobis obœ́diens usque ad mortem, mortem autem crucis.
Propter quod et Deus exaltávit illum, et dedit illi nomen, quod est super omne nomen. Allelúia, allelúia.
Dulce lignum, dulces clavos, dúlcia ferens póndera: quæ sola fuísti digna sustinére Regem cœlórum et Dóminum. Allelúia.
}
\newcommand{\gradualTranslation}{%
Christ became obedient for us to death, even to death on a cross.
Therefore God also has exalted Him, and has bestowed upon Him the name that is above every name. Alleluia, alleluia.
Sweet the wood, sweet the nails, sweet the load that hangs on you: to bear up the King and Lord of heaven, you alone were worthy. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
  In illo témpore: Dixit Iesus turbis Iudæórum: Nunc iudícium est mundi: nunc princeps huius mundi eiiciétur foras. Et ego si exaltátus fuero a terra, ómnia traham ad meipsum. (Hoc autem dicébat, signíficans qua morte esset moritúrus.) Respóndit ei turba. Nos audívimus ex lege, quia Christus manet in ætérnum: et quómodo tu dicis: Opórtet exaltári Fílium hóminis? Quis est iste Fílius hóminis? Dixit ergo eis Iesus: Adhuc módicum lumen in vobis est. Ambuláte, dum lucem habétis, ut non vos ténebræ comprehéndant: et qui ámbulat in ténebris, nescit, quo vadat. Dum lucem habétis, crédite in lucem, ut fílii lucis sitis.
  }
  \e{%
  At that time, Jesus said to the multitudes of the Jews, Now is the judgment of the world; now will the prince of the world be cast out. And I, if I be lifted up from the earth, will draw all things to Myself. Now he said this signifying by what death He was to die. The crowd answered Him, We have heard from the Law that the Christ abides forever. And how can You say, ‘The son of Man must be lifted up’? Who is this Son of Man? Jesus therefore said to them, Yet a little while the light is among you. Walk while you have the light, that darkness may not overtake you. He who walks in the darkness does not know where he goes. While you have the light, believe in the light, that you may become sons of light.
  }
}
\newcommand{\offertory}{%
Prótege, Dómine, plebem tuam per signum sanctæ Crucis ab ómnibus insídiis inimicórum ómnium: ut tibi gratam exhibeámus servitútem, et acceptábile fiat sacrifícium nostrum, allelúia.
}
\newcommand{\offertoryTranslation}{%
Through the sign of the Holy Cross protect Your people, O Lord, from the snares of all their enemies, that we may pay You a worthy service, and our sacrifice may be acceptable to You.
}
\newcommand{\secret}{%
  \l{%
  Iesu Christi, Dómini nostri, Córpore et Sánguine saginándi, per quem Crucis est sanctificátum vexíllum: quǽsumus, Dómine, Deus noster; ut, sicut illud adoráre merúimus, ita perénniter eius glóriæ salutáris potiámur efféctu.
  }
  \e{%
  We who are about to take as nourishment the Body and Blood of Jesus Christ our Lord, through Whom the Cross became a holy emblem, beseech You, O Lord, that just as we have the grace to honor it, so we may forever enjoy the salvation it has won for us.
  }
  \perEundem
}
\newcommand{\communion}{%
Per signum Crucis de inimícis nostris líbera nos, Deus noster.
}
\newcommand{\communionTranslation}{%
Through the sign of the Cross, deliver us from our enemies, O our God.
}
\newcommand{\postcommunion}{%
  \l{%
  Adésto nobis, Dómine, Deus noster: et, quos sanctæ Crucis lætári facis honóre, eius quoque perpétuis defénde subsídiis.
  }
  \e{%
  Stand by us, O Lord our God, and protect by Your everlasting help those to whom You have given strength through Your sacrament.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/8/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/8/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/8/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/8/agnus}

\newcommand{\itePath}{../Ordinaries/masses/8/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
