% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica IV Adventus}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Roráte, cœli, désuper, et nubes pluant iustum: aperiátur terra, et gérminet Salvatórem
Cœli enárrant glóriam Dei: et ópera mánuum eius annúntiat firmaméntum.
}
\newcommand{\introitTranslation}{%
Let the Just One descend, O heavens, like dew from above, like gentle rain let the skies drop Him down. Let the earth open and a Saviour bud forth.
The heavens declare the glory of God, and the firmament proclaims His handiwork.
}
% 
\newcommand{\collect}{%
  \l{%
Excita, quǽsumus, Dómine, poténtiam tuam, et veni: et magna nobis virtúte succúrre; ut per auxílium grátiæ tuæ, quod nostra peccáta præpédiunt, indulgéntiæ tuæ propitiatiónis accéleret:
  }
  \e{%
Put forth Your power, O Lord, we beseech You, and delay not: and with Your great might come to our aid, so that what is hindered by our sins may be hastened by Your merciful goodness.
  }
  \quiVivis
}
\newcommand{\lesson}{%
  \l{%
Fratres: Sic nos exístimet homo ut minístros Christi, et dispensatóres mysteriórum Dei. Hic iam quǽritur inter dispensatóres, ut fidélis quis inveniátur. Mihi autem pro mínimo est, ut a vobis iúdicer aut ab humano die: sed neque meípsum iudico. Nihil enim mihi cónscius sum: sed non in hoc iustificátus sum: qui autem iúdicat me, Dóminus est. Itaque nolíte ante tempus iudicáre, quoadúsque véniat Dóminus: qui et illuminábit abscóndita tenebrárum, et manifestábit consília córdium: et tunc laus erit unicuique a Deo.
  }
  \e{%
Brethren: Let a man so account us, as servants of Christ and stewards of the mysteries of God. Now here it is required in stewards that a man be found trustworthy. But with me it is a very small matter to be judged by you or by man’s tribunal. Nay I do not even judge my own self. For I have nothing on my conscience, yet I am not thereby justified; but he who judges me is the Lord. Therefore, pass no judgment before the time, until the Lord comes, Who will both bring to light the things hidden in darkness and make manifest the counsels of hearts; and then everyone will have his praise from God.
  }
}

% 
\newcommand{\gradual}{%
Prope est Dóminus ómnibus invocántibus eum: ómnibus, qui ínvocant eum in veritáte.
Laudem Dómini loquétur os meum: et benedícat omnis caro nomen sanctum eius. Allelúia, allelúia,
Veni, Dómine, et noli tardáre: reláxa facínora plebis tuæ Israël. Allelúia.
}
\newcommand{\gradualTranslation}{%
The Lord is near to all who call upon Him, to all who call upon Him in truth.
May my mouth speak the praise of the Lord, and may all flesh bless His holy name. Alleluia, alleluia.
Come, O Lord, and delay not; forgive the sins of Your people Israel. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
Anno quintodécimo impérii Tibérii Cǽsaris, procuránte Póntio Piláto Iudǽam, tetrárcha autem Galilǽæ Heróde, Philíppo autem fratre eius tetrárcha Iturǽæ et Trachonítidis regionis, et Lysánia Abilínæ tetrárcha, sub princípibus sacerdotum Anna et Cáipha: factum est verbum Domini super Ioannem, Zacharíæ filium, in deserto. Et venit in omnem regiónem Iordánis, prǽdicans baptísmum pæniténtiæ in remissiónem peccatórum, sicut scriptum est in libro sermónum Isaíæ Prophétæ: Vox clamántis in desérto: Paráte viam Dómini: rectas fácite sémitas eius: omnis vallis implébitur: et omnis mons et collis humiliábitur: et erunt prava in dirécta, et áspera in vias planas: et vidébit omnis caro salutáre Dei.
  }
  \e{%
Now in the fifteenth year of the reign of Tiberius Caesar, when Pontius Pilate was procurator of Judea, and Herod tetrarch of Galilee, and Philip his brother tetrarch of the district of Iturea and Trachonitis, and Lysanias tetrarch of Abilene, during the high priesthood of Annas and Caiphas, the word of God came to John, the son of Zachary, in the desert. And he went into all the region about the Jordan, preaching a baptism of repentance for the forgiveness of sins, as it is written in the book of the words of Isaiah the prophet, The voice of one crying in the desert, ‘Make ready the way of the Lord, make straight His paths. Every valley shall be filled, and every mountain and hill shall be brought low, and the crooked ways shall be made straight, and the rough ways smooth; and all mankind shall see the salvation of God.’
  }
}
\newcommand{\offertory}{%
Ave, María, gratia plena; Dóminus tecum: benedícta tu in muliéribus, et benedíctus fructus ventris tui.
}
\newcommand{\offertoryTranslation}{%
Hail, Mary, full of grace, the Lord is with you, blessed are you among women, and blessed is the fruit of your womb.
}
\newcommand{\secret}{%
  \l{%
Sacrifíciis præséntibus, quǽsumus, Dómine, placátus inténde: ut et devotióni nostræ profíciant et salúti.
  }
  \e{%
Look with favor, O Lord, we beseech You, upon the offerings here present, that they may be profitable for our devotion and for our salvation.
  }
  \perDominum
}
\newcommand{\communion}{%
Ecce, Virgo concípiet et páriet fílium: et vocábitur nomen eius Emmánuel.
}
\newcommand{\communionTranslation}{%
Behold, a virgin shall be with child and bear a son, and shall name Him Emmanuel.
}
\newcommand{\postcommunion}{%
  \l{%
Sumptis munéribus, quǽsumus, Dómine: ut, cum frequentatióne mystérii, crescat nostræ salútis efféctus.
  }
  \e{%
Having received Your gifts, we beseech You, O Lord, that each partaking of this sacrament may increase within us its saving effect.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/17/kyrie}

\newcommand{\sanctusPath}{../Ordinaries/masses/17/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/17/agnus}

\newcommand{\itePath}{../Ordinaries/masses/17/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/alma-redemptoris-mater}
\input{../MarianAntiphons/alma-redemptoris-mater_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
