% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica III Post Epiphaniam}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Adoráte Deum, omnes Angeli ejus: audívit, et lætáta est Sion: et exsultavérunt fíliæ Judæ.
Dóminus regnávit, exsúltet terra: læténtur ínsulæ multæ.
}
\newcommand{\introitTranslation}{%
Adore God, all you His angels: Sion hears and is glad, and the cities of Juda rejoice.
The Lord is King; let the earth rejoice; let the many isles be glad.
}
% 
\newcommand{\collect}{%
  \l{%
Omnípotens sempitérne Deus, infirmitatem nostram propítius réspice: atque, ad protegéndum nos, déxteram tuæ majestátis exténde.
  }
  \e{%
Almighty and everlasting God, look with favor upon our weakness, and stretch forth the right hand of Your majesty to help and defend us.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
Fratres: Nolíte esse prudéntes apud vosmetípsos: nulli malum pro malo reddéntes: providéntes bona non tantum coram Deo, sed étiam coram ómnibus homínibus. Si fíeri potest, quod ex vobis est, cum ómnibus homínibus pacem habéntes: Non vosmetípsos defendéntes, caríssimi, sed date locum iræ. Scriptum est enim: Mihi vindícta: ego retríbuam, dicit Dóminus. Sed si esuríerit inimícus tuus, ciba illum: si sitit, potum da illi: hoc enim fáciens, carbónes ignis cóngeres super caput ejus. Noli vinci a malo, sed vince in bono malum.
  }
  \e{%
Brethren: Be not wise in your own conceits. To no man render evil for evil, but provide good things not only in the sight of God, but also in the sight of all men. If it be possible, as far as in you lies, be at peace with all men. Do not avenge yourselves, beloved, but give place to the wrath, for it is written, Vengeance is Mine: I will repay, says the Lord. But, If your enemy is hungry, give him food; if he is thirsty, give him drink; for by so doing you will heap coals of fire upon his head. Be not overcome by evil, but overcome evil with good.
  }
}

% 
\newcommand{\gradual}{%
Timébunt gentes nomen tuum, Dómine, et omnes reges terræ glóriam tuam.
Quóniam ædificávit Dóminus Sion, et vidébitur in majestáte sua. Allelúja, allelúja.
Dóminus regnávit, exsúltet terra: læténtur ínsulæ multæ. Allelúja.
}
\newcommand{\gradualTranslation}{%
The nations shall revere Your name, O Lord, and all the kings of the earth Your glory.
For the Lord has rebuilt Sion, and He shall appear in His glory. Alleluia, alleluia.
The Lord is King; let the earth rejoice; let the many isles be glad. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Cum descendísset Jesus de monte, secútæ sunt eum turbæ multæ: et ecce, leprósus véniens adorábat eum, dicens: Dómine, si vis, potes me mundáre. Et exténdens Jesus manum, tétigit eum, dicens: Volo. Mundáre. Et conféstim mundáta est lepra ejus. Et ait illi Jesus: Vide, némini díxeris: sed vade, osténde te sacerdóti, et offer munus, quod præcépit Móyses, in testimónium illis. Cum autem introísset Caphárnaum, accéssit ad eum centúrio, rogans eum et dicens: Dómine, puer meus jacet in domo paralýticus, et male torquetur. Et ait illi Jesus: Ego véniam, et curábo eum. Et respóndens centúrio, ait: Dómine, non sum dignus, ut intres sub tectum meum: sed tantum dic verbo, et sanábitur puer meus. Nam et ego homo sum sub potestáte constitútus, habens sub me mílites, et dico huic: Vade, et vadit; et alii: Veni, et venit; et servo meo: Fac hoc, et facit. Audiens autem Jesus, mirátus est, et sequéntibus se dixit: Amen, dico vobis, non inveni tantam fidem in Israël. Dico autem vobis, quod multi ab Oriénte et Occidénte vénient, et recúmbent cum Abraham et Isaac et Jacob in regno cœlórum: fílii autem regni ejiciéntur in ténebras exterióres: ibi erit fletus et stridor déntium. Et dixit Jesus centurióni: Vade et, sicut credidísti, fiat tibi. Et sanátus est puer in illa hora.
  }
  \e{%
At that time, when Jesus had come down from the mountain, great crowds followed Him. And behold, a leper came up and worshipped Him, saying, Lord, if You will, You can make me clean. And stretching forth His hand Jesus touched him, saying, I will; be made clean. And immediately his leprosy was cleansed. And Jesus said to him, See that you tell no one; but go, show yourself to the priest, and offer the gift that Moses commanded, for a witness to them. Now when He had entered Capharnaum, there came to Him a centurion who entreated Him, saying, Lord, my servant is lying sick in the house, paralyzed, and is grievously afflicted. Jesus said to him, I will come and cure him. But in answer the centurion said, Lord, I am not worthy that You should come under my roof; but only say the word, and my servant will be healed. For I too am a man subject to authority, and have soldiers subject to me; and I say to one, ‘Go,’ and he goes; and to another, ‘Come,’ and he comes; and to my servant, ‘Do this,’ and he does it. And when Jesus heard this, He marveled, and said to those who were following Him, Amen I say to you, I have not found such great faith in Israel. And I tell you that many will come from the east and from the west and will feast with Abraham and Isaac and Jacob in the kingdom of heaven, but the children of the kingdom will be put forth into the darkness outside; there will be the weeping, and the gnashing of teeth. Then Jesus said to the centurion, Go your way; as you have believed, so be it done to you. And the servant was healed in that hour.
  }
}
\newcommand{\offertory}{%
Déxtera Dómini fecit virtutem, déxtera Dómini exaltávit me: non móriar, sed vivam, et narrábo ópera Dómini.
}
\newcommand{\offertoryTranslation}{%
The right hand of the Lord has struck with power: the right hand of the Lord has exalted me; I shall not die, but live, and declare the works of the Lord.
}
\newcommand{\secret}{%
  \l{%
Hæc hóstia, Dómine, quǽsumus, emúndet nostra delícta: et, ad sacrifícium celebrándum, subditórum tibi córpora mentésque sanctíficet.
  }
  \e{%
May this offering, O Lord, we beseech You, wipe away our transgressions, and make holy the minds and bodies of Your servants for celebrating this sacrifice.
  }
  \perDominum
}
\newcommand{\communion}{%
Mirabántur omnes de his, quæ procedébant de ore Dei.
}
\newcommand{\communionTranslation}{%
All marvelled at the words that came from the mouth of God.
}
\newcommand{\postcommunion}{%
  \l{%
Quos tantis, Dómine, largíris uti mystériis: quǽsumus; ut efféctibus nos eórum veráciter aptáre dignéris.
  }
  \e{%
O Lord, as You grant us to use this great sacrament, deign, we beseech You, to make us truly worthy of its fruits.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/4/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/4/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/4/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/4/agnus}

\newcommand{\itePath}{../Ordinaries/masses/4/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/alma-redemptoris-mater}
\input{../MarianAntiphons/alma-redemptoris-mater_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
