% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Sacratissimi Cordis Domini Nostri Jesu Christi (Friday after the Octave of Corpus Christi)}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Cogitatiónes Cordis ejus in generatióne et generatiónem: ut éruat a morte ánimas eórum et alat eos in fame.
Exsultáte, justi, in Dómino: rectos decet collaudátio.
}
\newcommand{\introitTranslation}{%
The thoughts of His Heart are to all generations: to deliver them from death and preserve them in spite of famine.
Exult, you just, in the Lord; praise from the upright is fitting.
}
% 
\newcommand{\collect}{%
  \l{%
Deus, qui nobis in Corde Fílii tui, nostris vulneráto peccátis, infinítos dilectiónis thesáuros misericórditer largíri dignáris: concéde, quǽsumus; ut, illi devótum pietátis nostræ præstántes obséquium, dignæ quoque satisfactiónis exhibeámus offícium. 
  }
  \e{%
O God, Who in the Heart of Your Son, wounded by our sins, mercifully lavish upon us the infinite riches of love, grant, we beseech You, that as we offer Him the faithful service of our devotion, we may also show forth fitting reparation.
  }
  \perEundem
}
\newcommand{\lesson}{%
  \l{%
Fratres: Mihi, ómnium sanctórum mínimo, data est grátia hæc, in géntibus evangelizáre investigábiles divítias Christi, et illumináre omnes, quæ sit dispensátio sacraménti abscónditi a sǽculis in Deo, qui ómnia creávit: ut innotéscat principátibus et potestátibus in cœléstibus per Ecclésiam multifórmis sapiéntia Dei, secúndum præfinitiónem sæculórum, quam fecit in Christo Jesu, Dómino nostro, in quo habémus fidúciam et accéssum in confidéntia per fidem ejus. Hujus rei grátia flecto génua mea ad Patrem Dómini nostri Jesu Christi, ex quo omnis patérnitas in cœlis ei in terra nominátur, ut det vobis, secúndum divítias glóriæ suæ, virtúte corroborári per Spíritum ejus in interiórem hóminem, Christum habitáre per fidem in córdibus vestris: in caritáte radicáti et fundáti, ut póssitis comprehéndere cum ómnibus sanctis, quæ sit latitúdo, et longitúdo, et sublímitas, et profúndum: scire étiam supereminéntem sciéntiæ caritátem Christi, ut impleámini in omnem plenitúdinem Dei.
  }
  \e{%
Brethren: To me, the very least of all saints, there was given this grace, to announce among the Gentiles the good tidings of the unfathomable riches of Christ, and to enlighten all men as to what is the dispensation of the mystery which has been hidden from eternity in God, Who created all things; in order that through the Church there be made known to the Principalities and the Powers in the heavens the manifold wisdom of God according to the eternal purpose which He accomplished in Christ Jesus our Lord. In Him we have assurance and confident access through faith in Him. For this reason I bend my knees to the Father of our Lord Jesus Christ, from Whom all fatherhood in heaven and on earth receives its name, that He may grant you from His glorious riches to be strengthened with power through His Spirit unto the progress of the inner man; and to have Christ dwelling through faith in your hearts: so that, being rooted and grounded in love, you may be able to comprehend with all the saints what is the breadth and length and height and depth, and to know Christ’s love which surpasses knowledge, in order that you may be filled unto all the fullness of God.
  }
}

% 
\newcommand{\gradual}{%
Dulcis et rectus Dóminus: propter hoc legem dabit delinquéntibus in via.
Díriget mansúetos in judício, docébit mites vias suas. 
Allelúja, allelúja. Tóllite jugum meum super vos, et díscite a me, quia mitis sum et húmilis Corde, et inveniétis réquiem animábus vestris. Allelúja.
}
\newcommand{\gradualTranslation}{%
Good and upright is the Lord; thus He shows sinners the way.
He guides the humble to justice; He teaches the humble His way.
Alleluia, alleluia. Take My yoke upon you, and learn from Me, for I am meek, and humble of heart: and you will find rest for your souls. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Judǽi - quóniam Parascéve erat, - ut non remanérent in cruce córpora sábbato - erat enim magnus dies ille sábbati, - rogavérunt Pilátum, ut frangeréntur eórum crura, et tolleréntur. Venérunt ergo mílites: et primi quidem fregérunt crura et alteríus, qui crucifíxus est cum eo. Ad Jesum autem cum veníssent, ut vidérunt eum jam mórtuum, non fregérunt ejus crura, sed unus mílitum láncea latus ejus apéruit, et contínuo exívit sanguis et aqua. Et qui vidit, testimónium perhíbuit: et verum est testimónium ejus. Et ille scit quia vera dicit, ut et vos credátis. Facta sunt enim hæc ut Scriptúra implerétur: Os non comminuétis ex eo. Et íterum alia Scriptúra dicit: Vidébunt in quem transfixérunt.
  }
  \e{%
At that time, the Jews, since it was the Preparation Day, in order that the bodies might not remain upon the cross on the Sabbath - for that Sabbath was a solemn day, - besought Pilate that their legs might be broken, and that they might be taken away. The soldiers therefore came and broke the legs of the first, and of the other, who had been crucified with Him. But when they came to Jesus, and saw that He was already dead, they did not break His legs; but one of the soldiers opened His side with a lance, and immediately there came out blood and water. And he who saw it has borne witness, and his witness is true; and he knows that he tells the truth, that you also may believe. For these things came to pass that the Scripture might be fulfilled, Not a bone of Him shall you break. And again another Scripture says, They shall look upon Him Whom they have pierced.
  }
}
\newcommand{\offertory}{%
Impropérium exspectávi Cor meum et misériam: et sustínui, qui simul mecum contristarétur, et non fuit: consolántem me quæsívi, et non invéni.
}
\newcommand{\offertoryTranslation}{%
My heart expected reproach and misery; I looked for sympathy, but there was none; and for comforters, and I found none.
}
\newcommand{\secret}{%
  \l{%
Réspice, quǽsumus, Dómine, ad ineffábilem Cordis dilécti Fílii tui caritátem: ut quod offérimus sit tibi munus accéptum et nostrórum expiátio delictórum. 
  }
  \e{%
Look, we beseech You, O Lord, upon the Heart of Your beloved Son, with its boundless love, so that what we offer, may be an acceptable gift in Your sight and an atonement for our sins.
  }
  \perEundem
}
\newcommand{\communion}{%
Unus mílitum láncea latus ejus apéruit, et contínuo exívit sanguis et aqua.
}
\newcommand{\communionTranslation}{%
One of the soldiers opened His side with a lance, and immediately there came out blood and water.
}
\newcommand{\postcommunion}{%
  \l{%
Prǽbeant nobis, Dómine Jesu, divínum tua sancta fervórem: quo dulcíssimi Cordis tui suavitáte percépta; discámus terréna despícere, et amáre cœléstia:
  }
  \e{%
May Your sacrament, O Lord Jesus, give us holy zeal, so that, seeing the sweetness of Your most loving Heart, we may learn to despise the things of earth and love those of heaven.
  }
  \quiVivis
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.



\newcommand{\kyriePath}{../Ordinaries/masses/1/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/1/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/1/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/1/agnus}

\newcommand{\itePath}{../Ordinaries/masses/1/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
