% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica XI Post Pentecosten}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Deus in loco sancto suo: Deus qui inhabitáre facit unánimes in domo: ipse dabit virtútem et fortitúdinem plebi suæ.
Exsúrgat Deus, et dissipéntur inimíci eius: et fúgiant, qui odérunt eum, a fácie eius.
}
\newcommand{\introitTranslation}{%
God is in His holy dwelling, God Who makes men of one mind to dwell in a house; He shall give power and strength to His people.
God arises; His enemies are scattered, and those who hate Him flee before Him.
}
% 
\newcommand{\collect}{%
  \l{%
Omnípotens sempitérne Deus, qui, abundántia pietátis tuæ, et mérita súpplicum excédis et vota: effúnde super nos misericórdiam tuam; ut dimíttas quæ consciéntia métuit, et adícias quod orátio non præsúmit.
  }
  \e{%
Almighty, eternal God, You Who in the abundance of Your love always grant more than Your humble petitioners deserve, and even more than they desire, pour forth Your mercy upon us that You may forgive whatever our conscience dreads, and give in addition what our prayer does not venture to ask.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
Fratres: Notum vobis fácio Evangélium, quod prædicávi vobis, quod et accepístis, in quo et statis, per quod et salvámini: qua ratione prædicáverim vobis, si tenétis, nisi frustra credidístis. Trádidi enim vobis in primis, quod et accépi: quóniam Christus mortuus est pro peccátis nostris secúndum Scriptúras: et quia sepúltus est, et quia resurréxit tértia die secúndum Scriptúras: et quia visus est Cephæ, et post hoc úndecim. Deinde visus est plus quam quingéntis frátribus simul, ex quibus multi manent usque adhuc, quidam autem dormiérunt. Deinde visus est Iacóbo, deinde Apóstolis ómnibus: novíssime autem ómnium tamquam abortívo, visus est et mihi. Ego enim sum mínimus Apostolórum, qui non sum dignus vocári Apóstolus, quóniam persecútus sum Ecclésiam Dei. Grátia autem Dei sum id quod sum, et grátia eius in me vácua non fuit.
  }
  \e{%
Brethren: I recall to your minds the Gospel that I preached to you, which also you received, wherein also you stand, through which also you are being saved, if you hold it fast, as I preached it to you - unless you have believed to no purpose. For I delivered to you first of all, what I also received, that Christ died for our sins according to the Scriptures, and that He was buried, and that He rose again the third day, according to the Scriptures, and that He appeared to Cephas, and after that to the Eleven. Then He was seen by more than five hundred brethren at one time, many of whom are with us still, but some have fallen asleep. After that He was seen by James, then by the Apostles. And last of all, as by one born out of due time, He was seen also by me. For I am the least of the Apostles, and am not worthy to be called an Apostle, because I persecuted the Church of God. But by the grace of God I am what I am, and His grace in me has not been fruitless.
  }
}

% 
\newcommand{\gradual}{%
In Deo sperávit cor meum, et adiútus sum: et reflóruit caro mea, et ex voluntáte mea confitébor illi.
Ad te, Dómine, clamávi: Deus meus, ne síleas, ne discédas a me. Allelúia, allelúia
Exsultáte Deo, adiutóri nostro, iubiláte Deo Iacob: súmite psalmum iucúndum cum cíthara. Allelúia.
}
\newcommand{\gradualTranslation}{%
In God my heart trusts, and I find help; then my heart exults, and with my song I give Him thanks.
To You, O Lord, I call; O my God, be not deaf to me; depart not from me. Alleluia, alleluia.
Sing joyfully to God our strength; acclaim the God of Jacob. Take up a pleasant psalm with the harp. Alleluia.
}
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Exiens Iesus de fínibus Tyri, venit per Sidónem ad mare Galilǽæ, inter médios fines Decapóleos. Et addúcunt ei surdum et mutum, et deprecabántur eum, ut impónat illi manum. Et apprehéndens eum de turba seórsum, misit dígitos suos in aurículas eius: et éxspuens, tétigit linguam eius: et suspíciens in cœlum, ingémuit, et ait illi: Ephphetha, quod est adaperíre. Et statim apértæ sunt aures eius, et solútum est vínculum linguæ eius, et loquebátur recte. Et præcépit illis, ne cui dícerent. Quanto autem eis præcipiébat, tanto magis plus prædicábant: et eo ámplius admirabántur, dicéntes: Bene ómnia fecit: et surdos fecit audíre et mutos loqui.
  }
  \e{%
At that time, Jesus departing from the district of Tyre came by way of Sidon to the sea of Galilee, through the midst of the district of Decapolis. And they brought to Him one deaf and dumb, and entreated Him to lay His hand upon him. And taking him aside from the crowd, He put His fingers into the man’s ears, and spitting, He sighed, and said to him, Ephpheta, that is, Be opened. And his ears were at once opened, and the bond of his tongue was loosed, and he began to speak correctly. And He charged them to tell no one. But the more He charged them, so much the more did they continue to publish it. And so much the more did they wonder, saying, He has done all things well. He has made both the deaf to hear and the dumb to speak.
  }
}
\newcommand{\offertory}{%
Exaltábo te, Dómine, quóniam suscepísti me, nec delectásti inimícos meos super me: Dómine, clamávi ad te, et sanásti me.
}
\newcommand{\offertoryTranslation}{%
 I will extol You, O Lord, for You drew me near and did not let my enemies rejoice over me; O Lord, I cried out to You and You healed me.
}
\newcommand{\secret}{%
  \l{%
Réspice, Dómine, quǽsumus, nostram propítius servitútem: ut, quod offérimus, sit tibi munus accéptum, et sit nostræ fragilitátis subsidium.
  }
  \e{%
Look with mercy, we beseech You, O Lord, upon our act of worship that the gift we offer may be acceptable to You and may support us in our frailty.
  }
}
\newcommand{\communion}{%
Hónora Dóminum de tua substántia, et de prímitiis frugum tuárum: et implebúntur hórrea tua saturitáte, et vino torculária redundábunt.
}
\newcommand{\communionTranslation}{%
Honor the Lord with your wealth, with first fruits of all your produce. Then will your barns be filled with grain, with new wine your vats will overflow.
}
\newcommand{\postcommunion}{%
  \l{%
Sentiámus, quǽsumus, Dómine, tui perceptióne sacraménti, subsídium mentis et córporis: ut, in utróque salváti, cæléstis remédii plenitúdine gloriémur.
  }
  \e{%
By receiving Your sacrament, O Lord, may we experience Your help in mind and body, that being cured in both, we may glory in the full effect of the heavenly remedy.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}
\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}
\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}
\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}
\newcommand{\itePath}{../Ordinaries/masses/11/ite}
% 
\newcommand{\creedPath}{../Ordinaries/credo/1/credo}
% 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
