% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{S. Joseph Sponsi B.M.V Confessoris}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Justus ut palma florébit: sicut cedrus Líbani multiplicábitur: plantátus in domo Dómini: in átriis domus Dei nostri.
Bonum est confitéri Dómino: et psállere nómini tuo, Altíssime.
}
\newcommand{\introitTranslation}{%
The just man shall flourish like the palm tree, like a cedar of Lebanon shall he grow: planted in the house of the Lord, in the courts of the house of our God.
It is good to give thanks to the Lord, to sing praise to Your name, Most High.
}
% 
\newcommand{\collect}{%
  \l{%
Sanctíssimæ Genetrícis tuæ Sponsi, quǽsumus, Dómine, méritis adjuvémur: ut, quod possibílitas nostra non óbtinet, ejus nobis intercessióne donétur:
  }
  \e{%
May the merits of Your most holy Mother’s spouse help us, we beseech You, O Lord, that through his intercession we may receive what we cannot obtain by our own efforts.
  }
  \quiVivis
}
\newcommand{\lesson}{%
  \l{%
Fratres: Spectáculum facti sumus mundo et Angelis et homínibus. Nos stulti propter Christum, vos autem prudéntes in Christo: nos infírmi, vos autem fortes: vos nóbiles, nos autem ignóbiles. Usque in hanc horam et esurímus, et sitímus, et nudi sumus, et cólaphis cǽdimur, et instábiles sumus, et laborámus operántes mánibus nostris: maledícimur, et benedícimus: persecutiónem pátimur, et sustinémus: blasphemámur, et obsecrámus: tamquam purgaménta hujus mundi facti sumus, ómnium peripséma usque adhuc. Non ut confúndant vos, hæc scribo, sed ut fílios meos caríssimos móneo: in Christo Jesu, Dómino nostro.
  }
  \e{%
Brethren: We have been made a spectacle to the world, and to angels, and to men. We are fools for Christ, but you are wise in Christ! We are weak, but you are strong! You are honored, but we are without honor! To this very hour we hunger and thirst, and we are naked and buffeted, and have no fixed abode. And we toil, working with our own hands. We are reviled and we bless, we are persecuted and we bear with it, we are maligned and we entreat, we have become as the refuse of this world, the offscouring of all, even until now! I write these things not to put you to shame, but to admonish you as my dearest children, in Christ Jesus our Lord.
  }
}

% 
\newcommand{\gradual}{%
Dómine, prævenísti eum in benedictiónibus dulcédinis: posuísti in cápite ejus corónam de lápide pretióso. 
Vitam pétiit a te, et tribuísti ei longitúdinem diérum in sǽculum sǽculi.
Beátus vir, qui timet Dóminum: in mandátis ejus cupit nimis.
Potens in terra erit semen ejus: generátio rectórum benedicétur.
Glória et divítiæ in domo ejus: et justítia ejus manet in sǽculum sǽculi.
}
\newcommand{\gradualTranslation}{%
O Lord, You welcomed him with goodly blessings, You placed on his head a crown of pure gold.
He asked life of You: You gave him length of days forever and ever.
Happy the man who fears the Lord, who greatly delights in His commands.
His posterity shall be mighty upon the earth; the upright generation shall be blessed.
Wealth and riches shall be in his house; his generosity shall endure forever.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
Cum esset desponsáta Mater Jesu María Joseph, ántequam convenírent, invénta est in útero habens de Spíritu Sancto. Joseph autem, vir ejus, cum esset justus et nollet eam tradúcere, vóluit occúlte dimíttere eam. Hæc autem eo cogitánte, ecce, Angelus Dómini appáruit in somnis ei, dicens: Joseph, fili David, noli timére accípere Maríam cónjugem tuam: quod enim in ea natum est, de Spíritu Sancto est. Páriet autem fílium, et vocábis nomen ejus Jesum: ipse enim salvum fáciet pópulum suum a peccátis eórum.
  }
  \e{%
When Mary the Mother of Jesus had been betrothed to Joseph, before they came together, she was found to be with child by the Holy Spirit. But Joseph her husband, being a just man, and not wishing to expose her to reproach, was minded to put her away privately. But while he thought on these things, behold, an angel of the Lord appeared to him in a dream, saying, Do not be afraid, Joseph, son of David, to take to you Mary your wife, for that which is begotten in her is of the Holy Spirit. And she shall bring forth a Son, and you shall call His name Jesus; for He shall save His people from their sins.
  }
}
\newcommand{\offertory}{%
Véritas mea et misericórdia mea cum ipso: et in nómine meo exaltábitur cornu ejus.
}
\newcommand{\offertoryTranslation}{%
My faithfulness and My kindness shall be with him, and through My name shall his horn be exalted.
}
\newcommand{\secret}{%
  \l{%
Débitum tibi, Dómine, nostræ réddimus servitútis, supplíciter exorántes: ut, suffrágiis beáti Joseph, Sponsi Genetrícis Fílii tui Jesu Christi, Dómini nostri, in nobis tua múnera tueáris, ob cujus venerándam festivitátem laudis tibi hóstias immolámus.
  }
  \e{%
O Lord, we dutifully worship You, humbly entreating You by the prayers of blessed Joseph, Spouse of the Mother of Jesus Christ, our Lord, in whose honor we offer these sacrifices of praise, that You protect Your gifts within us.
  }
  \perEundem
}
\newcommand{\communion}{%
Joseph, fili David, noli timére accípere Maríam cónjugem tuam: quod enim in ea natum est, de Spíritu Sancto est.
}
\newcommand{\communionTranslation}{%
Do not be afraid, Joseph, son of David, to take to you Mary your wife, for that which is begotten in her is of the Holy Spirit.
}
\newcommand{\postcommunion}{%
  \l{%
Adésto nobis, quǽsumus, miséricors Deus: et, intercedénte pro nobis beáto Joseph Confessóre, tua circa nos propitiátus dona custódi.
  }
  \e{%
Be with us, we beseech You, O merciful God, and by the intercession of blessed Joseph, Your Confessor, graciously keep safe the gifts You have given us.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.



\newcommand{\kyriePath}{../Ordinaries/masses/11/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/11/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/11/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/11/agnus}

\newcommand{\itePath}{../Ordinaries/masses/11/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/ave-regina-caelorum}
\input{../MarianAntiphons/ave-regina-caelorum_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
