% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica Pentecostes}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Spíritus Dómini replévit orbem terrárum, allelúia: et hoc quod cóntinet ómnia, sciéntiam habet vocis, allelúia, allelúia, allelúia.
Exsúrgat Deus, et dissipéntur inimíci eius: et fúgiant, qui odérunt eum, a fácie eius.
}
\newcommand{\introitTranslation}{%
The Spirit of the Lord fills the world, alleluia, is all-embracing, and knows man’s utterance, alleluia, alleluia, alleluia.
God arises; His enemies are scat\-tered, and those who hate Him flee before Him.
}
% 
\newcommand{\collect}{%
  \l{%
  Deus, qui hodiérna die corda fidélium Sancti Spíritus illustratióne docuísti: da nobis in eódem Spíritu recta sápere; et de eius semper consolatióne gaudére.
  }
  \e{%
  O God, You Who on this day have taught the hearts of the faithful by the light of the Holy Spirit, grant us by that Holy Spirit Himself, to know what is right and ever to rejoice in His help.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
  Cum compleréntur dies Pentecóstes, \linebreak[5] erant omnes discípuli pariter in eódem loco: et factus est repénte de cœlo sonus, tamquam adveniéntis spíritus veheméntis: et replévit totam domum, ubi erant sedentes. Et apparuérunt illis dispertítæ linguæ tamquam ignis, sedítque supra síngulos eórum: et repléti sunt omnes Spíritu Sancto, et cœpérunt loqui váriis linguis, prout Spíritus Sanctus dabat éloqui illis. Erant autem in Ierúsalem habitántes Iudǽi, viri religiósi ex omni natióne, quæ sub cœlo est. Facta autem hac voce, convénit multitúdo, et mente confúsa est, quóniam audiébat unusquísque lingua sua illos loquéntes. Stupébant autem omnes et mirabántur, dicéntes: Nonne ecce omnes isti, qui loquúntur, Galilǽi sunt? Et quómodo nos audívimus unusquísque linguam nostram, in qua nati sumus? Parthi et Medi et Ælamítæ et qui hábitant Mesopotámiam, Iudǽam et Cappadóciam, Pontum et Asiam, Phrýgiam et Pamphýliam, Ægýptum et partes Líbyæ, quæ est circa Cyrénen, et ádvenæ Románi, Iudǽi quoque et Prosélyti, Cretes et Arabes: audívimus eos loquéntes nostris linguis magnália Dei.
  }
  \e{%
  When the days of Pentecost were drawing to a close, they were all together in one place. And suddenly there came a sound from heaven, as of a violent wind blowing, and it filled the whole house where they were sitting. And there appeared to them parted tongues as of fire, which settled upon each of them. And they were all filled with the Holy spirit and began to speak in foreign tongues, even as the Holy Spirit prompted them to speak. Now there were staying at Jerusalem, devout Jews, from every nation under heaven. And when this sound was heard, the multitude gathered and were bewildered in mind, because each heard them speaking in his own language. But they were all amazed and marvelled saying, Behold, are not all these that are speaking Galileans? And how have we heard each his own language in which he was born? Parthians and Medes and Elamites, and inhabitants of Mesopotamia, Judea, and Cappadocia, Pontus and Asia, Phrygia and Pamphilia, Egypt and the parts of Libya about Cyrene, and visitors from Rome, Jews also and proselytes, Cretens and Arabians, we have heard them speaking in our own languages of the wonderful works of God.
  }
}

% 
\newcommand{\gradual}{%
Emítte Spíritum tuum, et creabúntur, et renovábis fáciem terræ. Allelúia.
Veni, Sancte Spíritus, reple tuórum corda fidélium: et tui amóris in eis ignem accénde.
}
\newcommand{\gradualTranslation}{%
Send forth Your Spirit, and they shall be created: and You shall renew the face of the earth. Alleluia.
Come, O Holy Spirit, fill the hearts of Your faithful: and kindle in them the fire of Your love.
}
%

\newcommand{\sequentia}{
Veni, Sancte Spíritus,
et emítte cǽlitus
lucis tuæ rádium.

Veni, pater páuperum;
veni, dator múnerum;
veni, lumen córdium.

Consolátor óptime,
dulcis hospes ánimæ,
dulce refrigérium.

In labóre réquies,
in æstu tempéries,
in fletu solácium.

O lux beatíssima,
reple cordis íntima
tuórum fidélium.

Sine tuo númine
nihil est in hómine,
nihil est innóxium.

Lava quod est sórdidum,
riga quod est áridum,
sana quod est sáucium.

Flecte quod est rígidum,
fove quod est frígidum,
rege quod est dévium.

Da tuis fidélibus,
in te confidéntibus,
sacrum septenárium.

Da virtútis méritum,
da salútis éxitum,
da perénne gáudium.
Amen. Allelúia.
}
\newcommand{\sequentiaTranslation}{
Come, Holy Spirit,
and send out from heaven
the ray of your light.

Come, father of the poor,
come, giver of gifts,
come, light of hearts.

Greatest comforter,
sweet guest of the soul,
sweet consolation.

In labour, rest,
in heat, temperateness,
in tears, solace.

O most blessed light,
fill the inmost heart
of your faithful.

Without the nod of your head,
there is nothing in man,
nothing that is harmless.

Cleanse what is unclean,
water what is parched,
heal what is wounded.

Bend what is inflexible,
warm what is chilled,
correct what has gone astray.

Give to your faithful,
who trust in you,
the sevenfold gift.

Give virtue's reward,
give salvation's end,
give joy eternal.
Amen. Alleluia.
}
%

\newcommand{\gospel}{%
  \l{%
  In illo témpore: Dixit Iesus discípulis suis: Si quis díligit me, sermónem meum servábit, et Pater meus díliget eum, et ad eum veniémus et mansiónem apud eum faciémus: qui non díligit me, sermónes meos non servat. Et sermónem quem audístis, non est meus: sed eius, qui misit me, Patris. Hæc locútus sum vobis, apud vos manens. Paráclitus autem Spíritus Sanctus, quem mittet Pater in nómine meo, ille vos docébit ómnia et súggeret vobis ómnia, quæcúmque díxero vobis. Pacem relínquo vobis, pacem meam do vobis: non quómodo mundus dat, ego do vobis. Non turbétur cor vestrum neque formídet. Audístis, quia ego dixi vobis: Vado et vénio ad vos. Si diligerétis me, gauderétis útique, quia vado ad Patrem: quia Pater maior me est. Et nunc dixi vobis, priúsquam fiat: ut, cum factum fúerit, credátis. Iam non multa loquar vobíscum. Venit enim princeps mundi huius, et in me non habet quidquam. Sed ut cognóscat mundus, quia díligo Patrem, et sicut mandátum dedit mihi Pater, sic fácio.
  }
  \e{%
  At that time, Jesus said to His disciples: If anyone love Me, he will keep My word, and My Father will love him, and We will come to him and make Our abode with him. He who does not love Me, does not keep My words. And the word that you have heard is not Mine, but the Father’s Who sent Me. These things I have spoken to you while yet dwelling with you. But the Advocate, the Holy Spirit, Whom the Father will send in My Name, He will teach you all things, and bring to your mind whatever I have said to you. Peace I leave with you, My peace I give to you; not as the world gives do I give to you. Do not let your heart be troubled, or be afraid. You have heard Me say to you, ‘I go away and I am coming to you.’ If you loved Me, you would indeed rejoice that I am going to the Father, for the Father is greater than I. And now I have told you before it comes to pass, that when it has come to pass you may believe. I will no longer speak much with you, for the prince of the world is coming and in Me he has nothing. But he comes that the world may know that I love the Father, and that I do as the Father has commanded Me.
  }
}
\newcommand{\offertory}{%
Confírma hoc, Deus, quod operátus es in nobis: a templo tuo, quod est in Ierúsalem, tibi ófferent reges múnera, allelúia.
}
\newcommand{\offertoryTranslation}{%
Confirm this, O God, what You have wrought in us; from Your temple, which is in Jerusalem, kings shall offer gifts to You. Alleluia.
}
\newcommand{\secret}{%
  \l{%
  Múnera, quǽsumus, Dómine, obláta sanctífica: et corda nostra Sancti Spíritus illustratióne emúnda.
  }
  \e{%
  Sanctify these offerings, we beseech You, O Lord, and cleanse our hearts by the light of the Holy Spirit.
  }
  \per
}
\newcommand{\communion}{%
Factus est repénte de cœlo sonus, tamquam adveniéntis spíritus veheméntis, ubi erant sedéntes, allelúia: et repléti sunt omnes Spíritu Sancto, loquéntes magnália Dei, allelúia, allelúia.
}
\newcommand{\communionTranslation}{%
Suddenly there came a sound from hea\-ven, as of a violent wind blowing, where they were sitting, alleluia: and they were all filled with the Holy Spirit, speaking of the wonderful works of God, alleluia, alleluia.
}
\newcommand{\postcommunion}{%
  \l{%
  Sancti Spíritus, Dómine, corda nostra mundet infúsio: et sui roris íntima aspersióne fecúndet.
  }
  \e{%
  May the inpouring of the Holy Spirit cleanse our hearts, O Lord, and make them fertile through the dew He sprin\-kles upon them.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.


\newcommand{\kyriePath}{../Ordinaries/masses/1/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/1/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/1/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/1/agnus}

\newcommand{\itePath}{../Ordinaries/masses/1/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\vidiAquamPath}{../ToniCommunes/roman/vidi-aquam}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/regina-caeli}
\input{../MarianAntiphons/regina-caeli_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
