% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica II Adventus}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Pópulus Sion, ecce, Dóminus véniet ad salvándas gentes: et audítam fáciet Dóminus glóriam vocis suæ in lætítia cordis vestri.
Qui regis Israël, inténde: qui dedúcis, velut ovem, Joseph.
}
\newcommand{\introitTranslation}{%
People of Sion, behold the Lord shall come to save the nations; and the Lord shall make the glory of His voice to be heard, in the joy of your heart.
O Shepherd of Israel, hearken, O Guide of the flock of Joseph!
}
% 
\newcommand{\collect}{%
  \l{%
  Excita, Dómine, corda nostra ad præparándas Unigéniti tui vias: ut, per ejus advéntum, purificátis tibi méntibus servíre mereámur:
  }
  \e{%
  Stir up our hearts, O Lord, to prepare the ways of Your only-begotten Son, so that through His coming we may be able to serve You with purified minds.
  }
  \quiTecum
}
\newcommand{\lesson}{%
  \l{%
  Fratres: Quæcúmque scripta sunt, ad nostram doctrínam scripta sunt: ut per patiéntiam et consolatiónem Scripturárum spem habeámus. Deus autem patiéntiæ et solácii det vobis idípsum sápere in altérutrum secúndum Jesum Christum: ut unánimes, uno ore honorificétis Deum et Patrem Dómini nostri Jesu Christi. Propter quod suscípite ínvicem, sicut et Christus suscépit vos in honórem Dei. Dico enim Christum Jesum minístrum fuísse circumcisiónis propter veritátem Dei, ad confirmándas promissiónes patrum: gentes autem super misericórdia honoráre Deum, sicut scriptum est: Proptérea confitébor tibi in géntibus, Dómine, et nómini tuo cantábo. Et íterum dicit: Lætámini, gentes, cum plebe ejus. Et iterum: Laudáte, omnes gentes, Dóminum: et magnificáte eum, omnes pópuli. Et rursus Isaías ait: Erit radix Jesse, et qui exsúrget régere gentes, in eum gentes sperábunt. Deus autem spei répleat vos omni gáudio et pace in credéndo: ut abundétis in spe et virtúte Spíritus Sancti.
  }
  \e{%
  Brethren: Whatever things have been written have been written for our instruction, that through the patience and the consolation afforded by the Scriptures we may have hope. May then the God of patience and of comfort grant you to be of one mind towards one another according to Jesus Christ; that, one in spirit, you may with one mouth glorify the God and Father of our Lord Jesus Christ. Wherefore receive one another, even as Christ has received you to the honor of God. For I say that Christ Jesus has been a minister of the circumcision in order to show God’s fidelity in confirming the promises made to our fathers, but that the Gentiles glorify God because of His mercy, as it is written, Therefore will I praise You among the Gentiles, and will sing to Your name. And again He says, Rejoice, you Gentiles, with His people. And again, Praise the Lord, all you Gentiles; and sing His praises, all you peoples. And again Isaias says, There shall be the root of Jesse, and He Who shall arise to rule the Gentiles... in Him the Gentiles shall hope. Now may the God of hope fill you with all joy and peace in believing, that you may abound in hope and in the power of the Holy Spirit.
  }
}

% 
\newcommand{\gradual}{%
Ex Sion species decóris ejus: Deus maniféste véniet,
Congregáte illi sanctos ejus, qui ordinavérunt testaméntum ejus super sacrifícia. Allelúja, allelúja,
Lætátus sum in his, quæ dicta sunt mihi: in domum Dómini íbimus. Allelúja.
}
\newcommand{\gradualTranslation}{%
From Sion, perfect in beauty, God shines forth.
Gather His faithful ones before Him, those who have made a covenant with Him by sacrifice. Alleluia, alleluia.
I rejoiced because they said to me: We will go up to the house of the Lord. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
  In illo tempore: Cum audísset Joánnes in vínculis ópera Christi, mittens duos de discípulis suis, ait illi: Tu es, qui ventúrus es, an alium exspectámus? Et respóndens Jesus, ait illis: Eúntes renuntiáte Joánni, quæ audístis et vidístis. Cæci vident, claudi ámbulant, leprósi mundántur, surdi áudiunt, mórtui resúrgunt, páuperes evangelizántur: et beátus est, qui non fúerit scandalizátus in me. Illis autem abeúntibus, cœpit Jesus dícere ad turbas de Joánne: Quid exístis in desértum vidére? arúndinem vento agitátam? Sed quid exístis vidére? hóminem móllibus vestitum? Ecce, qui móllibus vestiúntur, in dómibus regum sunt. Sed quid exístis vidére? Prophétam? Etiam dico vobis, et plus quam Prophétam. Hic est enim, de quo scriptum est: Ecce, ego mitto Angelum meum ante fáciem tuam, qui præparábit viam tuam ante te.
  }
  \e{%
  At that time, when John had heard in prison of the works of Christ, he sent two of his disciples to say to Him, Are You He Who is to come, or shall we look for another? And Jesus answering said to them, Go and report to John what you have heard and seen: the blind see, the lame walk, the lepers are cleansed, the deaf hear, the dead rise, the poor have the gospel preached to them. And blessed is he who is not scandalized in Me. Then, as they went away, Jesus began to say to the crowds concerning John, What did you go out to the desert to see? A reed shaken by the wind? But what did you go out to see? A man clothed in soft garments? Behold, those who wear soft garments are in the houses of kings. But what did you go out to see? A prophet? Yes, I tell you, and more than a prophet. This is he of whom it is written, ‘Behold, I send my messenger before Your face, who shall make ready Your way before You.’
  }
}
\newcommand{\offertory}{%
Deus, tu convérsus vivificábis nos, et plebs tua lætábitur in te: osténde nobis, Dómine, misericórdiam tuam, et salutáre tuum da nobis.
}
\newcommand{\offertoryTranslation}{%
Will You not, O God, give us life; and shall not Your people rejoice in You? Show us, O Lord, Your kindness, and grant us Your salvation.
}
\newcommand{\secret}{%
  \l{%
  Placáre, quǽsumus, Dómine, humilitátis nostræ précibus et hóstiis: et, ubi nulla suppétunt suffrágia meritórum, tuis nobis succúrre præsídiis.
  }
  \e{%
  Be appeased, we beseech You, O Lord, by the prayers and offerings of our human frailty, and where the support of our own merits is lacking, come to our assistance with Your protection.
  }
  \perDominum
}
\newcommand{\communion}{%
Jerúsalem, surge et sta in excélso, et vide jucunditátem, quæ véniet tibi a Deo tuo.
}
\newcommand{\communionTranslation}{%
Up, Jerusalem! stand upon the heights; and behold the joy that comes to you from your God.
}
\newcommand{\postcommunion}{%
  \l{%
  Repléti cibo spirituális alimóniæ, súpplices te, Dómine, deprecámur: ut, hujus participatióne mystérii, dóceas nos terréna despícere et amáre cœléstia.
  }
  \e{%
  We who have been refreshed by the food of spiritual nourishment, humbly beseech You, O Lord, that through partaking of this sacrament You will teach us to disdain the things of earth and love those of heaven.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/17/kyrie}

\newcommand{\sanctusPath}{../Ordinaries/masses/17/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/17/agnus}

\newcommand{\itePath}{../Ordinaries/masses/17/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/alma-redemptoris-mater}
\input{../MarianAntiphons/alma-redemptoris-mater_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
