% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Nativitate Beatæ Mariæ Virginis}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Salve, sancta parens, eníxa puérpera Regem: qui cælum terrámque regit in sǽcula sæculórum.
Eructávit cor meum verbum bonum: dico ego ópera mea Regi.
}
\newcommand{\introitTranslation}{%
Hail, holy Mother, who in childbirth brought forth the King Who rules heaven and earth world without end.
My heart overflows with a goodly theme; as I sing my ode to the King.
}
% 
\newcommand{\collect}{%
  \l{%
Fámulis tuis, quǽsumus, Dómine, cœléstis grátiæ munus impertíre: ut, quibus beátæ Vírginis partus éxstitit salútis exórdium; Nativitátis ejus votíva sollémnitas pacis tríbuat increméntum.
  }
  \e{%
Bestow upon Your servants, we beseech You, O Lord, the gift of heavenly grace, that, as the child-bearing of the Blessed Virgin stood for the beginning of our salvation, so may the solemn feast of her Nativity bring about an increase of peace.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
Dóminus possedit me in inítio viárum suárum, ántequam quidquam fáceret a princípio. Ab ætérno ordináta sum, et ex antíquis, ántequam terra fíeret. Nondum erant abýssi, et ego jam concépta eram: necdum fontes aquárum erúperant: necdum montes gravi mole constíterant: ante colles ego parturiébar: adhuc terram non fécerat et flúmina et cárdines orbis terræ. Quando præparábat cœlos, áderam: quando certa lege et gyro vallábat abýssos: quando æthera firmábat sursum et librábat fontes aquárum: quando circúmdabat mari términum suum et legem ponébat aquis, ne transírent fines suos: quando appendébat fundaménta terræ. Cum eo eram cuncta compónens: et delectábar per síngulos dies, ludens coram eo omni témpore: ludens in orbe terrárum: et delíciæ meæ esse cum filiis hóminum. Nunc ergo, filii, audíte me: Beáti, qui custódiunt vias meas. Audíte disciplínam, et estóte sapiéntes, et nolíte abjícere eam. Beátus homo, qui audit me et qui vígilat ad fores meas cotídie, et obsérvat ad postes óstii mei. Qui me invénerit, invéniet vitam et háuriet salútem a Dómino.
  }
  \e{%
The Lord begot me, the firstborn of His ways, the forerunner of His prodigies of long ago; from of old I was poured forth, at the first, before the earth. When there were not depths I was brought forth, when there were not fountains or springs of water; before the mountains were settled into place, before the hills, I was brought forth; while as yet the earth and the fields were not made, nor the first clods of the world. When He established the heavens I was there, when He marked out the vault over the face of the deep; when He made firm the skies above, and poised the fountains of waters; when He set for the sea its limit, so that the waters should not transgress His command; when He fixed fast the foundations of the earth, then was I beside Him as His craftsman, and I was His delight day by day, playing before Him all the while, playing on the surface of His earth and I found delight in the sons of men. So now, O children, listen to me; happy those who keep my ways. Hear instruction, and be wise, and refuse it not. Happy the man who obeys me, watching daily at my gates, waiting at my doorsteps; for he who finds me finds life, and wins favor from the Lord.
  }
}

% 
\newcommand{\gradual}{%
Benedícta et venerábilis es, Virgo María: quæ sine tactu pudóris invénta es Mater Salvatóris.
Virgo, Dei Génetrix, quem totus non capit orbis, in tua se clausit víscera factus homo. Allelúja, allelúja.
Felix es, sacra Virgo María, et omni laude digníssima: quia ex te ortus est sol justítiæ, Christus, Deus noster. Allelúja.
}
\newcommand{\gradualTranslation}{%
Blessed and venerable are you, O Virgin Mary, who, without spot to your maidenhood, were made the Mother of the Saviour.
O Virgin, Mother of God, He Whom the whole world cannot contain, enclosed Himself in your womb, becoming Man. Alleluia, alleluia.
Happy are you, O Holy Virgin Mary, and most worthy of all high praise; for out of you has risen the sun of justice, Christ our God. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
Liber generatiónis Jesu Christi, fílii David, fílii Abraham. Abraham génuit Isaac. Isaac autem génuit Jacob. Jacob autem génuit Judam et fratres ejus. Judas autem génuit Phares et Zaram de Thamar. Phares autem génuit Esron. Esron autem génuit Aram. Aram autem génuit Amínadab. Amínadab autem génuit Naásson. Naásson autem génuit Salmon. Salmon autem génuit Booz de Rahab. Booz autem génuit Obed ex Ruth. Obed autem génuit Jesse. Jesse autem génuit David regem. David autem rex génuit Salomónem ex ea, quæ fuit Uriæ. Sálomon autem génuit Róboam. Róboam autem génuit Abíam. Abías autem génuit Asa. Asa autem génuit Jósaphat. Jósaphat autem génuit Joram. Joram autem génuit Ozíam. Ozías autem génuit Jóatham. Jóatham autem génuit Achaz. Achaz autem génuit Ezechíam. Ezechías autem génuit Manássen. Manásses autem génuit Amon. Amon autem génuit Josíam. Josías autem génuit Jechoníam et fratres ejus in transmigratióne Babylónis. Et post transmigratiónem Babylónis: Jechonías génuit Saláthiel. Saláthiel autem génuit Zoróbabel. Zoróbabel autem génuit Abiud. Abiud autem génuit Elíacim. Elíacim autem génuit Azor. Azor autem génuit Sadoc. Sadoc autem génuit Achim. Achim autem génuit Eliud. Eliud autem génuit Eleázar. Eleázar autem génuit Mathan. Mathan autem génuit Jacob. Jacob autem génuit Joseph, virum Maríæ, de qua natus est Jesus, qui vocátur Christus.
  }
  \e{%
The book of the origins of Jesus Christ, the Son of David, the son of Abraham. Abraham begot Isaac, Isaac begot Jacob, Jacob begot Judas and his brethren. Judas begot Phares and Zara of Thamar, Phares begot Esron, Esron begot Aram. And Aram begot Aminadab, Aminadab begot Naasson, Naasson begot Salmon. Salmon begot Booz of Rahab. Booz begot Obed of Ruth, Obed begot Jesse, Jesse begot David the king. And David the king begot Solomon of the former wife of Urias. Solomon begot Roboam, Roboam begot Abia, Abia begot Asa. And Asa begot Josaphat, Josaphat begot Joram, Joram begot Ozias. And Ozias begot Joatham, Joatham begot Achaz, Achaz begot Ezechias. And Ezechias begot Manasses, Manasses begot Amon, Amon begot Josias. And Josias begot Jechonias and his brethren at the time of the carrying away to Babylon. And after the carrying away to Babylon Jechonias begot Salathiel, Salathiel begot Zorobabel. And Zorobabel begot Abiud, Abiud begot Eliachim, Eliachim begot Azor. And Azor begot Sadoc, Sadoc begot Achim, Achim, begot Eliud. And Eliud begot Eleazar, Eleazar begot Matthan, Matthan begot Jacob. And Jacob begot Joseph, the husband of Mary, and of her was born Jesus Who is called Christ.
  }
}
\newcommand{\offertory}{%
Beáta es, Virgo María, quæ ómnium portásti Creatórem: genuísti qui te fecit, et in ætérnum pérmanes Virgo. Allelúja.
}
\newcommand{\offertoryTranslation}{%
Blessed art thou, O Virgin Mary, who didst bear the Creator of all things, thou didst bring forth who made thee, and remainest a virgin forever. Alleluia.
}
\newcommand{\secret}{%
  \l{%
Unigéniti tui, Dómine, nobis succúrrat humánitas: ut, qui natus de Vírgine, matris integritátem non mínuit, sed sacrávit; in Nativitátis ejus sollémniis, nostris nos piáculis éxuens, oblatiónem nostram tibi fáciat accéptam Jesus Christus, Dóminus noster:
  }
  \e{%
May the humanity of Your only-begotten Son help us, O Lord, as He, Who, born of a virgin did not lessen but consecrated the purity of His mother, so, on the festival of her Nativity may Jesus Christ, our Lord, free us from our sins and render our sacrifice acceptable to You:
  }
  \quiTecum
}
\newcommand{\communion}{%
Beáta víscera Maríæ Vírginis, quæ portavérunt ætérni Patris Fílium.
}
\newcommand{\communionTranslation}{%
Blessed is the womb of the Virgin Mary, which bore the Son of the eternal Father.
}
\newcommand{\postcommunion}{%
  \l{%
Súmpsimus, Dómine, celebritátis ánnuæ votíva sacraménta: præsta, quǽsumus; ut et temporális vitæ nobis remédia prǽbeant et ætérnæ.
  }
  \e{%
O Lord, in celebration of this yearly feast, we have partaken of the sacrament: grant, we beseech You, that it may give us help for life on earth and for life everlasting.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.



\newcommand{\kyriePath}{../Ordinaries/masses/9/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/9/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/9/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/9/agnus}

\newcommand{\itePath}{../Ordinaries/masses/9/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/salve-regina}
\input{../MarianAntiphons/salve-regina_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
