% This file defines the properties to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly executed when building the document.

% For the title page
\newcommand{\feast}{Dominica II in Quadragesima}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
Reminíscere miseratiónum tuarum, Dómine, et misericórdiæ tuæ, quæ a sǽculo sunt: ne umquam dominéntur nobis inimíci nostri: líbera nos, Deus Israël, ex ómnibus angústiis nostris.
Ad te, Dómine, levávi ánimam meam: Deus meus, in te confído, non erubéscam.
}
\newcommand{\introitTranslation}{%
Remember that Your compassion, O Lord, and Your kindness are from of old; let not our enemies exult over us; deliver us, O God of Israel, from all our tribulations.
To You I lift up my soul, O Lord; in You, O my God, I trust; let me not be put to shame.
}
% 
\newcommand{\collect}{%
  \l{%
Deus, qui cónspicis omni nos virtúte destítui: intérius exteriúsque custódi; ut ab ómnibus adversitátibus muniámur in córpore, et a pravis cogitatiónibus mundémur in mente.
  }
  \e{%
O God, You Who see how we are deprived of all strength, guard us inwardly and outwardly, that in body we may be protected against all misfortunes, and in mind cleansed of evil thoughts.
  }
  \perDominum
}
\newcommand{\lesson}{%
  \l{%
Fratres: Rogámus vos et obsecrámus in Dómino Iesu: ut, quemádmodum accepístis a nobis, quómodo opórteat vos ambuláre et placére Deo, sic et ambulétis, ut abundétis magis. Scitis enim, quæ præcépta déderim vobis Per Dominum Iesum. Hæc est enim volúntas Dei, sanctificátio vestra: ut abstineátis vos a fornicatióne, ut sciat unusquísque vestrum vas suum possidére in sanctificatióne et honóre; non in passióne desidérii, sicut et gentes, quæ ignórant Deum: et ne quis supergrediátur neque circumvéniat in negótio fratrem suum: quóniam vindex est Dóminus de his ómnibus, sicut prædíximus vobis et testificáti sumus. Non enim vocávit nos Deus in immundítiam, sed in sanctificatiónem: in Christo Iesu, Dómino nostro.
  }
  \e{%
Brethren: Even as you have learned from us how you ought to walk to please God - as indeed you are walking - we beseech and exhort you in the Lord Jesus to make even greater progress. For you know what precepts I have given to you by the Lord Jesus. For this is the will of God, your sanctification; that you abstain from immorality; that every one of you learn how to possess his vessel in holiness and honor, not in the passion of lust like the Gentiles who do not know God; that no one transgress and overreach his brother in the matter, because the Lord is the avenger of all these things, as we have told you before and have testified. For God has not called us unto uncleanness, but unto holiness, in Christ Jesus our Lord.
  }
}

% 
\newcommand{\gradual}{%
Tribulatiónes cordis mei dilatátæ sunt: de necessitátibus meis éripe me, Dómine,
Vide humilitátem meam et labórem meum: et dimítte ómnia peccáta mea.
Confitémini Dómino, quóniam bonus: quóniam in sǽculum misericórdia eius.
Quis loquétur poténtias Dómini: audítas fáciet omnes laudes eius?
Beáti, qui custódiunt iudícium et fáciunt iustítiam in omni témpore.
Meménto nostri, Dómine, in beneplácito pópuli tui: vísita nos in salutári tuo.
}
\newcommand{\gradualTranslation}{%
Relieve the troubles of my heart and bring me out of my distress, O Lord.
Put an end to my affliction and my suffering, and take away all my sins.
Give thanks to the Lord, for He is good, for His kindness endures forever.
Who can tell the mighty deeds of the Lord, or proclaim all His praises?
Happy are they who observe what is right, who do always what is just.
Remember us, O Lord, as You favor Your people; visit us with Your saving help.
}
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Assúmpsit Iesus Petrum, et Iacóbum, et Ioánnem fratrem eius, et duxit illos in montem excélsum seórsum: et transfigurátus est ante eos. Et resplénduit fácies eius sicut sol: vestiménta autem eius facta sunt alba sicut nix. Et ecce, apparuérunt illis Móyses et Elías cum eo loquéntes. Respóndens autem Petrus, dixit ad Iesum: Dómine, bonum est nos hic esse: si vis, faciámus hic tria tabernácula, tibi unum, Móysi unum et Elíæ unum. Adhuc eo loquénte, ecce, nubes lúcida obumbrávit eos. Et ecce vox de nube, dicens: Hic est Fílius meus diléctus, in quo mihi bene complácui: ipsum audíte. Et audiéntes discípuli, cecidérunt in fáciem suam, et timuérunt valde. Et accéssit Iesus, et tétigit eos, dixítque eis: Súrgite, et nolíte timére. Levántes autem óculos suos, néminem vidérunt nisi solum Iesum. Et descendéntibus illis de monte, præcépit eis Iesus, dicens: Némini dixéritis visiónem, donec Fílius hóminis a mórtuis resúrgat.
  }
  \e{%
At that time, Jesus took Peter, James and his brother John, and led them up a high mountain by themselves, and was transfigured before them. And His face shone as the sun, and His garments became white as snow. And behold, there appeared to them Moses and Elias talking together with Him. Then Peter addressed Jesus, saying, Lord, it is good for us to be here. If You will, let us set up three tents here, one for You, one for Moses, and one for Elias. As he was still speaking, behold, a bright cloud overshadowed them, and behold, a voice out of the cloud said, This is My beloved Son, in Whom I am well pleased; hear Him. And on hearing it the disciples fell on their faces and were exceedingly afraid. And Jesus came near and touched them, and said to them, Arise, and do not be afraid. But lifting up their eyes, they saw no one but Jesus only. And as they were coming down from the mountain, Jesus cautioned them, saying, Tell the vision to no one, till the Son of Man has risen from the dead.
  }
}
\newcommand{\offertory}{%
Meditábor in mandátis tuis, quæ diléxi valde: et levábo manus meas ad mandáta tua, quæ diléxi.
}
\newcommand{\offertoryTranslation}{%
I will delight in Your commands, which I love exceedingly; and I will lift up my hands to Your commands, which I love.
}
\newcommand{\secret}{%
  \l{%
Sacrifíciis præséntibus, Dómine, quǽsumus, inténde placátus: ut et devotióni nostræ profíciant et salúti.
  }
  \e{%
Look with favor, we beseech You, O Lord, upon the offerings here before You, that they may be beneficial for our devotion and for our salvation.
  }
  \perDominum
}
\newcommand{\communion}{%
Intéllege clamórem meum: inténde voci oratiónis meæ, Rex meus et Deus meus: quóniam ad te orábo, Dómine.
}
\newcommand{\communionTranslation}{%
Attend to my sighing; heed my call for help, my King and my God! To You I pray, O Lord.
}
\newcommand{\postcommunion}{%
  \l{%
Súpplices te rogámus, omnípotens Deus: ut quos tuis réficis sacraméntis, tibi étiam plácitis móribus dignánter deservíre concédas.
  }
  \e{%
O almighty God, we humbly beseech You that those whom You refresh with Your sacrament may also worthily serve You in a way pleasing to You.
  }
  \perDominum
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\kyriePath}{../Ordinaries/masses/17/kyrie}

\newcommand{\sanctusPath}{../Ordinaries/masses/17/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/17/agnus}

\newcommand{\itePath}{../Ordinaries/masses/17/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_simple}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/ave-regina-caelorum}
\input{../MarianAntiphons/ave-regina-caelorum_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
