% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Dominica II Post Epiphanium}
\newcommand{\masstype}{ Missa Cantata%
  % %
}
% 
\newcommand{\introit}{%
  Omnis terra adóret te, Deus, et psallat tibi: psalmum dicat nómini tuo, Altíssime.
  Iubiláte Deo, omnis terra, psalmum dícite nómini eius: date glóriam laudi eius.
}
\newcommand{\introitTranslation}{%
  Let all on earth worship You, O God, and sing praise to You, sing praise to Your name, Most High.
  Shout joyfully to God, all you on earth, sing praise to the glory of His name; proclaim His glorious praise.
}
% 
\newcommand{\collect}{%
  \l{%
    Omnípotens sempitérne Deus, qui cœléstia simul et terréna moderáris: supplicatiónes pópuli tui cleménter exáudi; et pacem tuam nostris concéde tempóribus.
  }
  \e{%
    Almighty, everlasting God, You Who govern both the heavens and the earth, graciously hear the humble prayers of Your people and grant us Your peace all the days of our life.
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
    Fratres: Habéntes donatiónes secúndum grátiam, quæ data est nobis, differéntes: sive prophetíam secúndum ratiónem fídei, sive ministérium in ministrándo, sive qui docet in doctrína, qui exhortátur in exhortándo, qui tríbuit in simplicitáte, qui præest in sollicitúdine, qui miserétur in hilaritáte. Diléctio sine simulatióne. Odiéntes malum, adhæréntes bono: Caritáte fraternitátis ínvicem diligéntes: Honóre ínvicem præveniéntes: Sollicitúdine non pigri: Spíritu fervéntes: Dómino serviéntes: Spe gaudéntes: In tribulatióne patiéntes: Oratióni instántes: Necessitátibus sanctórum communicántes: Hospitalitátem sectántes. Benedícite persequéntibus vos: benedícite, et nolíte maledícere. Gaudére cum gaudéntibus, flere cum fléntibus: Idípsum ínvicem sentiéntes: Non alta sapiéntes, sed humílibus consentiéntes.
  }
  \e{%
    Brethren: We have gifts differing according to the grace that has been given us, such as prophecy to be used according to the proportion of faith; or ministry, in ministering; or he who teaches, in teaching; he who exhorts, in exhorting; he who gives, in simplicity; he who presides, with carefulness; he who shows mercy, with cheerfulness. Let love be without pretense. Hate what is evil, hold to what is good. Love one another with honor. Be not slothful in zeal; be fervent in spirit, serving the Lord, rejoicing in hope. Be patient in tribulation, persevering in prayer. Share the needs of the saints, practicing hospitality. Bless those who persecute you; bless and do not curse. Rejoice with those who rejoice; weep with those who weep. Be of one mind towards one another. Do not set your mind on high things but condescend to the lowly.
  }
}

% 
\newcommand{\gradual}{%
  Misit Dóminus verbum suum, et sanávit eos: et erípuit eos de intéritu eórum.
  Confiteántur Dómino misericórdiæ eius: et mirabília eius fíliis hóminum. Allelúia, allelúia.
  Laudáte Dóminum, omnes Angeli eius: laudáte eum, omnes virtútes eius. Allelúia.
}
\newcommand{\gradualTranslation}{%
  The Lord sent forth His word to heal them and to snatch them from destruction.
  Let them give thanks to the Lord for His kindness and His wondrous deeds to the children of men. Alleluia, alleluia.
  Praise the Lord, all you His angels, praise Him, all you His hosts. Alleluia.
}
% 
% 
\newcommand{\gospel}{%
  \l{%
In illo témpore: Núptiæ factæ sunt in Cana Galilǽæ: et erat Mater Iesu ibi. Vocátus est autem et Iesus, et discípuli eius ad núptias. Et deficiénte vino, dicit Mater Iesu ad eum: Vinum non habent. Et dicit ei Iesus: Quid mihi et tibi est, mulier? nondum venit hora mea. Dicit Mater eius minístris: Quodcúmque díxerit vobis, fácite. Erant autem ibi lapídeæ hýdriæ sex pósitæ secúndum purificatiónem Iudæórum, capiéntes síngulæ metrétas binas vel ternas. Dicit eis Iesus: Implete hýdrias aqua. Et implevérunt eas usque ad summum. Et dicit eis Iesus: Hauríte nunc, et ferte architriclíno. Et tulérunt. Ut autem gustávit architriclínus aquam vinum fáctam, et non sciébat unde esset, minístri autem sciébant, qui háuserant aquam: vocat sponsum architriclínus, et dicit ei: Omnis homo primum bonum vinum ponit: et cum inebriáti fúerint, tunc id, quod detérius est. Tu autem servásti bonum vinum usque adhuc. Hoc fecit inítium signórum Iesus in Cana Galilǽæ: et manifestávit glóriam suam, et credidérunt in eum discípuli eius.
  }
  \e{%
At that time, a marriage took place at Cana of Galilee, and the mother of Jesus was there. Now Jesus too was invited to the marriage, and also His disciples. And the wine having run short, the mother of Jesus said to Him, They have no wine. And Jesus said to her, What would you have me do, woman? My hour has not yet come. His mother said to the attendants, Do whatever He tells you. Now six stone water-jars were placed there, after the Jewish manner of purification, each holding two or three measures. Jesus said to them, Fill the jars with water. And they filled them to the brim. And Jesus said to them, Draw out now, and take to the chief steward. And they took it to him. Now when the chief steward had tasted the water after it had become wine, not knowing whence it was - though the attendants who had drawn the water knew, - the chief steward called the bridegroom, and said to him, Every man at first sets forth the good wine, and when they have drunk freely, then that which is poorer. But you have kept the good wine until now. This first of His signs Jesus worked at Cana of Galilee; and He manifested His glory, and His disciples believed in Him.
  }
}
\newcommand{\offertory}{%
  Iubiláte Deo, univérsa terra: psalmum dícite nómini eius: veníte et audíte, et narrábo vobis, omnes qui timétis Deum, quanta fecit Dóminus ánimæ meæ, allelúia.
}
\newcommand{\offertoryTranslation}{%
  Shout joyfully to God, all you on earth, sing praise to the glory of His name. Hear now, all you who fear God, while I declare what the Lord has done for me. Alleluia.
}
\newcommand{\secret}{%
  \l{%
    Oblata, Dómine, múnera sanctífica: nosque a peccatórum nostrórum máculis emúnda.
  }
  \e{%
    Hallow our offerings, O Lord, and cleanse us from the stains of our sins.
  }
  \per
}
\newcommand{\communion}{%
  Dicit Dóminus: Implete hýdrias aqua et ferte architriclíno. Cum gustásset architriclínus aquam vinum factam, dicit sponso: Servásti bonum vinum usque adhuc. Hoc signum fecit Iesus primum coram discípulis suis.
}
\newcommand{\communionTranslation}{%
  The Lord said, Fill the jars with water and take to the chief steward. When the chief steward had tasted the water after it had become wine, he said to the bridegroom, You have kept the good wine until now. This first miracle Jesus worked in the presence of His disciples.
}
\newcommand{\postcommunion}{%
  \l{%
    Augeátur in nobis, quǽsumus, Dómine, tuæ virtútis operatio: ut divínis vegetáti sacraméntis, ad eórum promíssa capiénda, tuo múnere præparémur.
  }
  \e{%
    O Lord, we beseech You that the effects of Your power may ever increase within us; and, strengthened by the divine sacrament, we may be prepared by Your grace to lay hold of what it promises.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.


\newcommand{\kyriePath}{../Ordinaries/masses/4/kyrie}

\newcommand{\gloriaPath}{../Ordinaries/masses/4/gloria}

\newcommand{\sanctusPath}{../Ordinaries/masses/4/sanctus}

\newcommand{\agnusPath}{../Ordinaries/masses/4/agnus}

\newcommand{\itePath}{../Ordinaries/masses/4/ite}


\newcommand{\creedPath}{../Ordinaries/credo/1/credo}


\newcommand{\amenPath}{../ToniCommunes/roman/amen}

\newcommand{\aspergesPath}{../ToniCommunes/roman/asperges}

\newcommand{\dominusVobiscumPath}{../ToniCommunes/roman/dominus-vobiscum}

\newcommand{\paxDominiPath}{../ToniCommunes/roman/pax-domini}

\newcommand{\prefacePath}{../ToniCommunes/roman/preface_standard}

\newcommand{\sedLiberaNosPath}{../ToniCommunes/roman/sed-libera-nos}

\newcommand{\sequentiPath}{../ToniCommunes/roman/sequenti}


\newcommand{\marianPath}{../MarianAntiphons/roman/alma-redemptoris-mater}
\input{../MarianAntiphons/alma-redemptoris-mater_resp}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
